---
title: "behavior_hypotheses_tests_srndnaUGR"
author: "Jen Yang"
date: "2024-11-11, last modified 2025-04-07"
output: 
  html_document:
    code_folding: hide
    toc: true
    toc_float:
      collapsed: false
      smooth_scroll: false
    hightlight: zenburn
    toc_depth: 6
---

```{r clean, include=FALSE}
# clean environment
rm(list = ls())
```

# Load libraries
```{r libraries, message_bi=FALSE, warning=TRUE, include=FALSE}
library(car)
library(plyr)
library(foreign)
library(pscl)
library(boot)
library(MASS)
library(robust)
library(sfsmisc)
library(ggplot2)
library(reshape2)
library(ppcor)
library(ggrepel)
library(Hmisc)
library(tidyverse)
library(sandwich)
library(ggpubr)
library(interactions)
library(knitr)
library(twowaytests)
library(ggfortify)
library(interactions)
library(broom)
library(patchwork)
library(robustbase)
library(lmtest)
library(modelr)
library(Rmisc)
# library(raincloudplots)
library(cowplot)
library(readr)
library(PupillometryR)
library(ggpp)
library(estimatr)
library(skedastic)
library(ggpubr)
library(lubridate)
library(readxl)
library(gridExtra)
library(scales)
library(rstudioapi)
library(jsonlite)
library(rjson)
library(readr)
library(hBayesDM)
library(brms)
library(emmeans)
library(mediation)
library(here)
library(lme4)
library(broom.mixed)
library(easyRT)
library(parameters)
library(effectsize)
library(effects)
library(lmerTest)
library(ez)
library(afex)
library(marginaleffects)
```

```{r}
set.seed(123)
```


# load tsv and prolific raw data
```{r}
gitrepo_path = "/Users/momocco/Documents/GitHub/srndna-ug/behavioral_analyses"

data_dir = paste(gitrepo_path,"data", sep = "/")
codes_dir = paste(gitrepo_path, "codes", sep = "/")
fit_dir = paste(gitrepo_path,"fits", sep = "/")
figure_dir = paste(gitrepo_path,"figures", sep = "/")
```

# load and prepare data
```{r}
# load subs
all_trials_df = read.csv(paste(data_dir, "all_trials_brains.csv", sep = "/"), header = TRUE) %>% 
  .[.$missed == 0,]

colnames(all_trials_df)[colnames(all_trials_df) == "subjID"] <- "participant_id"
indiv_df = read.csv(paste(data_dir, "participant_check.csv", sep = "/"), header = TRUE)  %>%
  mutate(age_bi = case_when(age <= 36 ~ "younger",
                            age > 36 ~ "older"))

all_trials_df = merge(all_trials_df, indiv_df, by.x = "participant_id", by.y = "participant_id")

sublist_final = read.csv(paste(data_dir, "participant_L3_47.csv", sep = "/"), header = TRUE)

all_trials_df = all_trials_df[all_trials_df$participant_id %in% sublist_final$subjID,]

## add a categorical variable that differentiate three groups
all_trials_df = all_trials_df %>% 
  mutate(group_tri = as.factor(case_when(human == 0 ~ 0, # computer
                               human == 1 & ingroup == 0 ~ 1, # outgroup
                               human == 1 & ingroup == 1 ~ 2))) # ingroup
# all_trials_df$group_tri = relevel(all_trials_df$group_tri, ref = "0") # computer

all_trials_df = all_trials_df %>% mutate(human = as.factor(human))

all_trials_df$group_tri = relevel(all_trials_df$group_tri, ref = "1") # outgroup

all_trials_df$age_bi = relevel(as.factor(all_trials_df$age_bi), ref = "younger")

all_trials_df = all_trials_df %>% 
  mutate(age_bi_dummy = case_when(age_bi == "younger" ~ 0,
                                  age_bi == "older" ~ 1)
         )
```

# prereg 1 analyses
## P1 H1.1
H1.1: All participants will reject more unfair offers from human partners as compared to computer partners; this effect will be stronger in younger adults.

Result: only offer/fairness is related to acceptance
```{r}
## full model, won't converge
# model_fit <- glmer(accept ~ offer * human * age_bi + sex +
#                      (1 + offer * human | participant_id),
#                             data = all_trials_df,
#                             family = binomial)
#

## won't converge
# model_fit <- glmer(accept ~ offer * human * age_bi + sex +
#                      (1 + offer * human || participant_id),
#                             data = all_trials_df,
#                             family = binomial)

## won't converge
# model_fit <- glmer(accept ~ offer * human + age_bi + sex +
#                      (1 + offer * human || participant_id),
#                             data = all_trials_df,
#                             family = binomial)

## won't converge
# model_fit <- glmer(accept ~ offer * human + age_bi + sex +
#                      (1 + offer + human || participant_id),
#                             data = all_trials_df,
#                             family = binomial)

## won't converge
# model_fit <- glmer(accept ~ offer * human * age_bi + sex +
#                      (1 + offer + human || participant_id),
#                             data = all_trials_df,
#                             family = binomial)

## won't converge
# model_fit <- glmer(accept ~ offer * human * age_bi + sex +
#                      (1 + offer || participant_id),
#                             data = all_trials_df,
#                            family = binomial)

## won't converge
# model_fit <- glmer(accept ~ offer * human * age_bi + sex +
#                      (1 + human || participant_id),
#                             data = all_trials_df,
#                             family = binomial)

## won't converge
# model1.1_fit <- glmer(accept ~ offer * human * age_bi + sex +
#                      (1 | participant_id),
#                             data = all_trials_df,
#                             family = binomial)
# summary(model1.1_fit)

## won't converge
# model1.1_2_fit <- glmer(accept ~ offer * human * age_bi_dummy + sex - offer : human : age_bi_dummy +
#                      (1 + age_bi_dummy | participant_id),
#                             data = all_trials_df,
#                             family = binomial)

## converged, SIG offer:age_bi effect, NO offer * human effect or age * human
model1.1_2_fit <- glmer(accept ~ offer * human * age_bi + sex - offer : human : age_bi +
                     (1 | participant_id),
                            data = all_trials_df,
                            family = binomial)
summary(model1.1_2_fit)

## converged, not better than model1.1_2_fit
# model1.1_21_fit <- glmer(accept ~ offer * human * age_bi + sex - offer : human : age_bi +
#                      (1 | participant_id) + (1 | block_fair),
#                             data = all_trials_df,
#                             family = binomial)
# summary(model1.1_21_fit)

## converged, not better than model1.1_2_fit
# model1.1_22_fit <- glmer(accept ~ offer * human * age_bi + sex - offer : human : age_bi +
#                      (1 | participant_id) + (1|age_bi),
#                             data = all_trials_df,
#                             family = binomial)
# summary(model1.1_22_fit)
# 
# anova(model1.1_2_fit,model1.1_22_fit,refit=F)
```

## P1 H1.2
H1.2: Within social conditions, younger adults will show increased rates of acceptance when interacting with younger vs. older partners; older adults’ rates of acceptance will not differ between partners.

```{r}
## full model, won't converge
# model1.2_fit <- glmer(accept ~ offer * ingroup * age_bi +
#                      (1 + offer * ingroup | participant_id),
#                             data = all_trials_df,
#                             family = binomial)

## won't converge
# model_fit <- glmer(accept ~ offer * ingroup * age_bi + sex +
#                      (1 + offer * ingroup || participant_id),
#                             data = all_trials_df,
#                             family = binomial)

## won't converge
# model1.2_fit <- glmer(accept ~ offer * ingroup * age_bi +
#                      (1 + offer + ingroup || participant_id),
#                             data = all_trials_df,
#                             family = binomial)

## won't converge
# model_fit <- glmer(accept ~ offer * ingroup + age_bi + sex +
#                      (1 + offer + ingroup || participant_id),
#                             data = all_trials_df,
#                             family = binomial)

## won't converge
# model_fit <- glmer(accept ~ offer * ingroup * age_bi + sex +
#                      (1 + offer || participant_id),
#                             data = all_trials_df,
#                            family = binomial)

## won't converge
# model_fit <- glmer(accept ~ offer * ingroup * age_bi + sex +
#                      (1 + ingroup || participant_id),
#                             data = all_trials_df,
#                             family = binomial)

## converged, no sig offer * ingroup * age_bi
model1.2_fit <- glmer(accept ~ offer * ingroup * age_bi +
                     (1 | participant_id),
                            data = all_trials_df,
                            family = binomial)
summary(model1.2_fit)

## failed to converge
# model1.21_fit <- glmer(accept ~ offer * ingroup * age_bi +
#                      (1 | participant_id) + (1 | block_fair),
#                             data = all_trials_df,
#                             family = binomial)
# summary(model1.21_fit)

## converged, SIG offer:age_biyounger
model1.2_1_fit <- glmer(accept ~ offer * ingroup * age_bi - offer : ingroup : age_bi +
                     (1 | participant_id),
                            data = all_trials_df,
                            family = binomial)
summary(model1.2_1_fit)

## converged, model1.2_1_fit simplified, SIG offer:age_biyounger
model1.2_2_fit <- glmer(accept ~ offer * age_bi + ingroup * age_bi +
                     (1 | participant_id),
                            data = all_trials_df,
                            family = binomial)
summary(model1.2_2_fit)
```

## P1 additional H1.3
suspected group effect of computer vs ingroup vs outgroup based on H1.1 and H1.2 results
H1.2 has sig offer*age interaction but H1.1 doesn't
```{r}
## won't converge 
# model1.3_fit <- glmer(accept ~ offer * group_tri * age_bi +
#                      (1 + offer + group_tri || participant_id),
#                             data = all_trials_df,
#                             family = binomial)

## won't converged, no sig offer * group_tri * age_bi
# model1.3_fit <- glmer(accept ~ offer * group_tri * age_bi + sex +
#                      (1 | participant_id),
#                             data = all_trials_df,
#                             family = binomial)

## converged, SIG offer:age_biolder
model1.3_fit <- glmer(accept ~ offer * group_tri + 
                        # sex +
                          offer * age_bi +
                          age_bi * group_tri +
                     (1 | participant_id),
                            data = all_trials_df,
                            family = binomial)

summary(model1.3_fit)

## converged, SIG offer:age_biolder
model1.3_1_fit <- glmer(accept ~  offer * age_bi + sex +
                     (1 | participant_id),
                            data = all_trials_df,
                            family = binomial)

summary(model1.3_1_fit)

## won't converge
# model1.3_1_fit <- glmer(accept ~ offer * group_tri + 
#                           offer * age_bi + 
#                           age_bi * group_tri +
#                      (1 + offer + group_tri| participant_id),
#                             data = all_trials_df,
#                             family = binomial)

## won't converge
# model1.3_1_fit <- glmer(accept ~ offer * group_tri + 
#                           offer * age_bi + 
#                      (1 + offer + group_tri| participant_id),
#                             data = all_trials_df,
#                             family = binomial)

## converged, SIG offer * age
model1.3_1_fit <- glmer(accept ~ offer * group_tri +
                          offer * age_bi +
                     (1 | participant_id),
                            data = all_trials_df,
                            family = binomial)
summary(model1.3_1_fit)

## won't converge
# model1.3_2_fit <- glmer(accept ~ offer + group_tri + age_bi +
#                      (1 + age_bi|participant_id),
#                             data = all_trials_df,
#                             family = binomial)
# summary(model1.3_2_fit)
```

# prereg 2 analyses
## P2 BH3
BH3) Acceptance rates for an individual offer will vary according to its consistency with other offers in a given block rather than the objective dollar amount of the offer. That is, there will be an offer amount by block interaction, such that acceptance of higher, unfair offers will be greater in unfair blocks, and acceptance of lower, fair offers will be lower in fair blocks, as opposed to participants always rejecting unfair offers and always accepting fair offers.
```{r}
## full model, won't converge
# model_P2_3_fit <- glmer(accept ~ group_tri * age_bi * block_fair +
#                      (1|participant_id),
#                             data = all_trials_df,
#                             family = binomial)

## converged, positive block effect at computer and young, group_tri2:block_fair p 0.097
model_P2_3_fit <- glmer(
  accept ~ group_tri * age_bi * block_fair - group_tri:age_bi:block_fair +
                     (1|participant_id),
                            data = all_trials_df,
                            family = binomial)
summary(model_P2_3_fit)

# block_fair ~ offer colinearity test
block_offer_cor = glm(block_fair~offer, data = all_trials_df, family = binomial)
summary(block_offer_cor)

block_offer_cor = lm(offer~block_fair, data = all_trials_df)
summary(block_offer_cor)
```


