---
title: "behavior_hypotheses_tests_srndnaUGR"
author: "Jen Yang"
date: "2024-11-11, last modified 2025-04-07"
output: 
  html_document:
    code_folding: hide
    toc: true
    toc_float:
      collapsed: false
      smooth_scroll: false
    hightlight: zenburn
    toc_depth: 6
---

```{r clean, include=FALSE}
# clean environment
rm(list = ls())
```

# Load libraries
```{r libraries, message_bi=FALSE, warning=TRUE, include=FALSE}
library(car)
library(plyr)
library(foreign)
library(pscl)
library(boot)
library(MASS)
library(robust)
library(sfsmisc)
library(ggplot2)
library(reshape2)
library(ppcor)
library(ggrepel)
library(Hmisc)
library(tidyverse)
library(sandwich)
library(ggpubr)
library(interactions)
library(knitr)
library(twowaytests)
library(ggfortify)
library(interactions)
library(broom)
library(patchwork)
library(robustbase)
library(lmtest)
library(modelr)
library(Rmisc)
# library(raincloudplots)
library(cowplot)
library(readr)
library(PupillometryR)
library(ggpp)
library(estimatr)
library(skedastic)
library(ggpubr)
library(lubridate)
library(readxl)
library(gridExtra)
library(scales)
library(rstudioapi)
library(jsonlite)
library(rjson)
library(readr)
library(hBayesDM)
library(brms)
library(emmeans)
library(mediation)
library(here)
library(lme4)
library(broom.mixed)
library(easyRT)
library(parameters)
library(effectsize)
library(effects)
library(lmerTest)
library(ez)
library(afex)
library(marginaleffects)
```

```{r}
set.seed(123)
```


# load tsv and prolific raw data
```{r}
gitrepo_path = "/Users/momocco/Documents/GitHub/srndna-ug/behavioral_analyses"

data_dir = paste(gitrepo_path,"data", sep = "/")
codes_dir = paste(gitrepo_path, "codes", sep = "/")
fit_dir = paste(gitrepo_path,"fits", sep = "/")
figure_dir = paste(gitrepo_path,"figures", sep = "/")
```

# load and prepare data
```{r}
# load subs
all_trials_df = read.csv(paste(data_dir, "all_trials_brains.csv", sep = "/"), header = TRUE) %>% 
  .[.$missed == 0,]

colnames(all_trials_df)[colnames(all_trials_df) == "subjID"] <- "participant_id"
indiv_df = read.csv(paste(data_dir, "participant_check.csv", sep = "/"), header = TRUE)  %>%
  mutate(age_bi = case_when(age <= 36 ~ "younger",
                            age > 36 ~ "older"))

all_trials_df = merge(all_trials_df, indiv_df, by.x = "participant_id", by.y = "participant_id")

sublist_final = read.csv(paste(data_dir, "participant_L3_47.csv", sep = "/"), header = TRUE)

all_trials_df = all_trials_df[all_trials_df$participant_id %in% sublist_final$subjID,]

## add a categorical variable that differentiate three groups
all_trials_df = all_trials_df %>% 
  mutate(group_tri = as.factor(case_when(human == 0 ~ 0, # computer
                               human == 1 & ingroup == 0 ~ 1, # outgroup
                               human == 1 & ingroup == 1 ~ 2))) # ingroup
# all_trials_df$group_tri = relevel(all_trials_df$group_tri, ref = "0") # computer

all_trials_df = all_trials_df %>% mutate(human = as.factor(human))

all_trials_df$group_tri = relevel(all_trials_df$group_tri, ref = "1") # outgroup

all_trials_df$age_bi = relevel(as.factor(all_trials_df$age_bi), ref = "younger")

all_trials_df = all_trials_df %>% 
  mutate(age_bi_dummy = case_when(age_bi == "younger" ~ 0,
                                  age_bi == "older" ~ 1)
         )
```

# prereg 1 analyses
## P1 H1.1
H1.1: All participants will reject more unfair offers from human partners as compared to computer partners; this effect will be stronger in younger adults.

Result: only offer/fairness is related to acceptance
```{r}
## full model, won't converge
# model_fit <- glmer(accept ~ offer * human * age_bi + sex +
#                      (1 + offer * human | participant_id),
#                             data = all_trials_df,
#                             family = binomial)
#

## won't converge
# model_fit <- glmer(accept ~ offer * human * age_bi + sex +
#                      (1 + offer * human || participant_id),
#                             data = all_trials_df,
#                             family = binomial)

## won't converge
# model_fit <- glmer(accept ~ offer * human + age_bi + sex +
#                      (1 + offer * human || participant_id),
#                             data = all_trials_df,
#                             family = binomial)

## won't converge
# model_fit <- glmer(accept ~ offer * human + age_bi + sex +
#                      (1 + offer + human || participant_id),
#                             data = all_trials_df,
#                             family = binomial)

## won't converge
# model_fit <- glmer(accept ~ offer * human * age_bi + sex +
#                      (1 + offer + human || participant_id),
#                             data = all_trials_df,
#                             family = binomial)

## won't converge
# model_fit <- glmer(accept ~ offer * human * age_bi + sex +
#                      (1 + offer || participant_id),
#                             data = all_trials_df,
#                            family = binomial)

## won't converge
# model_fit <- glmer(accept ~ offer * human * age_bi + sex +
#                      (1 + human || participant_id),
#                             data = all_trials_df,
#                             family = binomial)

## won't converge
# model1.1_fit <- glmer(accept ~ offer * human * age_bi + sex +
#                      (1 | participant_id),
#                             data = all_trials_df,
#                             family = binomial)
# summary(model1.1_fit)

## won't converge
# model1.1_2_fit <- glmer(accept ~ offer * human * age_bi_dummy + sex - offer : human : age_bi_dummy +
#                      (1 + age_bi_dummy | participant_id),
#                             data = all_trials_df,
#                             family = binomial)

## converged, SIG offer:age_bi effect, NO no offer * human effect or age * human
model1.1_2_fit <- glmer(accept ~ offer * human * age_bi + sex - offer : human : age_bi +
                     (1 | participant_id),
                            data = all_trials_df,
                            family = binomial)
summary(model1.1_2_fit)

## converged, not better than model1.1_2_fit
# model1.1_21_fit <- glmer(accept ~ offer * human * age_bi + sex - offer : human : age_bi +
#                      (1 | participant_id) + (1 | block_fair),
#                             data = all_trials_df,
#                             family = binomial)
# summary(model1.1_21_fit)

## converged, not better than model1.1_2_fit
# model1.1_22_fit <- glmer(accept ~ offer * human * age_bi + sex - offer : human : age_bi +
#                      (1 | participant_id) + (1|age_bi),
#                             data = all_trials_df,
#                             family = binomial)
# summary(model1.1_22_fit)
# 
# anova(model1.1_2_fit,model1.1_22_fit,refit=F)
```

## P1 H1.2
H1.2: Within social conditions, younger adults will show increased rates of acceptance when interacting with younger vs. older partners; older adults’ rates of acceptance will not differ between partners.

```{r}
## full model, won't converge
# model1.2_fit <- glmer(accept ~ offer * ingroup * age_bi +
#                      (1 + offer * ingroup | participant_id),
#                             data = all_trials_df,
#                             family = binomial)

## won't converge
# model_fit <- glmer(accept ~ offer * ingroup * age_bi + sex +
#                      (1 + offer * ingroup || participant_id),
#                             data = all_trials_df,
#                             family = binomial)

## won't converge
# model1.2_fit <- glmer(accept ~ offer * ingroup * age_bi +
#                      (1 + offer + ingroup || participant_id),
#                             data = all_trials_df,
#                             family = binomial)

## won't converge
# model_fit <- glmer(accept ~ offer * ingroup + age_bi + sex +
#                      (1 + offer + ingroup || participant_id),
#                             data = all_trials_df,
#                             family = binomial)

## won't converge
# model_fit <- glmer(accept ~ offer * ingroup * age_bi + sex +
#                      (1 + offer || participant_id),
#                             data = all_trials_df,
#                            family = binomial)

## won't converge
# model_fit <- glmer(accept ~ offer * ingroup * age_bi + sex +
#                      (1 + ingroup || participant_id),
#                             data = all_trials_df,
#                             family = binomial)

## converged, no sig offer * ingroup * age_bi
model1.2_fit <- glmer(accept ~ offer * ingroup * age_bi +
                     (1 | participant_id),
                            data = all_trials_df,
                            family = binomial)
summary(model1.2_fit)

## failed to converge
# model1.21_fit <- glmer(accept ~ offer * ingroup * age_bi +
#                      (1 | participant_id) + (1 | block_fair),
#                             data = all_trials_df,
#                             family = binomial)
# summary(model1.21_fit)

## converged, SIG offer:age_biyounger
model1.2_1_fit <- glmer(accept ~ offer * ingroup * age_bi - offer : ingroup : age_bi +
                     (1 | participant_id),
                            data = all_trials_df,
                            family = binomial)
summary(model1.2_1_fit)

## converged, model1.2_1_fit simplified, SIG offer:age_biyounger
model1.2_2_fit <- glmer(accept ~ offer * age_bi + ingroup * age_bi +
                     (1 | participant_id),
                            data = all_trials_df,
                            family = binomial)
summary(model1.2_2_fit)
```

## P1 additional H1.3
suspected group effect of computer vs ingroup vs outgroup based on H1.1 and H1.2 results
H1.2 has sig offer*age interaction but H1.1 doesn't
```{r}
## won't converge 
# model1.3_fit <- glmer(accept ~ offer * group_tri * age_bi +
#                      (1 + offer + group_tri || participant_id),
#                             data = all_trials_df,
#                             family = binomial)

## won't converged, no sig offer * group_tri * age_bi
# model1.3_fit <- glmer(accept ~ offer * group_tri * age_bi + sex +
#                      (1 | participant_id),
#                             data = all_trials_df,
#                             family = binomial)

## converged, SIG offer:age_biolder
model1.3_fit <- glmer(accept ~ offer * group_tri + sex +
                          offer * age_bi +
                          age_bi * group_tri +
                     (1 | participant_id),
                            data = all_trials_df,
                            family = binomial)

summary(model1.3_fit)

## converged, SIG offer:age_biolder
model1.3_1_fit <- glmer(accept ~  offer * age_bi + sex +
                     (1 | participant_id),
                            data = all_trials_df,
                            family = binomial)

summary(model1.3_1_fit)

## won't converge
# model1.3_1_fit <- glmer(accept ~ offer * group_tri + 
#                           offer * age_bi + 
#                           age_bi * group_tri +
#                      (1 + offer + group_tri| participant_id),
#                             data = all_trials_df,
#                             family = binomial)

## won't converge
# model1.3_1_fit <- glmer(accept ~ offer * group_tri + 
#                           offer * age_bi + 
#                      (1 + offer + group_tri| participant_id),
#                             data = all_trials_df,
#                             family = binomial)

## converged, SIG offer * age
model1.3_1_fit <- glmer(accept ~ offer * group_tri +
                          offer * age_bi +
                     (1 | participant_id),
                            data = all_trials_df,
                            family = binomial)
summary(model1.3_1_fit)

## won't converge
# model1.3_2_fit <- glmer(accept ~ offer + group_tri + age_bi +
#                      (1 + age_bi|participant_id),
#                             data = all_trials_df,
#                             family = binomial)
# summary(model1.3_2_fit)
```

# prereg 2 analyses
## P2 BH3
BH3) Acceptance rates for an individual offer will vary according to its consistency with other offers in a given block rather than the objective dollar amount of the offer. That is, there will be an offer amount by block interaction, such that acceptance of higher, unfair offers will be greater in unfair blocks, and acceptance of lower, fair offers will be lower in fair blocks, as opposed to participants always rejecting unfair offers and always accepting fair offers.
```{r}
## full model, won't converge
# model_P2_3_fit <- glmer(accept ~ offer * group_tri * age_bi * block_fair +
#                      (1|participant_id),
#                             data = all_trials_df,
#                             family = binomial)

## won't converge
# model_P2_3_fit <- glmer(
#   accept ~ offer * group_tri * age_bi * block_fair - offer:group_tri:age_bi:block_fair +
#                      (1|participant_id),
#                             data = all_trials_df,
#                             family = binomial)

## won't converge
# model_P2_3_fit <- glmer(accept ~ offer * age_bi * block_fair + group_tri +
#                      (1|participant_id),
#                             data = all_trials_df,
#                             family = binomial)

## won't converge
# model_P2_3_fit <- glmer(accept ~ offer * age_bi * block_fair + group_tri * block_fair +
#                      (1|participant_id),
#                             data = all_trials_df,
#                             family = binomial)

## converged, block main sig
model_P2_3_fit <- glmer(accept ~ offer * age_bi * block_fair + group_tri -
                          offer:age_bi:block_fair +
                     (1|participant_id),
                            data = all_trials_df,
                            family = binomial)


summary(model_P2_3_fit)

block_effect<-Effect("block_fair", model_P2_3_fit)
data.frame(block_effect)
avg_slopes(model=model_P2_3_fit,re.form=NA)

## further simplified model based on sig above, all unnecessary non-sig removed
model_P2_31_fit <- glmer(accept ~ offer * age_bi + block_fair +
                     (1|participant_id),
                            data = all_trials_df,
                            family = binomial)

summary(model_P2_31_fit)

block_effect<-Effect("block_fair", model_P2_31_fit)
data.frame(block_effect)
avg_slopes(model=model_P2_31_fit,re.form=NA)
```

## P2 NH1A
"NH1A) The anterior insula (ins), dorsal anterior cingulate cortex (dACC), ventromedial prefrontal cortex (vmPFC), and ventral striatum (VS) will be associated with choice." [ins, dACC, vmPFC, VS]

accept ~ brain * age(or group) + (1|participant)

### prepare empty df to store results
```{r}
results_cols = c("brain", "mod", "Coef", "p", "p_check", "p_0125_check")
results_df = data.frame(matrix(nrow = 4*(3+1), ncol = length(results_cols)))
colnames(results_df) = results_cols
```

### anterior insula * age, strict prereg, not sig
```{r}
## converge, no interaction
model_P2_NH1_antIns_age_fit = glmer(accept ~ anteriorinsula_corrected * age_bi +
                     (1|participant_id), 
                     data = all_trials_df,
                            family = binomial)
summary(model_P2_NH1_antIns_age_fit)

m_params = model_parameters(model_P2_NH1_antIns_age_fit, effects = "fixed")

N_nonNA_results = sum(!is.na(results_df$brain))
results_df$brain[N_nonNA_results+1] = m_params$Parameter[2]
results_df$mod[N_nonNA_results+1] = m_params$Parameter[3]
results_df$p[N_nonNA_results+1] = m_params$p[4]
results_df$Coef[N_nonNA_results+1] = m_params$Coefficient[4]
```

### anterior insula * group, strict prereg, sig
```{r}
## converge, no interaction
model_P2_NH1_antIns_group_fit = glmer(accept ~ anteriorinsula_corrected * group_tri +
                                      (1|participant_id), 
                                    data = all_trials_df,
                                    family = binomial)
summary(model_P2_NH1_antIns_group_fit)

m_params = model_parameters(model_P2_NH1_antIns_group_fit, effects = "fixed")

N_nonNA_results = sum(!is.na(results_df$brain))
results_df$brain[N_nonNA_results+1] = m_params$Parameter[2]
results_df$mod[N_nonNA_results+1] = m_params$Parameter[3]
results_df$p[N_nonNA_results+1] = m_params$p[5]
results_df$Coef[N_nonNA_results+1] = m_params$Coefficient[5]

N_nonNA_results = sum(!is.na(results_df$brain))
results_df$brain[N_nonNA_results+1] = m_params$Parameter[2]
results_df$mod[N_nonNA_results+1] = m_params$Parameter[4]
results_df$p[N_nonNA_results+1] = m_params$p[6]
results_df$Coef[N_nonNA_results+1] = m_params$Coefficient[6]
```

### ant insula main, strict prereg, not sig
```{r}
## converged, no sig vmpfc_corrected * age_bi
model_P2_NH1_antIns_main_fit <- glmer(accept ~ anteriorinsula_corrected +
                                      (1|participant_id),
                                    data = all_trials_df,
                                    family = binomial)
summary(model_P2_NH1_antIns_main_fit)

m_params = model_parameters(model_P2_NH1_antIns_main_fit, effects = "fixed")

N_nonNA_results = sum(!is.na(results_df$brain))
results_df$brain[N_nonNA_results+1] = m_params$Parameter[2]
results_df$mod[N_nonNA_results+1] = "main"
results_df$p[N_nonNA_results+1] = m_params$p[2]
results_df$Coef[N_nonNA_results+1] = m_params$Coefficient[2]
```

### dacc * age, strict prereg
```{r}
## converged, no sig dacc_corrected * age_bi
model_P2_NH1_dacc_age_fit <- glmer(accept ~ dacc_corrected * age_bi +
                                     (1|participant_id),
                            data = all_trials_df,
                            family = binomial)
summary(model_P2_NH1_dacc_age_fit)

m_params = model_parameters(model_P2_NH1_dacc_age_fit, effects = "fixed")

N_nonNA_results = sum(!is.na(results_df$brain))
results_df$brain[N_nonNA_results+1] = m_params$Parameter[2]
results_df$mod[N_nonNA_results+1] = m_params$Parameter[3]
results_df$p[N_nonNA_results+1] = m_params$p[4]
results_df$Coef[N_nonNA_results+1] = m_params$Coefficient[4]
```

### dacc * group, strict prereg, not sig
```{r}
## converged, no sig dacc_corrected * age_bi
model_P2_NH1_dacc_group_fit <- glmer(accept ~ dacc_corrected * group_tri +
                                     (1|participant_id),
                            data = all_trials_df,
                            family = binomial)
summary(model_P2_NH1_dacc_group_fit)

m_params = model_parameters(model_P2_NH1_dacc_group_fit, effects = "fixed")

N_nonNA_results = sum(!is.na(results_df$brain))
results_df$brain[N_nonNA_results+1] = m_params$Parameter[2]
results_df$mod[N_nonNA_results+1] = m_params$Parameter[3]
results_df$p[N_nonNA_results+1] = m_params$p[5]
results_df$Coef[N_nonNA_results+1] = m_params$Coefficient[5]

N_nonNA_results = sum(!is.na(results_df$brain))
results_df$brain[N_nonNA_results+1] = m_params$Parameter[2]
results_df$mod[N_nonNA_results+1] = m_params$Parameter[4]
results_df$p[N_nonNA_results+1] = m_params$p[6]
results_df$Coef[N_nonNA_results+1] = m_params$Coefficient[6]
```

### dacc main, strict prereg, not sig
```{r}
## converged, no sig dacc_corrected * age_bi
model_P2_NH1_dacc_main_fit <- glmer(accept ~ dacc_corrected +
                                     (1|participant_id),
                            data = all_trials_df,
                            family = binomial)
summary(model_P2_NH1_dacc_main_fit)

m_params = model_parameters(model_P2_NH1_dacc_main_fit, effects = "fixed")

N_nonNA_results = sum(!is.na(results_df$brain))
results_df$brain[N_nonNA_results+1] = m_params$Parameter[2]
results_df$mod[N_nonNA_results+1] = "main"
results_df$p[N_nonNA_results+1] = m_params$p[2]
results_df$Coef[N_nonNA_results+1] = m_params$Coefficient[2]
```

### VS * age, strict prereg, sig, not sig after correction
```{r}
## converged, no sig VS_corrected * age_bi
model_P2_NH1_VS_age_fit <- glmer(accept ~ VS_corrected * age_bi +
                                     (1|participant_id),
                                   data = all_trials_df,
                                   family = binomial)
summary(model_P2_NH1_VS_age_fit)

m_params = model_parameters(model_P2_NH1_VS_age_fit, effects = "fixed")

N_nonNA_results = sum(!is.na(results_df$brain))
results_df$brain[N_nonNA_results+1] = m_params$Parameter[2]
results_df$mod[N_nonNA_results+1] = m_params$Parameter[3]
results_df$p[N_nonNA_results+1] = m_params$p[4]
results_df$Coef[N_nonNA_results+1] = m_params$Coefficient[4]
```

### VS * group, strict prereg, sig
```{r}
## converged, no sig VS_corrected * age_bi
model_P2_NH1_VS_group_fit <- glmer(accept ~ VS_corrected * group_tri +
                                       (1|participant_id),
                                     data = all_trials_df,
                                     family = binomial)
summary(model_P2_NH1_VS_group_fit)

m_params = model_parameters(model_P2_NH1_VS_group_fit, effects = "fixed")

N_nonNA_results = sum(!is.na(results_df$brain))
results_df$brain[N_nonNA_results+1] = m_params$Parameter[2]
results_df$mod[N_nonNA_results+1] = m_params$Parameter[3]
results_df$p[N_nonNA_results+1] = m_params$p[5]
results_df$Coef[N_nonNA_results+1] = m_params$Coefficient[5]

N_nonNA_results = sum(!is.na(results_df$brain))
results_df$brain[N_nonNA_results+1] = m_params$Parameter[2]
results_df$mod[N_nonNA_results+1] = m_params$Parameter[4]
results_df$p[N_nonNA_results+1] = m_params$p[6]
results_df$Coef[N_nonNA_results+1] = m_params$Coefficient[6]
```

### VS main, strict prereg, sig
```{r}
## converged, no sig VS_corrected * age_bi
model_P2_NH1_VS_main_fit <- glmer(accept ~ VS_corrected +
                                      (1|participant_id),
                                    data = all_trials_df,
                                    family = binomial)
summary(model_P2_NH1_VS_main_fit)

m_params = model_parameters(model_P2_NH1_VS_main_fit, effects = "fixed")

N_nonNA_results = sum(!is.na(results_df$brain))
results_df$brain[N_nonNA_results+1] = m_params$Parameter[2]
results_df$mod[N_nonNA_results+1] = "main"
results_df$p[N_nonNA_results+1] = m_params$p[2]
results_df$Coef[N_nonNA_results+1] = m_params$Coefficient[2]
```

### vmpfc * age, strict prereg, sig
```{r}
## converged, no sig vmpfc_corrected * age_bi
model_P2_NH1_vmpfc_age_fit <- glmer(accept ~ vmpfc_corrected * age_bi +
                                     (1|participant_id),
                                   data = all_trials_df,
                                   family = binomial)
summary(model_P2_NH1_vmpfc_age_fit)

m_params = model_parameters(model_P2_NH1_vmpfc_age_fit, effects = "fixed")

N_nonNA_results = sum(!is.na(results_df$brain))
results_df$brain[N_nonNA_results+1] = m_params$Parameter[2]
results_df$mod[N_nonNA_results+1] = m_params$Parameter[3]
results_df$p[N_nonNA_results+1] = m_params$p[4]
results_df$Coef[N_nonNA_results+1] = m_params$Coefficient[4]
```

### vmpfc * group, strict prereg, not sig
```{r}
## converged, no sig vmpfc_corrected * age_bi
model_P2_NH1_vmpfc_group_fit <- glmer(accept ~ vmpfc_corrected * group_tri +
                                       (1|participant_id),
                                     data = all_trials_df,
                                     family = binomial)
summary(model_P2_NH1_vmpfc_group_fit)

m_params = model_parameters(model_P2_NH1_vmpfc_group_fit, effects = "fixed")

N_nonNA_results = sum(!is.na(results_df$brain))
results_df$brain[N_nonNA_results+1] = m_params$Parameter[2]
results_df$mod[N_nonNA_results+1] = m_params$Parameter[3]
results_df$p[N_nonNA_results+1] = m_params$p[5]
results_df$Coef[N_nonNA_results+1] = m_params$Coefficient[5]

N_nonNA_results = sum(!is.na(results_df$brain))
results_df$brain[N_nonNA_results+1] = m_params$Parameter[2]
results_df$mod[N_nonNA_results+1] = m_params$Parameter[4]
results_df$p[N_nonNA_results+1] = m_params$p[6]
results_df$Coef[N_nonNA_results+1] = m_params$Coefficient[6]
```

### vmpfc main, strict prereg, not sig
```{r}
## converged, no sig vmpfc_corrected * age_bi
model_P2_NH1_vmpfc_main_fit <- glmer(accept ~ vmpfc_corrected +
                                      (1|participant_id),
                                    data = all_trials_df,
                                    family = binomial)
summary(model_P2_NH1_vmpfc_main_fit)

m_params = model_parameters(model_P2_NH1_vmpfc_main_fit, effects = "fixed")

N_nonNA_results = sum(!is.na(results_df$brain))
results_df$brain[N_nonNA_results+1] = m_params$Parameter[2]
results_df$mod[N_nonNA_results+1] = "main"
results_df$p[N_nonNA_results+1] = m_params$p[2]
results_df$Coef[N_nonNA_results+1] = m_params$Coefficient[2]
```


### clean single trial results
```{r}
results_df = results_df %>% 
  mutate(p_check = case_when(p >=0.05 ~ NA,
                                p < 0.05 ~ "*" ),
         p_0125_check = case_when(p >=0.0125 ~ NA,
                                p < 0.0125 ~ "*"),
         p = round(p,4))
```


## P2 NH1A, human vs computer
"NH1A) The anterior insula (ins), dorsal anterior cingulate cortex (dACC), ventromedial prefrontal cortex (vmPFC), and ventral striatum (VS) will be associated with choice." [ins, dACC, vmPFC, VS]

accept ~ brain * age(or group) + (1|participant)

### prepare empty df to store results
```{r}
results_cols = c("brain", "mod", "Coef", "p", "p_check", "p_0125_check")
results_df = data.frame(matrix(nrow = 4*(3+1), ncol = length(results_cols)))
colnames(results_df) = results_cols
```

### anterior insula * age, strict prereg, not sig
```{r}
## converge, no interaction
model_P2_NH1_antIns_age_fit = glmer(accept ~ anteriorinsula_corrected * age_bi +
                                      (1|participant_id), 
                                    data = all_trials_df,
                                    family = binomial)
summary(model_P2_NH1_antIns_age_fit)

m_params = model_parameters(model_P2_NH1_antIns_age_fit, effects = "fixed")

N_nonNA_results = sum(!is.na(results_df$brain))
results_df$brain[N_nonNA_results+1] = m_params$Parameter[2]
results_df$mod[N_nonNA_results+1] = m_params$Parameter[3]
results_df$p[N_nonNA_results+1] = m_params$p[4]
results_df$Coef[N_nonNA_results+1] = m_params$Coefficient[4]
```

### anterior insula * group, strict prereg, sig
```{r}
## converge, no interaction
model_P2_NH1_antIns_group_fit = glmer(accept ~ anteriorinsula_corrected * human +
                                        (1|participant_id), 
                                      data = all_trials_df,
                                      family = binomial)
summary(model_P2_NH1_antIns_group_fit)

m_params = model_parameters(model_P2_NH1_antIns_group_fit, effects = "fixed")

N_nonNA_results = sum(!is.na(results_df$brain))
results_df$brain[N_nonNA_results+1] = m_params$Parameter[2]
results_df$mod[N_nonNA_results+1] = m_params$Parameter[3]
results_df$p[N_nonNA_results+1] = m_params$p[4]
results_df$Coef[N_nonNA_results+1] = m_params$Coefficient[4]
```

### ant insula main, strict prereg, not sig
```{r}
## converged, no sig vmpfc_corrected * age_bi
model_P2_NH1_antIns_main_fit <- glmer(accept ~ anteriorinsula_corrected +
                                        (1|participant_id),
                                      data = all_trials_df,
                                      family = binomial)
summary(model_P2_NH1_antIns_main_fit)

m_params = model_parameters(model_P2_NH1_antIns_main_fit, effects = "fixed")

N_nonNA_results = sum(!is.na(results_df$brain))
results_df$brain[N_nonNA_results+1] = m_params$Parameter[2]
results_df$mod[N_nonNA_results+1] = "main"
results_df$p[N_nonNA_results+1] = m_params$p[2]
results_df$Coef[N_nonNA_results+1] = m_params$Coefficient[2]
```

### dacc * age, strict prereg
```{r}
## converged, no sig dacc_corrected * age_bi
model_P2_NH1_dacc_age_fit <- glmer(accept ~ dacc_corrected * age_bi +
                                     (1|participant_id),
                                   data = all_trials_df,
                                   family = binomial)
summary(model_P2_NH1_dacc_age_fit)

m_params = model_parameters(model_P2_NH1_dacc_age_fit, effects = "fixed")

N_nonNA_results = sum(!is.na(results_df$brain))
results_df$brain[N_nonNA_results+1] = m_params$Parameter[2]
results_df$mod[N_nonNA_results+1] = m_params$Parameter[3]
results_df$p[N_nonNA_results+1] = m_params$p[4]
results_df$Coef[N_nonNA_results+1] = m_params$Coefficient[4]
```

### dacc * group, strict prereg, not sig
```{r}
## converged, no sig dacc_corrected * age_bi
model_P2_NH1_dacc_group_fit <- glmer(accept ~ dacc_corrected * human +
                                       (1|participant_id),
                                     data = all_trials_df,
                                     family = binomial)
summary(model_P2_NH1_dacc_group_fit)

m_params = model_parameters(model_P2_NH1_dacc_group_fit, effects = "fixed")

N_nonNA_results = sum(!is.na(results_df$brain))
results_df$brain[N_nonNA_results+1] = m_params$Parameter[2]
results_df$mod[N_nonNA_results+1] = m_params$Parameter[3]
results_df$p[N_nonNA_results+1] = m_params$p[4]
results_df$Coef[N_nonNA_results+1] = m_params$Coefficient[4]
```

### dacc main, strict prereg, not sig
```{r}
## converged, no sig dacc_corrected * age_bi
model_P2_NH1_dacc_main_fit <- glmer(accept ~ dacc_corrected +
                                      (1|participant_id),
                                    data = all_trials_df,
                                    family = binomial)
summary(model_P2_NH1_dacc_main_fit)

m_params = model_parameters(model_P2_NH1_dacc_main_fit, effects = "fixed")

N_nonNA_results = sum(!is.na(results_df$brain))
results_df$brain[N_nonNA_results+1] = m_params$Parameter[2]
results_df$mod[N_nonNA_results+1] = "main"
results_df$p[N_nonNA_results+1] = m_params$p[2]
results_df$Coef[N_nonNA_results+1] = m_params$Coefficient[2]
```

### VS * age, strict prereg, sig, not sig after correction
```{r}
## converged, no sig VS_corrected * age_bi
model_P2_NH1_VS_age_fit <- glmer(accept ~ VS_corrected * age_bi +
                                   (1|participant_id),
                                 data = all_trials_df,
                                 family = binomial)
summary(model_P2_NH1_VS_age_fit)

m_params = model_parameters(model_P2_NH1_VS_age_fit, effects = "fixed")

N_nonNA_results = sum(!is.na(results_df$brain))
results_df$brain[N_nonNA_results+1] = m_params$Parameter[2]
results_df$mod[N_nonNA_results+1] = m_params$Parameter[3]
results_df$p[N_nonNA_results+1] = m_params$p[4]
results_df$Coef[N_nonNA_results+1] = m_params$Coefficient[4]
```

### VS * group, strict prereg, sig
```{r}
## converged, no sig VS_corrected * age_bi
model_P2_NH1_VS_group_fit <- glmer(accept ~ VS_corrected * human +
                                     (1|participant_id),
                                   data = all_trials_df,
                                   family = binomial)
summary(model_P2_NH1_VS_group_fit)

m_params = model_parameters(model_P2_NH1_VS_group_fit, effects = "fixed")

N_nonNA_results = sum(!is.na(results_df$brain))
results_df$brain[N_nonNA_results+1] = m_params$Parameter[2]
results_df$mod[N_nonNA_results+1] = m_params$Parameter[3]
results_df$p[N_nonNA_results+1] = m_params$p[4]
results_df$Coef[N_nonNA_results+1] = m_params$Coefficient[4]
```

### VS main, strict prereg, sig
```{r}
## converged, no sig VS_corrected * age_bi
model_P2_NH1_VS_main_fit <- glmer(accept ~ VS_corrected +
                                    (1|participant_id),
                                  data = all_trials_df,
                                  family = binomial)
summary(model_P2_NH1_VS_main_fit)

m_params = model_parameters(model_P2_NH1_VS_main_fit, effects = "fixed")

N_nonNA_results = sum(!is.na(results_df$brain))
results_df$brain[N_nonNA_results+1] = m_params$Parameter[2]
results_df$mod[N_nonNA_results+1] = "main"
results_df$p[N_nonNA_results+1] = m_params$p[2]
results_df$Coef[N_nonNA_results+1] = m_params$Coefficient[2]
```

### vmpfc * age, strict prereg, sig
```{r}
## converged, no sig vmpfc_corrected * age_bi
model_P2_NH1_vmpfc_age_fit <- glmer(accept ~ vmpfc_corrected * age_bi +
                                      (1|participant_id),
                                    data = all_trials_df,
                                    family = binomial)
summary(model_P2_NH1_vmpfc_age_fit)

m_params = model_parameters(model_P2_NH1_vmpfc_age_fit, effects = "fixed")

N_nonNA_results = sum(!is.na(results_df$brain))
results_df$brain[N_nonNA_results+1] = m_params$Parameter[2]
results_df$mod[N_nonNA_results+1] = m_params$Parameter[3]
results_df$p[N_nonNA_results+1] = m_params$p[4]
results_df$Coef[N_nonNA_results+1] = m_params$Coefficient[4]
```

### vmpfc * group, strict prereg, not sig
```{r}
## converged, no sig vmpfc_corrected * age_bi
model_P2_NH1_vmpfc_group_fit <- glmer(accept ~ vmpfc_corrected * human +
                                        (1|participant_id),
                                      data = all_trials_df,
                                      family = binomial)
summary(model_P2_NH1_vmpfc_group_fit)

m_params = model_parameters(model_P2_NH1_vmpfc_group_fit, effects = "fixed")

N_nonNA_results = sum(!is.na(results_df$brain))
results_df$brain[N_nonNA_results+1] = m_params$Parameter[2]
results_df$mod[N_nonNA_results+1] = m_params$Parameter[3]
results_df$p[N_nonNA_results+1] = m_params$p[4]
results_df$Coef[N_nonNA_results+1] = m_params$Coefficient[4]
```

### vmpfc main, strict prereg, not sig
```{r}
## converged, no sig vmpfc_corrected * age_bi
model_P2_NH1_vmpfc_main_fit <- glmer(accept ~ vmpfc_corrected +
                                       (1|participant_id),
                                     data = all_trials_df,
                                     family = binomial)
summary(model_P2_NH1_vmpfc_main_fit)

m_params = model_parameters(model_P2_NH1_vmpfc_main_fit, effects = "fixed")

N_nonNA_results = sum(!is.na(results_df$brain))
results_df$brain[N_nonNA_results+1] = m_params$Parameter[2]
results_df$mod[N_nonNA_results+1] = "main"
results_df$p[N_nonNA_results+1] = m_params$p[2]
results_df$Coef[N_nonNA_results+1] = m_params$Coefficient[2]
```


## clean single trial results
```{r}
results_df = results_df %>% 
  mutate(p_check = case_when(p >=0.05 ~ NA,
                             p < 0.05 ~ "*" ),
         p_0125_check = case_when(p >=0.0125 ~ NA,
                                  p < 0.0125 ~ "*"),
         p = round(p,4))
```



## P2 NH1B
"NH1B) The ins and dACC will be activated during the rejection of offers."
[insula, dACC][reject] (?)


## P2 NH1C
"NH1C) The vmPFC and VS will be activated during the acceptance of offers."
[vmPFC, VS][accept] (?) 


## P2 NH2A
"NH2A) All effects specified in NH1 will be blunted in older adults."
ROI mean ~ age



## P2 NH2B
"NH2B) The effect specified in NHB1 will be enhanced when rejecting unfair offers from human versus computer partners."
[insula, dACC][reject, human > computer]


# P2 NH single trial exploratory
### anterior insula, exploratory
```{r, eval = F}
# ## won't converge
# # model_P2_NH1_antIns_fit <- glmer(accept ~ anteriorinsula_corrected * age_bi * group_tri * block_fair +
# #                      (1|participant_id),
# #                             data = all_trials_df,
# #                             family = binomial)
# 
# ## converged, NO SIG three-way interaction
# model_P2_NH1_antIns_fit <- glmer(accept ~ anteriorinsula_corrected * age_bi * group_tri * block_fair -
#                             anteriorinsula_corrected:age_bi:group_tri:block_fair +
#                             (1|participant_id),
#                             data = all_trials_df,
#                             family = binomial)
# summary(model_P2_NH1_antIns_fit)
# 
# ## converged, SIG ant insula * group interaction
# model_P2_NH1_antIns_fit <- glmer(accept ~ anteriorinsula_corrected * age_bi * group_tri * block_fair -
#                             anteriorinsula_corrected:age_bi:group_tri:block_fair -
#                               anteriorinsula_corrected:age_bi:group_tri -
#                               anteriorinsula_corrected:age_bi:block_fair -
#                               anteriorinsula_corrected:group_tri:block_fair -
#                               age_bi:group_tri:block_fair +
#                               (1|participant_id),
#                             data = all_trials_df,
#                             family = binomial)
# summary(model_P2_NH1_antIns_fit)
# 
# ## won't converge
# # model_P2_NH1_fit <- glmer(accept ~ anteriorinsula_corrected * age_bi * group_tri +
# #                      (1|participant_id),
# #                             data = all_trials_df,
# #                             family = binomial)
# 
# ## converged, SIG insula*group interaction
# model_P2_NH1_antIns_fit <- glmer(accept ~ anteriorinsula_corrected * age_bi * group_tri -
#                             anteriorinsula_corrected:age_bi:group_tri + 
#                               anteriorinsula_corrected * age_bi * block_fair +
#                      (1|participant_id),
#                             data = all_trials_df,
#                             family = binomial)
# summary(model_P2_NH1_antIns_fit)
```


