---
title: "singletrial_hypotheses_tests_srndnaUGR"
author: "Jen Yang"
date: "2025-04-09, last modified 2025-04-09"
output: 
  html_document:
    code_folding: hide
    toc: true
    toc_float:
      collapsed: false
      smooth_scroll: false
    hightlight: zenburn
    toc_depth: 6
---

```{r clean, include=FALSE}
# clean environment
rm(list = ls())
```

# Load libraries
```{r libraries, message_bi=FALSE, warning=TRUE, include=FALSE}
library(car)
library(plyr)
library(foreign)
library(pscl)
library(boot)
library(MASS)
library(robust)
library(sfsmisc)
library(ggplot2)
library(reshape2)
library(ppcor)
library(ggrepel)
library(Hmisc)
library(tidyverse)
library(sandwich)
library(ggpubr)
library(interactions)
library(knitr)
library(twowaytests)
library(ggfortify)
library(interactions)
library(broom)
library(patchwork)
library(robustbase)
library(lmtest)
library(modelr)
library(Rmisc)
# library(raincloudplots)
library(cowplot)
library(readr)
library(PupillometryR)
library(ggpp)
library(estimatr)
library(skedastic)
library(ggpubr)
library(lubridate)
library(readxl)
library(gridExtra)
library(scales)
library(rstudioapi)
library(jsonlite)
library(rjson)
library(readr)
library(hBayesDM)
library(brms)
library(emmeans)
library(mediation)
library(here)
library(lme4)
library(broom.mixed)
library(easyRT)
library(parameters)
library(effectsize)
library(effects)
library(lmerTest)
library(ez)
library(afex)
library(marginaleffects)
```

```{r}
set.seed(123)
```

# load tsv and prolific raw data
```{r}
gitrepo_path = "/Users/momocco/Documents/GitHub/srndna-ug/behavioral_analyses"

data_dir = paste(gitrepo_path,"data", sep = "/")
codes_dir = paste(gitrepo_path, "codes", sep = "/")
fit_dir = paste(gitrepo_path,"fits", sep = "/")
figure_dir = paste(gitrepo_path,"figures", sep = "/")
```

# load and prepare data
```{r}
# load subs
all_trials_df = read.csv(paste(data_dir, "all_trials_brains.csv", sep = "/"), header = TRUE) %>% 
  .[.$missed == 0,]

colnames(all_trials_df)[colnames(all_trials_df) == "subjID"] <- "participant_id"
indiv_df = read.csv(paste(data_dir, "participant_check.csv", sep = "/"), header = TRUE)  %>%
  mutate(age_bi = case_when(age <= 36 ~ "younger",
                            age > 36 ~ "older"))

all_trials_df = merge(all_trials_df, indiv_df, by.x = "participant_id", by.y = "participant_id")

sublist_final = read.csv(paste(data_dir, "participant_L3_47.csv", sep = "/"), header = TRUE)

all_trials_df = all_trials_df[all_trials_df$participant_id %in% sublist_final$subjID,]
```


```{r}
## add a categorical variable that differentiate three groups
all_trials_df = all_trials_df %>% 
  mutate(group_tri = as.factor(case_when(human == 0 ~ 0, # computer
                               human == 1 & ingroup == 0 ~ 1, # outgroup
                               human == 1 & ingroup == 1 ~ 2))) # ingroup
# all_trials_df$group_tri = relevel(all_trials_df$group_tri, ref = "0") # computer

all_trials_df = all_trials_df %>% mutate(human = as.factor(human))

all_trials_df$group_tri = relevel(all_trials_df$group_tri, ref = "1") # outgroup

all_trials_df$age_bi = relevel(as.factor(all_trials_df$age_bi), ref = "younger")

all_trials_df = all_trials_df %>% 
  mutate(age_bi_dummy = case_when(age_bi == "younger" ~ 0,
                                  age_bi == "older" ~ 1)
         )
```

## add fdmean, tsnr vars to data
```{r}
fmri_control_data = 
  read.csv(paste(data_dir, "Task-ultimatum_Level-Run_Outlier-info.csv", 
                 sep = "/"), header = TRUE) %>% 
  filter(Sub %in% sublist_final$subjID == 1) %>% 
  # mutate(subjID = Sub) %>% 
  select(-task, -outlier_run_Custom1)

all_trials_df = merge(all_trials_df, fmri_control_data, 
                      by.x = c("participant_id", "run"),
                      by.y = c("Sub", "run"))
```

# prereg 2 single trial analyses
## P2 BH3
BH3) Acceptance rates for an individual offer will vary according to its consistency with other offers in a given block rather than the objective dollar amount of the offer. That is, there will be an offer amount by block interaction, such that acceptance of higher, unfair offers will be greater in unfair blocks, and acceptance of lower, fair offers will be lower in fair blocks, as opposed to participants always rejecting unfair offers and always accepting fair offers.
```{r}
## full model, won't converge
# model_P2_3_fit <- glmer(accept ~ offer * group_tri * age_bi * block_fair +
#                      (1|participant_id),
#                             data = all_trials_df,
#                             family = binomial)

## won't converge
# model_P2_3_fit <- glmer(
#   accept ~ offer * group_tri * age_bi * block_fair - offer:group_tri:age_bi:block_fair +
#                      (1|participant_id),
#                             data = all_trials_df,
#                             family = binomial)

## won't converge
# model_P2_3_fit <- glmer(accept ~ offer * age_bi * block_fair + group_tri +
#                      (1|participant_id),
#                             data = all_trials_df,
#                             family = binomial)

## won't converge
# model_P2_3_fit <- glmer(accept ~ offer * age_bi * block_fair + group_tri * block_fair +
#                      (1|participant_id),
#                             data = all_trials_df,
#                             family = binomial)

## converged, block main sig
model_P2_3_fit <- glmer(accept ~ offer * age_bi * block_fair + group_tri -
                          offer:age_bi:block_fair +
                     (1|participant_id),
                            data = all_trials_df,
                            family = binomial)


summary(model_P2_3_fit)

block_effect<-Effect("block_fair", model_P2_3_fit)
data.frame(block_effect)
avg_slopes(model=model_P2_3_fit,re.form=NA)

## further simplified model based on sig above, all unnecessary non-sig removed
model_P2_31_fit <- glmer(accept ~ offer * age_bi + block_fair +
                     (1|participant_id),
                            data = all_trials_df,
                            family = binomial)

summary(model_P2_31_fit)

block_effect<-Effect("block_fair", model_P2_31_fit)
data.frame(block_effect)
avg_slopes(model=model_P2_31_fit,re.form=NA)
```

## P2 NH1A, group_tri & age_bi respectively
"NH1A) The anterior insula (ins), dorsal anterior cingulate cortex (dACC), ventromedial prefrontal cortex (vmPFC), and ventral striatum (VS) will be associated with choice." [ins, dACC, vmPFC, VS]

accept ~ brain * age(or group) + (1|participant)

### prepare empty df to store results
```{r}
results_cols = c("brain", "mod", "Coef", "p", "p_check", "p_0125_check")
results_df = data.frame(matrix(nrow = 4*(3+1), ncol = length(results_cols)))
colnames(results_df) = results_cols
```

### anterior insula * age, strict prereg, not sig
```{r}
## converge, no interaction
model_P2_NH1_antIns_age_fit = glmer(accept ~ anteriorinsula_corrected * age_bi +
                     (1|participant_id), 
                     data = all_trials_df,
                            family = binomial)
summary(model_P2_NH1_antIns_age_fit)

m_params = model_parameters(model_P2_NH1_antIns_age_fit, effects = "fixed")

N_nonNA_results = sum(!is.na(results_df$brain))
results_df$brain[N_nonNA_results+1] = m_params$Parameter[2]
results_df$mod[N_nonNA_results+1] = m_params$Parameter[3]
results_df$p[N_nonNA_results+1] = m_params$p[4]
results_df$Coef[N_nonNA_results+1] = m_params$Coefficient[4]
```

### anterior insula * group, strict prereg, sig
```{r}
## converge, no interaction
model_P2_NH1_antIns_group_fit = glmer(accept ~ anteriorinsula_corrected * group_tri +
                                      (1|participant_id), 
                                    data = all_trials_df,
                                    family = binomial)
summary(model_P2_NH1_antIns_group_fit)

m_params = model_parameters(model_P2_NH1_antIns_group_fit, effects = "fixed")

N_nonNA_results = sum(!is.na(results_df$brain))
results_df$brain[N_nonNA_results+1] = m_params$Parameter[2]
results_df$mod[N_nonNA_results+1] = m_params$Parameter[3]
results_df$p[N_nonNA_results+1] = m_params$p[5]
results_df$Coef[N_nonNA_results+1] = m_params$Coefficient[5]

N_nonNA_results = sum(!is.na(results_df$brain))
results_df$brain[N_nonNA_results+1] = m_params$Parameter[2]
results_df$mod[N_nonNA_results+1] = m_params$Parameter[4]
results_df$p[N_nonNA_results+1] = m_params$p[6]
results_df$Coef[N_nonNA_results+1] = m_params$Coefficient[6]
```

### ant insula main, strict prereg, not sig
```{r}
## converged, no sig vmpfc_corrected * age_bi
model_P2_NH1_antIns_main_fit <- glmer(accept ~ anteriorinsula_corrected +
                                      (1|participant_id),
                                    data = all_trials_df,
                                    family = binomial)
summary(model_P2_NH1_antIns_main_fit)

m_params = model_parameters(model_P2_NH1_antIns_main_fit, effects = "fixed")

N_nonNA_results = sum(!is.na(results_df$brain))
results_df$brain[N_nonNA_results+1] = m_params$Parameter[2]
results_df$mod[N_nonNA_results+1] = "main"
results_df$p[N_nonNA_results+1] = m_params$p[2]
results_df$Coef[N_nonNA_results+1] = m_params$Coefficient[2]
```

### dacc * age, strict prereg
```{r}
## converged, no sig dacc_corrected * age_bi
model_P2_NH1_dacc_age_fit <- glmer(accept ~ dacc_corrected * age_bi +
                                     (1|participant_id),
                            data = all_trials_df,
                            family = binomial)
summary(model_P2_NH1_dacc_age_fit)

m_params = model_parameters(model_P2_NH1_dacc_age_fit, effects = "fixed")

N_nonNA_results = sum(!is.na(results_df$brain))
results_df$brain[N_nonNA_results+1] = m_params$Parameter[2]
results_df$mod[N_nonNA_results+1] = m_params$Parameter[3]
results_df$p[N_nonNA_results+1] = m_params$p[4]
results_df$Coef[N_nonNA_results+1] = m_params$Coefficient[4]
```

### dacc * group, strict prereg, not sig
```{r}
## converged, no sig dacc_corrected * age_bi
model_P2_NH1_dacc_group_fit <- glmer(accept ~ dacc_corrected * group_tri +
                                     (1|participant_id),
                            data = all_trials_df,
                            family = binomial)
summary(model_P2_NH1_dacc_group_fit)

m_params = model_parameters(model_P2_NH1_dacc_group_fit, effects = "fixed")

N_nonNA_results = sum(!is.na(results_df$brain))
results_df$brain[N_nonNA_results+1] = m_params$Parameter[2]
results_df$mod[N_nonNA_results+1] = m_params$Parameter[3]
results_df$p[N_nonNA_results+1] = m_params$p[5]
results_df$Coef[N_nonNA_results+1] = m_params$Coefficient[5]

N_nonNA_results = sum(!is.na(results_df$brain))
results_df$brain[N_nonNA_results+1] = m_params$Parameter[2]
results_df$mod[N_nonNA_results+1] = m_params$Parameter[4]
results_df$p[N_nonNA_results+1] = m_params$p[6]
results_df$Coef[N_nonNA_results+1] = m_params$Coefficient[6]
```

### dacc main, strict prereg, not sig
```{r}
## converged, no sig dacc_corrected * age_bi
model_P2_NH1_dacc_main_fit <- glmer(accept ~ dacc_corrected +
                                     (1|participant_id),
                            data = all_trials_df,
                            family = binomial)
summary(model_P2_NH1_dacc_main_fit)

m_params = model_parameters(model_P2_NH1_dacc_main_fit, effects = "fixed")

N_nonNA_results = sum(!is.na(results_df$brain))
results_df$brain[N_nonNA_results+1] = m_params$Parameter[2]
results_df$mod[N_nonNA_results+1] = "main"
results_df$p[N_nonNA_results+1] = m_params$p[2]
results_df$Coef[N_nonNA_results+1] = m_params$Coefficient[2]
```

### VS * age, strict prereg, sig, not sig after correction
```{r}
## converged, no sig VS_corrected * age_bi
model_P2_NH1_VS_age_fit <- glmer(accept ~ VS_corrected * age_bi +
                                     (1|participant_id),
                                   data = all_trials_df,
                                   family = binomial)
summary(model_P2_NH1_VS_age_fit)

m_params = model_parameters(model_P2_NH1_VS_age_fit, effects = "fixed")

N_nonNA_results = sum(!is.na(results_df$brain))
results_df$brain[N_nonNA_results+1] = m_params$Parameter[2]
results_df$mod[N_nonNA_results+1] = m_params$Parameter[3]
results_df$p[N_nonNA_results+1] = m_params$p[4]
results_df$Coef[N_nonNA_results+1] = m_params$Coefficient[4]
```

### VS * group, strict prereg, sig
```{r}
## converged, no sig VS_corrected * age_bi
model_P2_NH1_VS_group_fit <- glmer(accept ~ VS_corrected * group_tri +
                                       (1|participant_id),
                                     data = all_trials_df,
                                     family = binomial)
summary(model_P2_NH1_VS_group_fit)

m_params = model_parameters(model_P2_NH1_VS_group_fit, effects = "fixed")

N_nonNA_results = sum(!is.na(results_df$brain))
results_df$brain[N_nonNA_results+1] = m_params$Parameter[2]
results_df$mod[N_nonNA_results+1] = m_params$Parameter[3]
results_df$p[N_nonNA_results+1] = m_params$p[5]
results_df$Coef[N_nonNA_results+1] = m_params$Coefficient[5]

N_nonNA_results = sum(!is.na(results_df$brain))
results_df$brain[N_nonNA_results+1] = m_params$Parameter[2]
results_df$mod[N_nonNA_results+1] = m_params$Parameter[4]
results_df$p[N_nonNA_results+1] = m_params$p[6]
results_df$Coef[N_nonNA_results+1] = m_params$Coefficient[6]
```

### VS main, strict prereg, sig
```{r}
## converged, no sig VS_corrected * age_bi
model_P2_NH1_VS_main_fit <- glmer(accept ~ VS_corrected +
                                      (1|participant_id),
                                    data = all_trials_df,
                                    family = binomial)
summary(model_P2_NH1_VS_main_fit)

m_params = model_parameters(model_P2_NH1_VS_main_fit, effects = "fixed")

N_nonNA_results = sum(!is.na(results_df$brain))
results_df$brain[N_nonNA_results+1] = m_params$Parameter[2]
results_df$mod[N_nonNA_results+1] = "main"
results_df$p[N_nonNA_results+1] = m_params$p[2]
results_df$Coef[N_nonNA_results+1] = m_params$Coefficient[2]
```

### vmpfc * age, strict prereg, sig
```{r}
## converged, no sig vmpfc_corrected * age_bi
model_P2_NH1_vmpfc_age_fit <- glmer(accept ~ vmpfc_corrected * age_bi +
                                     (1|participant_id),
                                   data = all_trials_df,
                                   family = binomial)
summary(model_P2_NH1_vmpfc_age_fit)

m_params = model_parameters(model_P2_NH1_vmpfc_age_fit, effects = "fixed")

N_nonNA_results = sum(!is.na(results_df$brain))
results_df$brain[N_nonNA_results+1] = m_params$Parameter[2]
results_df$mod[N_nonNA_results+1] = m_params$Parameter[3]
results_df$p[N_nonNA_results+1] = m_params$p[4]
results_df$Coef[N_nonNA_results+1] = m_params$Coefficient[4]
```

### vmpfc * group, strict prereg, not sig
```{r}
## converged, no sig vmpfc_corrected * age_bi
model_P2_NH1_vmpfc_group_fit <- glmer(accept ~ vmpfc_corrected * group_tri +
                                       (1|participant_id),
                                     data = all_trials_df,
                                     family = binomial)
summary(model_P2_NH1_vmpfc_group_fit)

m_params = model_parameters(model_P2_NH1_vmpfc_group_fit, effects = "fixed")

N_nonNA_results = sum(!is.na(results_df$brain))
results_df$brain[N_nonNA_results+1] = m_params$Parameter[2]
results_df$mod[N_nonNA_results+1] = m_params$Parameter[3]
results_df$p[N_nonNA_results+1] = m_params$p[5]
results_df$Coef[N_nonNA_results+1] = m_params$Coefficient[5]

N_nonNA_results = sum(!is.na(results_df$brain))
results_df$brain[N_nonNA_results+1] = m_params$Parameter[2]
results_df$mod[N_nonNA_results+1] = m_params$Parameter[4]
results_df$p[N_nonNA_results+1] = m_params$p[6]
results_df$Coef[N_nonNA_results+1] = m_params$Coefficient[6]
```

### vmpfc main, strict prereg, not sig
```{r}
## converged, no sig vmpfc_corrected * age_bi
model_P2_NH1_vmpfc_main_fit <- glmer(accept ~ vmpfc_corrected +
                                      (1|participant_id),
                                    data = all_trials_df,
                                    family = binomial)
summary(model_P2_NH1_vmpfc_main_fit)

m_params = model_parameters(model_P2_NH1_vmpfc_main_fit, effects = "fixed")

N_nonNA_results = sum(!is.na(results_df$brain))
results_df$brain[N_nonNA_results+1] = m_params$Parameter[2]
results_df$mod[N_nonNA_results+1] = "main"
results_df$p[N_nonNA_results+1] = m_params$p[2]
results_df$Coef[N_nonNA_results+1] = m_params$Coefficient[2]
```


### clean single trial results
```{r}
results_df = results_df %>% 
  mutate(p_check = case_when(p >=0.05 ~ NA,
                                p < 0.05 ~ "*" ),
         p_0125_check = case_when(p >=0.0125 ~ NA,
                                p < 0.0125 ~ "*"),
         p = round(p,4))
```


## P2 NH1A, human vs computer
"NH1A) The anterior insula (ins), dorsal anterior cingulate cortex (dACC), ventromedial prefrontal cortex (vmPFC), and ventral striatum (VS) will be associated with choice." [ins, dACC, vmPFC, VS]

accept ~ brain * age(or group) + (1|participant)

### prepare empty df to store results
```{r}
results_cols = c("brain", "mod", "Coef", "p", "p_check", "p_0125_check")
results_df = data.frame(matrix(nrow = 4*(3+1), ncol = length(results_cols)))
colnames(results_df) = results_cols
```

### anterior insula * age, strict prereg, not sig
```{r}
## converge, no interaction
model_P2_NH1_antIns_age_fit = glmer(accept ~ anteriorinsula_corrected * age_bi +
                                      (1|participant_id), 
                                    data = all_trials_df,
                                    family = binomial)
summary(model_P2_NH1_antIns_age_fit)

m_params = model_parameters(model_P2_NH1_antIns_age_fit, effects = "fixed")

N_nonNA_results = sum(!is.na(results_df$brain))
results_df$brain[N_nonNA_results+1] = m_params$Parameter[2]
results_df$mod[N_nonNA_results+1] = m_params$Parameter[3]
results_df$p[N_nonNA_results+1] = m_params$p[4]
results_df$Coef[N_nonNA_results+1] = m_params$Coefficient[4]
```

### anterior insula * group, strict prereg, sig
```{r}
## converge, no interaction
model_P2_NH1_antIns_group_fit = glmer(accept ~ anteriorinsula_corrected * human +
                                        (1|participant_id), 
                                      data = all_trials_df,
                                      family = binomial)
summary(model_P2_NH1_antIns_group_fit)

m_params = model_parameters(model_P2_NH1_antIns_group_fit, effects = "fixed")

N_nonNA_results = sum(!is.na(results_df$brain))
results_df$brain[N_nonNA_results+1] = m_params$Parameter[2]
results_df$mod[N_nonNA_results+1] = m_params$Parameter[3]
results_df$p[N_nonNA_results+1] = m_params$p[4]
results_df$Coef[N_nonNA_results+1] = m_params$Coefficient[4]
```

### ant insula main, strict prereg, not sig
```{r}
## converged, no sig vmpfc_corrected * age_bi
model_P2_NH1_antIns_main_fit <- glmer(accept ~ anteriorinsula_corrected +
                                        (1|participant_id),
                                      data = all_trials_df,
                                      family = binomial)
summary(model_P2_NH1_antIns_main_fit)

m_params = model_parameters(model_P2_NH1_antIns_main_fit, effects = "fixed")

N_nonNA_results = sum(!is.na(results_df$brain))
results_df$brain[N_nonNA_results+1] = m_params$Parameter[2]
results_df$mod[N_nonNA_results+1] = "main"
results_df$p[N_nonNA_results+1] = m_params$p[2]
results_df$Coef[N_nonNA_results+1] = m_params$Coefficient[2]
```

### dacc * age, strict prereg
```{r}
## converged, no sig dacc_corrected * age_bi
model_P2_NH1_dacc_age_fit <- glmer(accept ~ dacc_corrected * age_bi +
                                     (1|participant_id),
                                   data = all_trials_df,
                                   family = binomial)
summary(model_P2_NH1_dacc_age_fit)

m_params = model_parameters(model_P2_NH1_dacc_age_fit, effects = "fixed")

N_nonNA_results = sum(!is.na(results_df$brain))
results_df$brain[N_nonNA_results+1] = m_params$Parameter[2]
results_df$mod[N_nonNA_results+1] = m_params$Parameter[3]
results_df$p[N_nonNA_results+1] = m_params$p[4]
results_df$Coef[N_nonNA_results+1] = m_params$Coefficient[4]
```

### dacc * group, strict prereg, not sig
```{r}
## converged, no sig dacc_corrected * age_bi
model_P2_NH1_dacc_group_fit <- glmer(accept ~ dacc_corrected * human +
                                       (1|participant_id),
                                     data = all_trials_df,
                                     family = binomial)
summary(model_P2_NH1_dacc_group_fit)

m_params = model_parameters(model_P2_NH1_dacc_group_fit, effects = "fixed")

N_nonNA_results = sum(!is.na(results_df$brain))
results_df$brain[N_nonNA_results+1] = m_params$Parameter[2]
results_df$mod[N_nonNA_results+1] = m_params$Parameter[3]
results_df$p[N_nonNA_results+1] = m_params$p[4]
results_df$Coef[N_nonNA_results+1] = m_params$Coefficient[4]
```

### dacc main, strict prereg, not sig
```{r}
## converged, no sig dacc_corrected * age_bi
model_P2_NH1_dacc_main_fit <- glmer(accept ~ dacc_corrected +
                                      (1|participant_id),
                                    data = all_trials_df,
                                    family = binomial)
summary(model_P2_NH1_dacc_main_fit)

m_params = model_parameters(model_P2_NH1_dacc_main_fit, effects = "fixed")

N_nonNA_results = sum(!is.na(results_df$brain))
results_df$brain[N_nonNA_results+1] = m_params$Parameter[2]
results_df$mod[N_nonNA_results+1] = "main"
results_df$p[N_nonNA_results+1] = m_params$p[2]
results_df$Coef[N_nonNA_results+1] = m_params$Coefficient[2]
```

### VS * age, strict prereg, sig, not sig after correction
```{r}
## converged, no sig VS_corrected * age_bi
model_P2_NH1_VS_age_fit <- glmer(accept ~ VS_corrected * age_bi +
                                   (1|participant_id),
                                 data = all_trials_df,
                                 family = binomial)
summary(model_P2_NH1_VS_age_fit)

m_params = model_parameters(model_P2_NH1_VS_age_fit, effects = "fixed")

N_nonNA_results = sum(!is.na(results_df$brain))
results_df$brain[N_nonNA_results+1] = m_params$Parameter[2]
results_df$mod[N_nonNA_results+1] = m_params$Parameter[3]
results_df$p[N_nonNA_results+1] = m_params$p[4]
results_df$Coef[N_nonNA_results+1] = m_params$Coefficient[4]
```

### VS * group, strict prereg, sig
```{r}
## converged, no sig VS_corrected * age_bi
model_P2_NH1_VS_group_fit <- glmer(accept ~ VS_corrected * human +
                                     (1|participant_id),
                                   data = all_trials_df,
                                   family = binomial)
summary(model_P2_NH1_VS_group_fit)

m_params = model_parameters(model_P2_NH1_VS_group_fit, effects = "fixed")

N_nonNA_results = sum(!is.na(results_df$brain))
results_df$brain[N_nonNA_results+1] = m_params$Parameter[2]
results_df$mod[N_nonNA_results+1] = m_params$Parameter[3]
results_df$p[N_nonNA_results+1] = m_params$p[4]
results_df$Coef[N_nonNA_results+1] = m_params$Coefficient[4]
```

### VS main, strict prereg, sig
```{r}
## converged, no sig VS_corrected * age_bi
model_P2_NH1_VS_main_fit <- glmer(accept ~ VS_corrected +
                                    (1|participant_id),
                                  data = all_trials_df,
                                  family = binomial)
summary(model_P2_NH1_VS_main_fit)

m_params = model_parameters(model_P2_NH1_VS_main_fit, effects = "fixed")

N_nonNA_results = sum(!is.na(results_df$brain))
results_df$brain[N_nonNA_results+1] = m_params$Parameter[2]
results_df$mod[N_nonNA_results+1] = "main"
results_df$p[N_nonNA_results+1] = m_params$p[2]
results_df$Coef[N_nonNA_results+1] = m_params$Coefficient[2]
```

### vmpfc * age, strict prereg, sig
```{r}
## converged, no sig vmpfc_corrected * age_bi
model_P2_NH1_vmpfc_age_fit <- glmer(accept ~ vmpfc_corrected * age_bi +
                                      (1|participant_id),
                                    data = all_trials_df,
                                    family = binomial)
summary(model_P2_NH1_vmpfc_age_fit)

m_params = model_parameters(model_P2_NH1_vmpfc_age_fit, effects = "fixed")

N_nonNA_results = sum(!is.na(results_df$brain))
results_df$brain[N_nonNA_results+1] = m_params$Parameter[2]
results_df$mod[N_nonNA_results+1] = m_params$Parameter[3]
results_df$p[N_nonNA_results+1] = m_params$p[4]
results_df$Coef[N_nonNA_results+1] = m_params$Coefficient[4]
```

### vmpfc * group, strict prereg, not sig
```{r}
## converged, no sig vmpfc_corrected * age_bi
model_P2_NH1_vmpfc_group_fit <- glmer(accept ~ vmpfc_corrected * human +
                                        (1|participant_id),
                                      data = all_trials_df,
                                      family = binomial)
summary(model_P2_NH1_vmpfc_group_fit)

m_params = model_parameters(model_P2_NH1_vmpfc_group_fit, effects = "fixed")

N_nonNA_results = sum(!is.na(results_df$brain))
results_df$brain[N_nonNA_results+1] = m_params$Parameter[2]
results_df$mod[N_nonNA_results+1] = m_params$Parameter[3]
results_df$p[N_nonNA_results+1] = m_params$p[4]
results_df$Coef[N_nonNA_results+1] = m_params$Coefficient[4]
```

### vmpfc main, strict prereg, not sig
```{r}
## converged, no sig vmpfc_corrected * age_bi
model_P2_NH1_vmpfc_main_fit <- glmer(accept ~ vmpfc_corrected +
                                       (1|participant_id),
                                     data = all_trials_df,
                                     family = binomial)
summary(model_P2_NH1_vmpfc_main_fit)

m_params = model_parameters(model_P2_NH1_vmpfc_main_fit, effects = "fixed")

N_nonNA_results = sum(!is.na(results_df$brain))
results_df$brain[N_nonNA_results+1] = m_params$Parameter[2]
results_df$mod[N_nonNA_results+1] = "main"
results_df$p[N_nonNA_results+1] = m_params$p[2]
results_df$Coef[N_nonNA_results+1] = m_params$Coefficient[2]
```


### clean single trial results
```{r}
results_df = results_df %>% 
  mutate(p_check = case_when(p >=0.05 ~ NA,
                             p < 0.05 ~ "*" ),
         p_0125_check = case_when(p >=0.0125 ~ NA,
                                  p < 0.0125 ~ "*"),
         p = round(p,4))
```

# single trial exploratory
## accept ~ brain * block
```{r}
## not sig
antIns_block_fit <- glmer(accept ~ anteriorinsula_corrected * block_fair +
                                        (1|participant_id),
                                      data = all_trials_df,
                                      family = binomial)
summary(antIns_block_fit)

#@ not sig
VS_block_fit <- glmer(accept ~ VS_corrected * block_fair +
                                        (1|participant_id),
                                      data = all_trials_df,
                                      family = binomial)
summary(VS_block_fit)

## not sig
dacc_block_fit <- glmer(accept ~ dacc_corrected * block_fair +
                                        (1|participant_id),
                                      data = all_trials_df,
                                      family = binomial)
summary(dacc_block_fit)

## not sig
vmpfc_block_fit <- glmer(accept ~ vmpfc_corrected * block_fair +
                                        (1|participant_id),
                                      data = all_trials_df,
                                      family = binomial)
summary(vmpfc_block_fit)
```

## brain ~ offer + group + block + accept
```{r}
# vmpfc_task_fit <- lmer(vmpfc_corrected ~ (1 |participant_id),
#                                       data = all_trials_df)
# summary(vmpfc_task_fit)
vmpfc_task_fit <- lm(vmpfc_corrected ~ offer + block_fair + accept + group_tri + age_bi,
                                      data = all_trials_df)
summary(vmpfc_task_fit)


# VS_task_fit <- lmer(VS_corrected ~ (1 |participant_id),
#                                       data = all_trials_df)
# summary(VS_task_fit)
VS_task_fit <- lm(VS_corrected ~ offer + block_fair + accept + group_tri + age_bi,
                                      data = all_trials_df)
summary(VS_task_fit)

# anteriorinsula_task_fit <- lmer(anteriorinsula_corrected ~ (1 |participant_id),
#                                       data = all_trials_df)
# summary(anteriorinsula_task_fit)
anteriorinsula_task_fit <- lm(anteriorinsula_corrected ~ offer + block_fair + accept + group_tri + age_bi,
                  data = all_trials_df)
summary(anteriorinsula_task_fit)

# dacc_task_fit <- lmer(dacc_corrected ~ (1 |participant_id),
#                                       data = all_trials_df)
# summary(dacc_task_fit)
dacc_task_fit <- lm(dacc_corrected ~ offer + block_fair + accept + group_tri + age_bi,
                  data = all_trials_df)
summary(dacc_task_fit)
```


```{r}
dacc_vmpfc_fit = lm(dacc_corrected ~ vmpfc_corrected * age_bi,
                  data = all_trials_df)
summary(dacc_vmpfc_fit)

VS_vmpfc_fit = lm(VS_corrected ~ vmpfc_corrected * age_bi,
                  data = all_trials_df)
summary(VS_vmpfc_fit)

anteriorinsula_vmpfc_fit = lm(anteriorinsula_corrected ~ vmpfc_corrected * age_bi,
                  data = all_trials_df)
summary(anteriorinsula_vmpfc_fit)

anteriorinsula_VS_fit = lm(anteriorinsula_corrected ~ VS_corrected * age_bi,
                  data = all_trials_df)
summary(anteriorinsula_VS_fit)

anteriorinsula_dacc_fit = lm(anteriorinsula_corrected ~ dacc_corrected * age_bi,
                  data = all_trials_df)
summary(anteriorinsula_dacc_fit)

VS_dacc_fit = lm(VS_corrected ~ dacc_corrected * age_bi,
                  data = all_trials_df)
summary(VS_dacc_fit)
```








## if brain contribute above behavior model
### base behavior model
```{r}
all_trials_df = na.omit(all_trials_df)

beh_full_fit = glmer(accept ~ offer * age_bi + block_fair + 
                                       (1|participant_id),
                                     data = all_trials_df,
                                     family = binomial)

summary(beh_full_fit)
```
### prepare empty df for results
```{r}
# brain_behavior_formula_cols = c("brain", "formula", "chisq_p", "sig_check")
# brain_behavior_formula_df = data.frame(matrix(nrow = 4, ncol = length(brain_behavior_formula_cols)))
# colnames(brain_behavior_formula_df) = brain_behavior_formula_cols

brain_behavior_cols = c("brain", "predictor", "pre_p", "pre_sig", "model_p", "model_sig")
brain_behavior_df = data.frame(matrix(nrow = 4, ncol = length(brain_behavior_cols)))
colnames(brain_behavior_df) = brain_behavior_cols
```

### VS,offer sig
```{r}
## full model, converged
# beh_VS_full_0_fit = glmer(accept ~ offer * age_bi + block_fair + 
#                             VS_corrected * offer * age_bi + 
#                             VS_corrected * block_fair +
#                             (1|participant_id),
#                           data = all_trials_df,
#                           family = binomial)
# 
# summary(beh_VS_full_0_fit)

## reduced model, no 3-way interaction
# beh_VS_full_1_fit = glmer(accept ~ offer * age_bi + block_fair + 
#                             VS_corrected * offer * age_bi -
#                             VS_corrected:offer:age_bi +
#                             VS_corrected * block_fair +
#                             (1|participant_id),
#                           data = all_trials_df,
#                           family = binomial)
# summary(beh_VS_full_1_fit)

## no diff in fit quality between full and reduced model. use reduced model for later comparison
# anova(beh_VS_full_0_fit, beh_VS_full_1_fit, refit = T)

## reduced model, brain * age
beh_VS_full_2_fit = glmer(accept ~ offer * age_bi + block_fair + 
                            VS_corrected * age_bi +
                            (1|participant_id),
                          data = all_trials_df,
                          family = binomial)
summary(beh_VS_full_2_fit)

anova_predictor_test = data.frame(Anova(beh_VS_full_2_fit))
anova_model_test = data.frame(anova(beh_full_fit, beh_VS_full_2_fit, refit = TRUE))

N_nonNA_results = sum(!is.na(brain_behavior_df$brain))
brain_name = "VS_corrected"

predictor_name = paste("age_bi", brain_name, sep = ":")
brain_behavior_df$brain[N_nonNA_results+1] = brain_name
brain_behavior_df$predictor[N_nonNA_results+1] = predictor_name

brain_behavior_df$pre_p[N_nonNA_results+1] = 
  anova_predictor_test$Pr..Chisq.[row.names(anova_predictor_test) == predictor_name]

brain_behavior_df$model_p[N_nonNA_results+1] = 
  anova_model_test$Pr..Chisq.[2]
```
### dacc, not sig but close
```{r}
# beh_dacc_full_0_fit = glmer(accept ~ offer * age_bi + block_fair + 
#                           dacc_corrected * offer * age_bi + dacc_corrected * block_fair +
#                           (1|participant_id),
#                         data = all_trials_df,
#                         family = binomial)
# 
# summary(beh_dacc_full_0_fit)

# beh_dacc_full_1_fit = glmer(accept ~ offer * age_bi + block_fair + 
#                           dacc_corrected * offer * age_bi - 
#                             dacc_corrected:offer:age_bi +
#                             dacc_corrected * block_fair +
#                           (1|participant_id),
#                         data = all_trials_df,
#                         family = binomial)

beh_dacc_full_2_fit = glmer(accept ~ offer * age_bi + block_fair +
                          dacc_corrected * age_bi +
                          (1|participant_id),
                        data = all_trials_df,
                        family = binomial)
summary(beh_dacc_full_2_fit)

anova_predictor_test = data.frame(Anova(beh_dacc_full_2_fit))
anova_model_test = data.frame(anova(beh_full_fit, beh_dacc_full_2_fit, refit = TRUE))

N_nonNA_results = sum(!is.na(brain_behavior_df$brain))
brain_name = "dacc_corrected"

predictor_name = paste("age_bi", brain_name, sep = ":")
brain_behavior_df$brain[N_nonNA_results+1] = brain_name
brain_behavior_df$predictor[N_nonNA_results+1] = predictor_name

brain_behavior_df$pre_p[N_nonNA_results+1] = 
  anova_predictor_test$Pr..Chisq.[row.names(anova_predictor_test) == predictor_name]

brain_behavior_df$model_p[N_nonNA_results+1] = 
  anova_model_test$Pr..Chisq.[2]
```

### vmpfc, not sig
```{r}
# beh_vmpfc_full_0_fit = glmer(accept ~ offer * age_bi + block_fair + 
#                             vmpfc_corrected * offer * age_bi + vmpfc_corrected * block_fair +
#                             (1|participant_id),
#                           data = all_trials_df,
#                           family = binomial)
# 
# summary(beh_vmpfc_full_0_fit)

# beh_vmpfc_full_1_fit = glmer(accept ~ offer * age_bi + block_fair + 
#                             vmpfc_corrected * offer * age_bi - 
#                               vmpfc_corrected:offer:age_bi +
#                               vmpfc_corrected * block_fair +
#                             (1|participant_id),
#                           data = all_trials_df,
#                           family = binomial)

beh_vmpfc_full_2_fit = glmer(accept ~ offer * age_bi + block_fair + 
                            vmpfc_corrected * age_bi - 
                            (1|participant_id),
                          data = all_trials_df,
                          family = binomial)

anova_predictor_test = data.frame(Anova(beh_vmpfc_full_2_fit))
anova_model_test = data.frame(anova(beh_full_fit, beh_vmpfc_full_2_fit, refit = TRUE))

N_nonNA_results = sum(!is.na(brain_behavior_df$brain))
brain_name = "vmpfc_corrected"

predictor_name = paste("age_bi", brain_name, sep = ":")
brain_behavior_df$brain[N_nonNA_results+1] = brain_name
brain_behavior_df$predictor[N_nonNA_results+1] = predictor_name

brain_behavior_df$pre_p[N_nonNA_results+1] = 
  anova_predictor_test$Pr..Chisq.[row.names(anova_predictor_test) == predictor_name]

brain_behavior_df$model_p[N_nonNA_results+1] = 
  anova_model_test$Pr..Chisq.[2]
```

### mark sig results
```{r}
brain_behavior_df = brain_behavior_df %>% 
  mutate(pre_sig = case_when(pre_p >=0.05 ~ NA,
                             pre_p < 0.05 ~ "*"),
         model_sig = case_when(model_p >=0.05 ~ NA,
                    model_p < 0.05 ~ "*"))
```


### anteriorinsula_corrected, very sig
```{r}
## full model won't converge
# beh_antIns_full_0_fit = glmer(accept ~ 
#                             anteriorinsula_corrected * offer * age_bi +
#                               anteriorinsula_corrected * block_fair +
#                             (1|participant_id),
#                           data = all_trials_df,
#                           family = binomial)
# allFit(beh_antIns_full_0_fit)

## reduced model based on purpose of test - see potentional interactions between brain and other non-brain factors
# beh_antIns_full_1_fit = glmer(accept ~ offer * age_bi + block_fair + 
#                             anteriorinsula_corrected * offer * age_bi -
#                               anteriorinsula_corrected:offer:age_bi +
#                               anteriorinsula_corrected * block_fair +
#                             (1|participant_id),
#                           data = all_trials_df,
#                           family = binomial)
# summary(beh_antIns_full_1_fit)

###### to delete ###### 
# temp_m = glmer(anteriorinsula_corrected ~ offer * age_bi * block_fair * group_tri +
#                             (1|participant_id),
#                           data = all_trials_df,
#                           family = binomial)
###### ###### ###### ###### 

beh_antIns_full_2_fit = glmer(accept ~ offer * age_bi + block_fair +
                            anteriorinsula_corrected * age_bi -
                            (1|participant_id),
                          data = all_trials_df,
                          family = binomial)
# summary(beh_antIns_full_2_fit)

anova_predictor_test = data.frame(Anova(beh_antIns_full_2_fit))
anova_model_test = data.frame(anova(beh_full_fit, beh_antIns_full_2_fit, refit = TRUE))

N_nonNA_results = sum(!is.na(brain_behavior_df$brain))
brain_name = "anteriorinsula_corrected"

predictor_name = paste("age_bi", brain_name, sep = ":")
brain_behavior_df$brain[N_nonNA_results+1] = brain_name
brain_behavior_df$predictor[N_nonNA_results+1] = predictor_name

brain_behavior_df$pre_p[N_nonNA_results+1] = 
  anova_predictor_test$Pr..Chisq.[row.names(anova_predictor_test) == predictor_name]

brain_behavior_df$model_p[N_nonNA_results+1] = 
  anova_model_test$Pr..Chisq.[2]
```
# hierarchical 1, brain x age, brain x offer
```{r}
## converged, anteriorinsula_corrected:age_biolder sig, anova sig
beh_antIns_full_0_fit = glmer(accept ~ 
                            anteriorinsula_corrected * offer * age_bi -
                              anteriorinsula_corrected:offer:age_bi +
                              # anteriorinsula_corrected * block_fair + # not sig, commented out
                              block_fair +
                            (1|participant_id),
                          data = all_trials_df,
                          family = binomial)
summary(beh_antIns_full_0_fit)
anova(beh_full_fit, beh_antIns_full_0_fit)

## converged, VS_corrected:offer sig, anova sig
beh_VS_full_0_fit = glmer(accept ~ 
                                VS_corrected * offer * age_bi -
                                VS_corrected:offer:age_bi +
                                # VS_corrected * block_fair + # not sig, commented out
                                block_fair +
                                (1|participant_id),
                              data = all_trials_df,
                              family = binomial)
summary(beh_VS_full_0_fit)
anova(beh_full_fit, beh_VS_full_0_fit)

## converged, no sig interaction, anova sig though
beh_dacc_full_0_fit = glmer(accept ~ 
                                dacc_corrected * offer * age_bi -
                                dacc_corrected:offer:age_bi +
                                # dacc_corrected * block_fair + # not sig, commented out
                              block_fair +
                                (1|participant_id),
                              data = all_trials_df,
                              family = binomial)
summary(beh_dacc_full_0_fit)
anova(beh_full_fit, beh_VS_full_0_fit)


## converged, not sig ingeraction, anove not sig
beh_vmpfc_full_0_fit = glmer(accept ~ 
                                vmpfc_corrected * offer * age_bi -
                                vmpfc_corrected:offer:age_bi +
                                # vmpfc_corrected * block_fair + # won't converge, conmment out
                               block_fair +
                                (1|participant_id),
                              data = all_trials_df,
                              family = binomial)
summary(beh_vmpfc_full_0_fit)
anova(beh_full_fit, beh_vmpfc_full_0_fit)
```

# hierarchical 2, brain * age only
```{r}
## converged, anteriorinsula_corrected:age_biolder sig, anova sig
beh_antIns_h2_fit = glmer(accept ~ 
                            offer * age_bi +
                              anteriorinsula_corrected * age_bi +
                              # anteriorinsula_corrected * block_fair + # not sig, commented out
                              block_fair +
                            (1|participant_id),
                          data = all_trials_df,
                          family = binomial)
summary(beh_antIns_h2_fit)
anova(beh_full_fit, beh_antIns_h2_fit)

## converged, interaction no sig, anova sig
beh_VS_full_h2_fit = glmer(accept ~ 
                                offer * age_bi +
                              VS_corrected * age_bi +
                                # VS_corrected * block_fair + # not sig, commented out
                                block_fair +
                                (1|participant_id),
                              data = all_trials_df,
                              family = binomial)
summary(beh_VS_full_h2_fit)
anova(beh_full_fit, beh_VS_full_h2_fit)

## converged, no sig interaction, anova sig though
beh_dacc_full_0_fit = glmer(accept ~ 
                                dacc_corrected * offer * age_bi -
                                dacc_corrected:offer:age_bi +
                                # dacc_corrected * block_fair + # not sig, commented out
                              block_fair +
                                (1|participant_id),
                              data = all_trials_df,
                              family = binomial)
summary(beh_dacc_full_0_fit)
anova(beh_full_fit, beh_VS_full_0_fit)


## converged, not sig ingeraction, anove not sig
beh_vmpfc_full_0_fit = glmer(accept ~ 
                                vmpfc_corrected * offer * age_bi -
                                vmpfc_corrected:offer:age_bi +
                                # vmpfc_corrected * block_fair + # won't converge, conmment out
                               block_fair +
                                (1|participant_id),
                              data = all_trials_df,
                              family = binomial)
summary(beh_vmpfc_full_0_fit)
anova(beh_full_fit, beh_vmpfc_full_0_fit)
```

### main brain only model
```{r}
beh_VS_full_fit = glmer(accept ~ offer * age_bi + block_fair + group_tri + 
                       VS_corrected + 
                                       (1|participant_id),
                                     data = all_trials_df,
                                     family = binomial)

# summary(beh_VS_full_fit)

beh_vmpfc_full_fit = glmer(accept ~ offer * age_bi + block_fair + group_tri + 
                       vmpfc_corrected + 
                                       (1|participant_id),
                                     data = all_trials_df,
                                     family = binomial)

beh_antIns_full_fit = glmer(accept ~ offer * age_bi + block_fair + group_tri + 
                       anteriorinsula_corrected + 
                         (1|participant_id),
                                     data = all_trials_df,
                                     family = binomial)

beh_dacc_full_fit = glmer(accept ~ offer * age_bi + block_fair + group_tri + 
                       dacc_corrected + 
                         (1|participant_id),
                                     data = all_trials_df,
                                     family = binomial)

anova(beh_full_fit, beh_VS_full_fit, refit = TRUE)
anova(beh_full_fit, beh_vmpfc_full_fit, refit = TRUE)
anova(beh_full_fit, beh_antIns_full_fit, refit = TRUE)
anova(beh_full_fit, beh_dacc_full_fit, refit = TRUE)
```






## P2 NH1B
"NH1B) The ins and dACC will be activated during the rejection of offers."
[insula, dACC][reject] (?)


## P2 NH1C
"NH1C) The vmPFC and VS will be activated during the acceptance of offers."
[vmPFC, VS][accept] (?) 


## P2 NH2A
"NH2A) All effects specified in NH1 will be blunted in older adults."
ROI mean ~ age



## P2 NH2B
"NH2B) The effect specified in NHB1 will be enhanced when rejecting unfair offers from human versus computer partners."
[insula, dACC][reject, human > computer]


# P2 NH single trial exploratory
### anterior insula, exploratory
```{r, eval = F}
# ## won't converge
# # model_P2_NH1_antIns_fit <- glmer(accept ~ anteriorinsula_corrected * age_bi * group_tri * block_fair +
# #                      (1|participant_id),
# #                             data = all_trials_df,
# #                             family = binomial)
# 
# ## converged, NO SIG three-way interaction
# model_P2_NH1_antIns_fit <- glmer(accept ~ anteriorinsula_corrected * age_bi * group_tri * block_fair -
#                             anteriorinsula_corrected:age_bi:group_tri:block_fair +
#                             (1|participant_id),
#                             data = all_trials_df,
#                             family = binomial)
# summary(model_P2_NH1_antIns_fit)
# 
# ## converged, SIG ant insula * group interaction
# model_P2_NH1_antIns_fit <- glmer(accept ~ anteriorinsula_corrected * age_bi * group_tri * block_fair -
#                             anteriorinsula_corrected:age_bi:group_tri:block_fair -
#                               anteriorinsula_corrected:age_bi:group_tri -
#                               anteriorinsula_corrected:age_bi:block_fair -
#                               anteriorinsula_corrected:group_tri:block_fair -
#                               age_bi:group_tri:block_fair +
#                               (1|participant_id),
#                             data = all_trials_df,
#                             family = binomial)
# summary(model_P2_NH1_antIns_fit)
# 
# ## won't converge
# # model_P2_NH1_fit <- glmer(accept ~ anteriorinsula_corrected * age_bi * group_tri +
# #                      (1|participant_id),
# #                             data = all_trials_df,
# #                             family = binomial)
# 
# ## converged, SIG insula*group interaction
# model_P2_NH1_antIns_fit <- glmer(accept ~ anteriorinsula_corrected * age_bi * group_tri -
#                             anteriorinsula_corrected:age_bi:group_tri + 
#                               anteriorinsula_corrected * age_bi * block_fair +
#                      (1|participant_id),
#                             data = all_trials_df,
#                             family = binomial)
# summary(model_P2_NH1_antIns_fit)
```


