---
title: "data_wrangle_srndnaUGR"
author: "Jen Yang"
date: "2024-11-1, last modified 2025-04-04"
output: 
  html_document:
    code_folding: hide
    toc: true
    toc_float:
      collapsed: false
      smooth_scroll: false
    hightlight: zenburn
    toc_depth: 6
---

<!-- this code extracts behabior data the data paper folder -->

```{r clean, include=FALSE}
# clean environment
rm(list = ls())
```

# Load libraries
```{r libraries, message=FALSE, warning=TRUE, include=FALSE}
library(car)
library(plyr)
library(foreign)
library(pscl)
library(boot)
library(MASS)
library(robust)
library(sfsmisc)
library(ggplot2)
library(reshape2)
library(ppcor)
library(ggrepel)
library(Hmisc)
library(tidyverse)
library(sandwich)
library(ggpubr)
library(interactions)
library(knitr)
library(twowaytests)
library(ggfortify)
library(interactions)
library(broom)
library(patchwork)
library(robustbase)
library(lmtest)
library(modelr)
library(Rmisc)
# library(raincloudplots)
library(cowplot)
library(readr)
library(PupillometryR)
library(ggpp)
library(estimatr)
library(skedastic)
library(ggpubr)
library(lubridate)
library(readxl)
library(gridExtra)
library(scales)
library(rstudioapi)
library(jsonlite)
library(rjson)
library(readr)
library(hBayesDM)
library(brms)
```

# load tsv and prolific raw data
```{r}
gitrepo_path = "/Users/momocco/Documents/GitHub/srndna-ug/behavioral_analyses"

data_dir = paste(gitrepo_path,"data", sep = "/")
codes_dir = paste(gitrepo_path, "codes", sep = "/")
fit_dir = paste(gitrepo_path,"fits", sep = "/")
figure_dir = paste(gitrepo_path,"figures", sep = "/")

bids_dir = "/Users/momocco/Documents/GitHub/srndna-datapaper/bids"
```

# participant list
```{r}
# load sub list
participants_tsv = "participants.tsv"

participants_df = read.table(file = paste(bids_dir, participants_tsv, sep = "/"), sep = '\t', header = TRUE)
participants_df$trial_total = 0
sublist = participants_df$participant_id
```

# create empty df to contain all decisions
```{r}
col_unify_names = c("onset", "duration", "trial_type", 
                  "response_time", "Offer")

all_col_names = c("onset", "duration", "trial_type", 
                  "response_time", "Offer", 
                  "block_type", "subjID", "run")

# create empty dataframe
all_long_df = data.frame(matrix(ncol = length(all_col_names), nrow = 0))
colnames(all_long_df) = all_col_names

block_col_names = c("onset", "block_type", "BlockNum", "BlockTrial", "BlockInclude", "run", "subID")

# create empty dataframe
block_long_df = data.frame(matrix(ncol = length(block_col_names), nrow = 0))
colnames(block_long_df) = block_col_names

withinsub_col_names = c("onset", "duration", "block_type", 
                  "response_time", "Offer", 
                  "subjID")
```

# prepare trial and block info
```{r}
decision_partner_types = c("event_accept_outgroup", "event_reject_outgroup",
                "event_accept_ingroup", "event_reject_ingroup",
                "event_accept_computer", "event_reject_computer",
                "event_accept_outgroup_fair", "event_reject_outgroup_fair",
                "event_accept_ingroup_fair", "event_reject_ingroup_fair",
                "event_accept_computer_fair", "event_reject_computer_fair",
                "event_accept_outgroup_unfair", "event_reject_outgroup_unfair",
                "event_accept_ingroup_unfair", "event_reject_ingroup_unfair",
                "event_accept_computer_unfair", "event_reject_computer_unfair",
                "missed_trial")

block_types = c("block_outgroup_fair", "block_outgroup_unfair",
                "block_ingroup_fair", "block_ingroup_unfair",
                "block_computer_fair", "block_computer_unfair")


```

# extract behavior
```{r}
for (i in 1:nrow(participants_df)) {
  # i = 5 # for testing, to comment out
  print(i)
  sub_name = sublist[i]
  print(sub_name)
  # find all ultimatum tsv files
  ug_tsv <- list.files(path = paste(bids_dir, sub_name, "func", sep = "/"), 
                       pattern = ".*ultimatum.*events.*\\.tsv$",
                       full.names = FALSE)
  
  # clean behavior data per run
  for (j in 1:length(ug_tsv)) {
    # j = 1
    # print(j)
    event_run_ij = paste(sub_name,sprintf("_task-ultimatum_run-0%d_events.tsv", j), sep = "")
    event_run_ij_df = 
      read.table(file = paste(bids_dir, sublist[i], "func", event_run_ij, sep = '/'), header = TRUE) %>% 
      select(all_of(col_unify_names))
    
    # extract trial type info per sub
    decision_partner_types_rows = event_run_ij_df$trial_type %in% decision_partner_types 
    decision_partner_types_rows_hitOnly = 
      event_run_ij_df$trial_type %in% decision_partner_types[1:length(decision_partner_types)-1] # exclude missed trials
    
    decision_partner_df = event_run_ij_df[decision_partner_types_rows,]
    decision_partner_df$block_type = NA
    decision_partner_df$run = j
    
    decision_partner_hitOnly_df = event_run_ij_df[decision_partner_types_rows_hitOnly,]
    decision_partner_hitOnly_df$block_type = NA
    decision_partner_hitOnly_df$run = j
    
    # count total hit trials
    participants_df$trial_total[i] = 
      participants_df$trial_total[i] + sum(decision_partner_types_rows_hitOnly)
    
    # extract block info per sub
    block_types_rows = event_run_ij_df$trial_type %in% block_types
    block_df = event_run_ij_df[block_types_rows,]
    block_df$BlockNum = 1:nrow(block_df)
    block_df$BlockTrial = NA
    block_df$BlockInclude = NA # default set to a block not included
    block_df$subID = NA
    
    # create empty df to compile trials from all blocks
    block_long_df_j = data.frame(matrix(ncol = length(withinsub_col_names), nrow = 0))
    colnames(block_long_df_j) = withinsub_col_names
    
    # check trial number per block
    for (k in 1:nrow(block_df)) {
      # k = 9
      # print(k)
      block_type_k = block_df$trial_type[k] # extract block type
      if (k < nrow(block_df)) {
      # find trial using block type
      n_trials_k =  sum(decision_partner_hitOnly_df$onset >= block_df$onset[k] & 
                          decision_partner_hitOnly_df$onset < block_df$onset[k+1])
      
      # marking block type for each trial, including missed trials
      decision_partner_df$block_type[decision_partner_df$onset >= block_df$onset[k] & 
                          decision_partner_df$onset < block_df$onset[k+1]] = block_type_k
      # marking block type for each hit trial
      decision_partner_hitOnly_df$block_type[decision_partner_hitOnly_df$onset >= block_df$onset[k] & 
                          decision_partner_hitOnly_df$onset < block_df$onset[k+1]] = block_type_k
      
      } else {
        n_trials_k = sum(decision_partner_hitOnly_df$onset >= block_df$onset[k])
        decision_partner_hitOnly_df$block_type[decision_partner_hitOnly_df$onset >= block_df$onset[k]] =
          block_type_k
      }
      block_df$BlockTrial[k] = n_trials_k
      if (n_trials_k >= 4) {
        block_df$BlockInclude[k] = "yes"
      }
      # cleanup and renome
      block_df_clean = block_df %>% 
        # rename columns
        mutate(block_type = trial_type) %>% 
        select(onset, block_type, BlockNum, BlockTrial, BlockInclude)
    }
    block_df_clean$run = j
    block_df_clean$subID = sub_name
    block_long_df = rbind(block_long_df, block_df_clean)
    
    decision_partner_df$subjID = sub_name
    
    # ## remove missed trials
    # decision_partner_df = decision_partner_df[decision_partner_df$trial_type != "missed_trial",]
    
    all_long_df = rbind(all_long_df, decision_partner_df)
    print(sprintf("run %d N trial = %d", j, nrow(decision_partner_hitOnly_df)))
  }
}
```

# recode and reorder
```{r}
all_clean_df = all_long_df %>% 
  mutate(offer = Offer,
         accept = as.numeric(grepl("accept", .$trial_type, fixed = TRUE)),
         missed = as.numeric(grepl("missed", .$trial_type, fixed = TRUE)),
         human = as.numeric(grepl("ingroup", .$trial_type, fixed = TRUE) | 
                              grepl("outgroup", .$trial_type, fixed = TRUE)),
         ingroup = as.numeric(grepl("ingroup", .$trial_type, fixed = TRUE)),
         block_fair = as.numeric(grepl("_fair", .$block_type, fixed = TRUE)),
         response_time = as.numeric(response_time)-1) %>% 
  select(subjID, offer, missed, accept, response_time, human, ingroup, block_fair, run)

sum(all_clean_df$response_time <0.2)

participants_df = participants_df %>% 
  mutate(Include = case_when(trial_total >= 115 ~ "yes",
                             trial_total < 115 ~ "no")) %>% 
  select(-group)

block_long_df = block_long_df %>% 
  select(subID, run, block_type, BlockNum, BlockTrial, BlockInclude)
```

# save cleaned data, missed trials are included
```{r}
write.csv(all_clean_df, paste(data_dir, "all_trials_missedIncluded.csv", sep = "/"), row.names = FALSE)
write.csv(block_long_df, paste(data_dir, "block_check.csv", sep = "/"), row.names = FALSE)
write.csv(participants_df, paste(data_dir, "participant_check.csv", sep = "/"), row.names = FALSE)
```

# create separate txt for each condition
```{r}
# remove missed trials
all_clean_df = all_clean_df[is.na(all_clean_df$response_time) == FALSE,]
write.csv(all_clean_df, paste(data_dir, "all_trials.csv", sep = "/"), row.names = FALSE)

computer_df = all_clean_df[all_clean_df$human == 0,]
human_df = all_clean_df[all_clean_df$human == 1,]
ingroup_df = human_df[human_df$ingroup == 1,]
outgroup_df = human_df[human_df$ingroup == 0,]
```

# save all data per condition
```{r}
write.table(computer_df, file = paste(data_dir, "computer.txt", sep = "/"), 
            sep = "\t", row.names = FALSE, quote = FALSE)
write.table(human_df, file = paste(data_dir, "human.txt", sep = "/"), 
            sep = "\t", row.names = FALSE, quote = FALSE)
write.table(ingroup_df, file = paste(data_dir, "ingroup.txt", sep = "/"), 
            sep = "\t", row.names = FALSE, quote = FALSE)
write.table(outgroup_df, file = paste(data_dir, "outgroup.txt", sep = "/"), 
            sep = "\t", row.names = FALSE, quote = FALSE)
```

# check behaviors of each participant
```{r}
col_names_choice_check = c("subjID", 
                           "computer_total", "computer_accept", "computer_reject",
                           "human_total", "human_accept", "human_reject",
                           "ingroup_total", "ingroup_accept", "ingroup_reject",
                           "outgroup_total", "outgroup_accept", "outgroup_reject")
choice_check = data.frame(matrix(ncol = length(col_names_choice_check), nrow = nrow(participants_df)))
colnames(choice_check) = col_names_choice_check

for (i in 1:nrow(participants_df)) {
  sub_name = sublist[i]
  computer_total = nrow(computer_df[computer_df$subjID == sub_name, ])
  computer_accept <- nrow(computer_df[computer_df$subjID == sub_name & computer_df$accept == 1, ])
  computer_reject <- nrow(computer_df[computer_df$subjID == sub_name & computer_df$accept == 0, ])
  
  human_total = nrow(human_df[human_df$subjID == sub_name, ])
  human_accept <- nrow(human_df[human_df$subjID == sub_name & human_df$accept == 1, ])
  human_reject <- nrow(human_df[human_df$subjID == sub_name & human_df$accept == 0, ])
  
  ingroup_total = nrow(ingroup_df[ingroup_df$subjID == sub_name, ])
  ingroup_accept <- nrow(ingroup_df[ingroup_df$subjID == sub_name & ingroup_df$accept == 1, ])
  ingroup_reject <- nrow(ingroup_df[ingroup_df$subjID == sub_name & ingroup_df$accept == 0, ])
  
  outgroup_total = nrow(outgroup_df[outgroup_df$subjID == sub_name, ])
  outgroup_accept <- nrow(outgroup_df[outgroup_df$subjID == sub_name & outgroup_df$accept == 1, ])
  outgroup_reject <- nrow(outgroup_df[outgroup_df$subjID == sub_name & outgroup_df$accept == 0, ])
  
  choice_check$subjID[i] = sub_name
  
  choice_check$computer_reject[i] = computer_reject
  choice_check$human_reject[i] = human_reject
  choice_check$ingroup_reject[i] = ingroup_reject
  choice_check$outgroup_reject[i] = outgroup_reject
  
  choice_check$computer_accept[i] = computer_accept
  choice_check$human_accept[i] = human_accept
  choice_check$ingroup_accept[i] = ingroup_accept
  choice_check$outgroup_accept[i] = outgroup_accept
  
  choice_check$computer_total[i] = computer_total
  choice_check$human_total[i] = human_total
  choice_check$ingroup_total[i] = ingroup_total
  choice_check$outgroup_total[i] = outgroup_total
}

choice_check = choice_check %>% 
  mutate(computer_accept_diff = computer_total - computer_accept,
         computer_reject_diff = computer_total - computer_reject,
         ingroup_accept_diff = ingroup_total - ingroup_accept,
         ingroup_reject_diff = ingroup_total - ingroup_reject,
         outgroup_accept_diff = outgroup_total - outgroup_accept,
         outgroup_reject_diff = outgroup_total - outgroup_reject)
  
  
sub_exclude = choice_check$subjID[choice_check$computer_accept_diff <= 2 |
                                    choice_check$ingroup_accept_diff <= 2 |
                                    choice_check$outgroup_accept_diff <= 2 |
                                    choice_check$computer_reject_diff <= 2 |
                                    choice_check$ingroup_reject_diff <= 2 |
                                    choice_check$outgroup_reject_diff <= 2]
length(sub_exclude)

```

# exclude subjects that choose reject fewer than 11 times (0-10)
```{r}
all_clean_filtered_df = all_clean_df[!(all_clean_df$subjID %in% sub_exclude),]
sub_include = unique(all_clean_filtered_df$subjID)
sub_include = data.frame(subjID = sub_include[])
```

# create separate txt for each condition
```{r}
computer_filtered_df = all_clean_filtered_df[all_clean_filtered_df$human == 0,]
human_filtered_df = all_clean_filtered_df[all_clean_filtered_df$human == 1,]
ingroup_filtered_df = human_filtered_df[human_filtered_df$ingroup == 1,]
outgroup_filtered_df = human_filtered_df[human_filtered_df$ingroup == 0,]
```

# save filtered data
```{r}
write.csv(all_clean_filtered_df, file = paste(data_dir, "all_clean_filtered_df.csv", sep = "/"), 
            row.names = FALSE)
write.csv(sub_include, file = paste(data_dir, "sub_include_behaviorVary.csv", sep = "/"), 
            row.names = FALSE)
write.table(computer_filtered_df, file = paste(data_dir, "computer_filtered.txt", sep = "/"), 
            sep = "\t", row.names = FALSE, quote = FALSE)
write.table(human_filtered_df, file = paste(data_dir, "human_filtered.txt", sep = "/"), 
            sep = "\t", row.names = FALSE, quote = FALSE)
write.table(ingroup_filtered_df, file = paste(data_dir, "ingroup_filtered.txt", sep = "/"), 
            sep = "\t", row.names = FALSE, quote = FALSE)
write.table(outgroup_filtered_df, file = paste(data_dir, "outgroup_filtered.txt", sep = "/"), 
            sep = "\t", row.names = FALSE, quote = FALSE)
```



