---
title: "layered_plot"
author: "Jen Yang"
date: "2024-7-17"
output: html_document
---

```{r clean, include=FALSE}
# clean environment
rm(list = ls())
```

```{r restart R session, include=FALSE, results='hide'}
# .rs.restartR()
```
# Load libraries
```{r libraries, message=FALSE, warning=TRUE, include=FALSE}
library(car)
library(plyr)
library(foreign)
library(pscl)
library(boot)
library(MASS)
library(robust)
library(sfsmisc)
library(ggplot2)
library(ggtext)
library(reshape2)
library(ppcor)
library(ggrepel)
library(Hmisc)
library(tidyverse)
library(sandwich)
library(ggpubr)
library(interactions)
library(knitr)
library(twowaytests)
library(ggfortify)
library(interactions)
library(broom)
library(patchwork)
library(robustbase)
library(lmtest)
library(modelr)
library(Rmisc)
# library(raincloudplots)
library(cowplot)
library(readr)
library(PupillometryR)
library(ggpp)
library(estimatr)
library(skedastic)
library(RColorBrewer)
library(svglite)
library(latex2exp)
```

# Global chunk setting
```{r chunkGlobal, include=FALSE}
# global chunk setting
knitr::opts_chunk$set(message=FALSE, warning=FALSE, cache = FALSE)
```
# Load functions
```{r load_functons, include=FALSE}
source("raincloud_IV1IV2continuous_mean_plot_fun.R", local = knitr::knit_global())
source("raincloud_main_mean_plot_fun.R", local = knitr::knit_global())
```

# Load data
```{r , include=FALSE}
# .csv file folder
file_folder = 
  "/Users/Momocco/Documents/GitHub/Financial_Exploitation/Financial_Exploitation/ANALYSES/DATA_PROCESSED"
fig_folder = "/Users/Momocco/Documents/GitHub/Financial_Exploitation/Financial_Exploitation/ANALYSES/PLOTS/revision_manu_figs"
```

## Study 1
```{r}
study1_file_name = "study_1_data_clean_processed_selected.csv"
study1_IV_names = "study1_IVs_list.csv"

# read csv
study1_data_raw <- read.csv(paste(file_folder, study1_file_name, sep = "/"))

study1_IVs_list <- read.csv(study1_IV_names)
study1_N_IVs = nrow(study1_IVs_list)
study1_IVs_list <- as.character(study1_IVs_list[,1])
recode_gender_cat = study1_data_raw$gender == 1
study1_data_raw$gender_cat[recode_gender_cat] = 'Male'
study1_data_raw$gender_cat[!recode_gender_cat] = 'Female'
study1_data_raw$gender_cat = as.factor(study1_data_raw$gender_cat)
recode_race = study1_data_raw$race_binary == 1
study1_data_raw$race_cat[recode_race] = 'minority'
study1_data_raw$race_cat[!recode_race] = 'non-minority'
study1_data_raw$race_binary = as.numeric(study1_data_raw$race_binary)
```

## Study 2
```{r}
study2_file_name = "study_2_data_clean_processed_selected_OAFEM_recode.csv"
study2_IV_names = "study2_IVs_list.csv"

# read csv
study2_data_raw <- read.csv(paste(file_folder, study2_file_name, sep = "/"))

recode_gender = study2_data_raw$gender == 1
study2_data_raw$gender_cat[recode_gender] = 'Male'
study2_data_raw$gender_cat[!recode_gender] = 'Female'
study2_data_raw$gender[!recode_gender] = 0
study2_data_raw$gender_cat = as.factor(study2_data_raw$gender_cat)
recode_race = study2_data_raw$race_binary == 1
study2_data_raw$race_cat[recode_race] = 'minority'
study2_data_raw$race_cat[!recode_race] = 'non-minority'
study2_data_raw$race_cat = as.factor(study2_data_raw$race_cat)
study2_IVs_list <- read.csv(study2_IV_names)
N_IVs = nrow(study2_IVs_list)
study2_IVs_list <- as.character(study2_IVs_list[,1])
```

## Study 3
```{r directories and data, include=FALSE}
# csv file name
study3_file_name = "study_3_data_clean_processed_selected_OAFEM_recode.csv"
study3_IV_names = "study3_IVs_list.csv"

# read csv
study3_data_raw <- read.csv(paste(file_folder, study3_file_name, sep = "/"))

# keep only subs with similar oafem and fevs ratings
study3_data_raw_FEVSfiltered = study3_data_raw[study3_data_raw$oafem_fevs_cat!='',]

# recode some categorical data
recode_gender = study3_data_raw_FEVSfiltered$gender == 1
study3_data_raw_FEVSfiltered$gender_cat[recode_gender] = 'Male'
study3_data_raw_FEVSfiltered$gender_cat[!recode_gender] = 'Female'
study3_data_raw_FEVSfiltered$gender[!recode_gender] = 0
study3_data_raw_FEVSfiltered$gender_cat = as.factor(study3_data_raw_FEVSfiltered$gender_cat)
# study3_data_raw_FEVSfiltered$Ugame_unfair_reject = as.factor(study3_data_raw_FEVSfiltered$Ugame_unfair_reject)
recode_race = study3_data_raw_FEVSfiltered$race_binary == 1
study3_data_raw_FEVSfiltered$race_cat[recode_race] = 'minority'
study3_data_raw_FEVSfiltered$race_cat[!recode_race] = 'non-minority'
study3_data_raw_FEVSfiltered$race_cat = as.factor(study3_data_raw_FEVSfiltered$race_cat)

# no OAFEM-FEVS filter
recode_gender = study3_data_raw$gender == 1
study3_data_raw$gender_cat[recode_gender] = 'Male'
study3_data_raw$gender_cat[!recode_gender] = 'Female'
study3_data_raw$gender[!recode_gender] = 0
study3_data_raw$gender_cat = as.factor(study3_data_raw$gender_cat)
# study3_data_raw$Ugame_unfair_reject = as.factor(study3_data_raw$Ugame_unfair_reject)
recode_race = study3_data_raw$race_binary == 1
study3_data_raw$race_cat[recode_race] = 'minority'
study3_data_raw$race_cat[!recode_race] = 'non-minority'
study3_data_raw$race_cat = as.factor(study3_data_raw$race_cat)
study3_IVs_list <- read.csv(study3_IV_names)
N_IVs = nrow(study3_IVs_list)
study3_IVs_list <- as.character(study3_IVs_list[,1])

study3_data_raw = study3_data_raw %>% mutate(oafem_sum_z = scale(oafem_sum, center = TRUE, scale = TRUE),
                                            fevs_sum_z = scale(fevs_sum, center = TRUE, scale = TRUE),
                                            oafem_fevs_z_diff = abs(oafem_sum_z - fevs_sum_z))
study3_data_z2_filtered = study3_data_raw[study3_data_raw$oafem_fevs_z_diff<=2,]

study3_data_z2_filtered$age_current = study3_data_z2_filtered$age_check
study3_data_z2_filtered$education_control = study3_data_z2_filtered$education_degree
```

# Load study123 results big table
```{r}
study123_interaction_ageControl_regression_results_raw = readRDS("study123_interaction_regression_results_raw.rds")
study123_mainEffect_regression_results_raw = readRDS("study123_mainEffect_regression_results_raw.rds")

study123_interaction_ageControl_regression_results_844 = readRDS("study123_interaction_regression_results_844.rds")
```

# figure dimension
```{r}
w = 7
h = 5
axis_title = 10
axis_ticks = 8
axis_text = 10
legend_all = 10
```

# Study 1
## parameters
```{r}
Study_ID = "1"
Study_title = "Study_1_"
# mydata = study1_data_raw
DV_str = 'oafem_sum'
DV_ylabel_str = 'OAFEM' # DV_ylabel_str = 'Self-Reported \nFinancial Exploitation (OAFEM)'
```

## Intrinsic Affect-Worsening * SES
```{r}
IV1_str = "intrinsic_worsening_avg"
IV1_xlabel_str = 'Intrinsic Affect-Worsening'
IV1_xticks_str = c("smaller amount", "larger amount")

mod_str = "SES_global_sum"
mod_legend_title_str = 'SES'

mydata = study1_data_raw[,c(DV_str, IV1_str, mod_str, "age_current", "gender", "race_binary")] %>% 
  na.omit()

model_rlm_full = rlm(oafem_sum ~ intrinsic_worsening_avg * SES_global_sum + age_current + gender + race_binary, study1_data_raw)
summary(model_rlm_full)
vif(model_rlm_full)

model_rlm_full_s2 = rlm(oafem_sum ~ intrinsic_worsening_avg * ses_2 + age_current + gender + race_binary, study2_data_raw)
summary(model_rlm_full_s2)
vif(model_rlm_full_s2)


interact_plot(model_rlm_full, 
              pred = intrinsic_worsening_avg,
              modx = SES_global_sum,
              plot.points = TRUE,
              jitter = c(0.05,0),
              data = mydata,
              partial.residuals = FALSE,
              point.alpha = 0.3,
              point.size = 0.7,
              x.label = IV1_xlabel_str,
              y.label = DV_ylabel_str,
              pred.labels = NULL,
              modx.labels = c(),
              mod2.labels = NULL,
              main.title = NULL,
              legend.main = mod_legend_title_str) +
  ylim(0,50) + # four points larger than 50 are not shown in the figure
  scale_x_continuous(
    breaks = c(1.5, 4),
    labels = IV1_xticks_str) +
  theme(
        # plot.subtitle=element_text(size = 14+4),
        # legend.position = c(.95, .95),
        # legend.position="top",
        legend.position="right",
        # legend.justification = c("right", "top"),
        # legend.box.just = "right",
        # legend.margin = margin(6, 6, 6, 6),
        legend.margin = margin(0, 2, 0, -6),
        legend.title=element_text(size=legend_all),
        legend.text=element_text(size=legend_all-2, margin = margin(l = 0.5)),
        # legend.spacing.y = unit(0.5, 'cm'),
        axis.line = element_line(size = 0.5, colour = "black", linetype=1),
        axis.text.x = element_text(size = axis_text), axis.text.y = element_text(size = axis_text), 
        axis.title.x = element_text(size = axis_title, face = "bold"), axis.title.y = element_text(size = axis_title, face = "bold"),
        # panel.grid.minor = element_line(size = 0.25, linetype = 'dotted',
                                        # colour = "black"),
        panel.grid = element_blank(),
        panel.background = element_blank())

save_name = paste("revision", mod_str, "INTER", IV1_str, sep = "_")
save_name = paste(Study_title, save_name, ".png", sep = "")
ggsave(paste(fig_folder,save_name, sep = "/"), width = w-3, height = h-2)
```

# Study 2
## parameters
```{r}
Study_ID = "2"
Study_title = "Study_2_"
mydata = study2_data_raw
DV_str = 'oafem_sum'
DV_ylabel_str = 'OAFEM' # DV_ylabel_str = 'Self-Reported \nFinancial Exploitation (OAFEM)'
```

## 1. everyday cognitive decline * SES
```{r}
mod_str ='ses_2'
mod_legend_title_str = 'SES'
IV1_xticks_str = c("smaller decline", "larger decline")

IV1_str = 'everyday_cog_avg'
IV1_xlabel_str = 'Everyday Cognitive Decline'
###

mydata = study2_data_raw[,c(DV_str, IV1_str, mod_str, "age_current", "gender", "race_binary")] %>% 
  na.omit()

model_rlm_full = rlm(oafem_sum ~ everyday_cog_avg * ses_2 + age_current + gender + race_binary, mydata)

plot_11 = interact_plot(model_rlm_full, 
              pred = everyday_cog_avg,
              modx = ses_2,
              plot.points = TRUE,
              jitter = c(0.05,0),
              data = mydata,
              partial.residuals = FALSE,
              point.alpha = 0.3,
              point.size = 0.7,
              x.label = IV1_xlabel_str,
              y.label = DV_ylabel_str,
              pred.labels = NULL,
              modx.labels = NULL,
              mod2.labels = NULL,
              main.title = NULL,
              legend.main = mod_legend_title_str) +
  ylim(0,40) + # 3 points not shown
  scale_x_continuous(
    # limits = c(1,4),
    breaks = c(1.5, 3),
    labels = IV1_xticks_str) +
  theme(
        # plot.subtitle=element_text(size = 14+4),
        # legend.position = c(.95, .95),
        # legend.position="top",
        legend.position="right",
        # legend.justification = c("right", "top"),
        # legend.box.just = "right",
        # legend.margin = margin(6, 6, 6, 6),
        legend.margin = margin(0, 2, 0, -6),
        legend.title=element_text(size=legend_all),
        legend.text=element_text(size=legend_all-2, margin = margin(l = 0.5)),
        # legend.spacing.y = unit(0.5, 'cm'),
        axis.line = element_line(size = 0.5, colour = "black", linetype=1),
        axis.text.x = element_text(size = axis_text), axis.text.y = element_text(size = axis_text), 
        axis.title.x = element_text(size = axis_title, face = "bold"), axis.title.y = element_text(size = axis_title, face = "bold"),
        # panel.grid.minor = element_line(size = 0.25, linetype = 'dotted',
                                        # colour = "black"),
        panel.grid = element_blank(),
        panel.background = element_blank())

plot_11
save_name = paste("revision", mod_str, "INTER", IV1_str, sep = "_")
save_name = paste(Study_title, save_name, ".png", sep = "")
ggsave(paste(fig_folder,save_name, sep = "/"), width = w-3, height = h-2)
```

## 2. persuadability * SES
```{r}
mod_str ='ses_2'
mod_legend_title_str = 'SES'

IV1_str = 'gull_persuasive_avg'
IV1_xticks_str = c('less persuadable',
                   'more persuadable')
IV1_xlabel_str = 'Persuadability'

mydata = study2_data_raw[,c(DV_str, IV1_str, mod_str, "age_current", "gender", "race_binary")] %>% 
  na.omit()

model_rlm_full = rlm(oafem_sum ~ gull_persuasive_avg * ses_2 + age_current + gender + race_binary, mydata, maxit = 100)

plot_12 = interact_plot(model_rlm_full, 
              pred = gull_persuasive_avg,
              modx = ses_2,
              plot.points = TRUE,
              jitter = c(0.05,0),
              data = mydata,
              partial.residuals = FALSE,
              point.alpha = 0.3,
              point.size = 0.7,
              x.label = IV1_xlabel_str,
              y.label = DV_ylabel_str,
              pred.labels = NULL,
              modx.labels = NULL,
              mod2.labels = NULL,
              main.title = NULL,
              legend.main = mod_legend_title_str) +
  ylim(0,40) + # 3 points not shown
  # xlim(1,7) +
  scale_x_continuous(
    breaks = c(2, 6),
    labels = IV1_xticks_str) +
  theme(
        # plot.subtitle=element_text(size = 14+4),
        # legend.position = c(.95, .95),
        # legend.position="top",
        legend.position="right",
        # legend.justification = c("right", "top"),
        # legend.box.just = "right",
        # legend.margin = margin(6, 6, 6, 6),
        legend.margin = margin(0, 2, 0, -6),
        legend.title=element_text(size=legend_all),
        legend.text=element_text(size=legend_all-2, margin = margin(l = 0.5)),
        # legend.spacing.y = unit(0.5, 'cm'),
        axis.line = element_line(size = 0.5, colour = "black", linetype=1),
        axis.text.x = element_text(size = axis_text), axis.text.y = element_text(size = axis_text), 
        axis.title.x = element_text(size = axis_title, face = "bold"), axis.title.y = element_text(size = axis_title, face = "bold"),
        # panel.grid.minor = element_line(size = 0.25, linetype = 'dotted',
                                        # colour = "black"),
        panel.grid = element_blank(),
        panel.background = element_blank())

plot_12
save_name = paste("revision", mod_str, "INTER", IV1_str, sep = "_")
save_name = paste(Study_title, save_name, ".png", sep = "")
ggsave(paste(fig_folder,save_name, sep = "/"), width = w-3, height = h-2)
```

## 3. making others feel worse * SES
```{r}
mod_str ='ses_2'
mod_legend_title_str = 'SES'

IV1_str = 'extrinsic_worsening_avg'
IV1_xticks_str = c('smaller amount',
                   'greater amount')
IV1_xlabel_str = 'Extrinsic Affect-Worsening'

mydata = study2_data_raw[,c(DV_str, IV1_str, mod_str, "age_current", "gender", "race_binary")] %>% 
  na.omit()

model_rlm_full = rlm(oafem_sum ~ extrinsic_worsening_avg * ses_2 + age_current + gender + race_binary, mydata, maxit = 100)

plot_21 = interact_plot(model_rlm_full, 
              pred = extrinsic_worsening_avg,
              modx = ses_2,
              plot.points = TRUE,
              jitter = c(0.05,0),
              data = mydata,
              partial.residuals = FALSE,
              point.alpha = 0.3,
              point.size = 0.7,
              x.label = IV1_xlabel_str,
              y.label = DV_ylabel_str,
              pred.labels = NULL,
              modx.labels = NULL,
              mod2.labels = NULL,
              main.title = NULL,
              legend.main = mod_legend_title_str) +
  ylim(0,40) + # 3 points not shown
  scale_x_continuous(
    # limits = c(1,5),
    breaks = c(1.5, 4),
    labels = IV1_xticks_str) +
  theme(
        # plot.subtitle=element_text(size = 14+4),
        # legend.position = c(.95, .95),
        # legend.position="top",
        legend.position="right",
        # legend.justification = c("right", "top"),
        # legend.box.just = "right",
        # legend.margin = margin(6, 6, 6, 6),
        legend.margin = margin(0, 2, 0, -6),
        legend.title=element_text(size=legend_all),
        legend.text=element_text(size=legend_all-2, margin = margin(l = 0.5)),
        # legend.spacing.y = unit(0.5, 'cm'),
        axis.line = element_line(size = 0.5, colour = "black", linetype=1),
        axis.text.x = element_text(size = axis_text), axis.text.y = element_text(size = axis_text), 
        axis.title.x = element_text(size = axis_title, face = "bold"), axis.title.y = element_text(size = axis_title, face = "bold"),
        # panel.grid.minor = element_line(size = 0.25, linetype = 'dotted',
                                        # colour = "black"),
        panel.grid = element_blank(),
        panel.background = element_blank())

plot_21
save_name = paste("revision", mod_str, "INTER", IV1_str, sep = "_")
save_name = paste(Study_title, save_name, ".png", sep = "")
ggsave(paste(fig_folder,save_name, sep = "/"), width = w-3, height = h-2)

```

## 4. making oneself feel worse * SES
```{r}
mod_str ='ses_2'
mod_legend_title_str = 'SES'

IV1_str = 'intrinsic_worsening_avg'
IV1_xticks_str = c('smaller amount',
                   'greater amount')
IV1_xlabel_str = 'Intrinsic Affect-Worsening'

mydata = study2_data_raw[,c(DV_str, IV1_str, mod_str, "age_current", "gender", "race_binary")] %>% 
  na.omit()

model_rlm_full = rlm(oafem_sum ~ intrinsic_worsening_avg * ses_2 + age_current + gender + race_binary, mydata, maxit = 100)

plot_22 = interact_plot(model_rlm_full, 
              pred = intrinsic_worsening_avg,
              modx = ses_2,
              plot.points = TRUE,
              jitter = c(0.05,0),
              data = mydata,
              partial.residuals = FALSE,
              point.alpha = 0.3,
              point.size = 0.7,
              x.label = IV1_xlabel_str,
              y.label = DV_ylabel_str,
              pred.labels = NULL,
              modx.labels = NULL,
              mod2.labels = NULL,
              main.title = NULL,
              legend.main = mod_legend_title_str) +
  ylim(0,40) + # 3 points not shown
  scale_x_continuous(
    # limits = c(1,5),
    breaks = c(1.5, 3.5),
    labels = IV1_xticks_str) +
  theme(
        # plot.subtitle=element_text(size = 14+4),
        # legend.position = c(.95, .95),
        # legend.position="top",
        legend.position="right",
        # legend.justification = c("right", "top"),
        # legend.box.just = "right",
        # legend.margin = margin(6, 6, 6, 6),
        legend.margin = margin(0, 2, 0, -6),
        legend.title=element_text(size=legend_all),
        legend.text=element_text(size=legend_all-2, margin = margin(l = 0.5)),
        # legend.spacing.y = unit(0.5, 'cm'),
        axis.line = element_line(size = 0.5, colour = "black", linetype=1),
        axis.text.x = element_text(size = axis_text), axis.text.y = element_text(size = axis_text), 
        axis.title.x = element_text(size = axis_title, face = "bold"), axis.title.y = element_text(size = axis_title, face = "bold"),
        # panel.grid.minor = element_line(size = 0.25, linetype = 'dotted',
                                        # colour = "black"),
        panel.grid = element_blank(),
        panel.background = element_blank())

plot_22
save_name = paste("revision", mod_str, "INTER", IV1_str, sep = "_")
save_name = paste(Study_title, save_name, ".png", sep = "")
ggsave(paste(fig_folder,save_name, sep = "/"), width = w-3, height = h-2)
```

## figure with all panels
```{r}
ggarrange(plot_11, plot_12, plot_21, plot_22, 
          ncol = 2, nrow = 2, labels="AUTO", common.legend = TRUE)

ggsave(paste(fig_folder, "revision_study2_inter.png", sep = "/"), width = w, height = h)
```

# Study 3, z-diff, OAFEM
## parameters
```{r}
Study_ID = "3 all"
Study_title = "Study_3_OAFEM_"
DV_str = 'oafem_sum'
# DV_lim = c(0, 124) # max = 124
DV_lim = c(0, 40) # max = 124
DV_ylabel_str = 'OAFEM' # DV_ylabel_str = 'Self-Reported \nFinancial Exploitation (OAFEM)'
```

## 1. persuadability * age
```{r}
mod_str ='age_current'
mod_legend_title_str = 'Age'

IV1_str = 'gull_persuasive_avg'
IV1_xticks_str = c('less', 'more')
IV1_xlabel_str = 'Persuadability'

mydata = study3_data_z2_filtered[,c(DV_str, IV1_str, mod_str, "gender", "race_binary", "education_control")] %>% 
  na.omit()

model_rlm_full = rlm(oafem_sum ~ gull_persuasive_avg * age_current + gender + race_binary + education_control, mydata, maxit = 100)

plot_31 =
  interact_plot(model_rlm_full, 
              pred = gull_persuasive_avg,
              modx = age_current,
              plot.points = TRUE,
              jitter = c(0.05,0),
              data = mydata,
              partial.residuals = FALSE,
              point.alpha = 0.3,
              point.size = 0.7,
              x.label = IV1_xlabel_str,
              y.label = DV_ylabel_str,
              pred.labels = NULL,
              modx.labels = NULL,
              mod2.labels = NULL,
              main.title = NULL,
              legend.main = mod_legend_title_str) +
  # ylim(0,100) + # 6 points not shown
  scale_x_continuous(
    # limits = c(1,7),
    breaks = c(2, 6),
    labels = IV1_xticks_str) +
  theme(
        # plot.subtitle=element_text(size = 14+4),
        # legend.position = c(.95, .95),
        # legend.position="top",
        legend.position="right",
        # legend.justification = c("right", "top"),
        # legend.box.just = "right",
        # legend.margin = margin(6, 6, 6, 6),
        legend.margin = margin(0, 2, 0, -6),
        legend.title=element_text(size=legend_all),
        legend.text=element_text(size=legend_all-2, margin = margin(l = 0)),
        legend.key.width = unit(1, 'cm'), #change legend key width
        # legend.spacing.y = unit(0.5, 'cm'),
        axis.line = element_line(size = 0.5, colour = "black", linetype=1),
        axis.text.x = element_text(size = axis_text), axis.text.y = element_text(size = axis_text), 
        axis.title.x = element_text(size = axis_title, face = "bold"), axis.title.y = element_text(size = axis_title, face = "bold"),
        # panel.grid.minor = element_line(size = 0.25, linetype = 'dotted',
                                        # colour = "black"),
        panel.grid = element_blank(),
        panel.background = element_blank())

plot_31
save_name = paste("revision_OAFEM", mod_str, "INTER", IV1_str, sep = "_")
save_name = paste(Study_title, save_name, ".png", sep = "")
ggsave(paste(fig_folder,save_name, sep = "/"), width = w-3, height = h-2)
```

## 2. persuadability * SES
```{r}
mod_str ='SES_global_sum'
mod_legend_title_str = 'SES'

IV1_str = 'gull_persuasive_avg'
IV1_xticks_str = c('less', 'more')
IV1_xlabel_str = 'Persuadability'

mydata = study3_data_z2_filtered[,c(DV_str, IV1_str, mod_str, "age_current", "gender", "race_binary")] %>% 
  na.omit()

model_rlm_full = rlm(oafem_sum ~ gull_persuasive_avg * SES_global_sum + age_current + gender + race_binary, mydata, maxit = 100)

plot_32 =
  interact_plot(model_rlm_full, 
              pred = gull_persuasive_avg,
              modx = SES_global_sum,
              plot.points = TRUE,
              jitter = c(0.05,0),
              data = mydata,
              partial.residuals = FALSE,
              point.alpha = 0.3,
              point.size = 0.7,
              x.label = IV1_xlabel_str,
              y.label = DV_ylabel_str,
              pred.labels = NULL,
              modx.labels = NULL,
              mod2.labels = NULL,
              main.title = NULL,
              legend.main = mod_legend_title_str) +
  # ylim(0,40) + # 3 points not shown
  # xlim(1,7) +
  scale_x_continuous(
    breaks = c(2, 6),
    labels = IV1_xticks_str) +
  theme(
        # plot.subtitle=element_text(size = 14+4),
        # legend.position = c(.95, .95),
        # legend.position="top",
        legend.position="right",
        # legend.justification = c("right", "top"),
        # legend.box.just = "right",
        # legend.margin = margin(6, 6, 6, 6),
        legend.margin = margin(0, 2, 0, -6),
        legend.title=element_text(size=legend_all),
        legend.text=element_text(size=legend_all-2, margin = margin(l = 0.5)),
        legend.key.width = unit(1, 'cm'), #change legend key width
        # legend.spacing.y = unit(0.5, 'cm'),
        axis.line = element_line(size = 0.5, colour = "black", linetype=1),
        axis.text.x = element_text(size = axis_text), axis.text.y = element_text(size = axis_text), 
        axis.title.x = element_text(size = axis_title, face = "bold"), axis.title.y = element_text(size = axis_title, face = "bold"),
        # panel.grid.minor = element_line(size = 0.25, linetype = 'dotted',
                                        # colour = "black"),
        panel.grid = element_blank(),
        panel.background = element_blank())

plot_32
save_name = paste("revision_OAFEM", mod_str, "INTER", IV1_str, sep = "_")
save_name = paste(Study_title, save_name, ".png", sep = "")
ggsave(paste(fig_folder,save_name, sep = "/"), width = w-3, height = h-2)
```

## 3. insensitivity to trustworthiness cues * age
```{r}
mod_str ='age_current'
mod_legend_title_str = 'Age'

IV1_str = 'gull_insensitive_avg'
IV1_xticks_str = c('less', 'more')
IV1_xlabel_str = 'Insensitivity to\nTrustworthiness Cues'

mydata = study3_data_z2_filtered[,c(DV_str, IV1_str, mod_str, "gender", "race_binary", "education_control")] %>% 
  na.omit()

model_rlm_full = rlm(oafem_sum ~ gull_insensitive_avg * age_current + gender + race_binary + education_control, mydata, maxit = 100)

plot_33 =
  interact_plot(model_rlm_full, 
              pred = gull_insensitive_avg,
              modx = age_current,
              plot.points = TRUE,
              jitter = c(0.05,0),
              data = mydata,
              partial.residuals = FALSE,
              point.alpha = 0.3,
              point.size = 0.7,
              x.label = IV1_xlabel_str,
              y.label = DV_ylabel_str,
              pred.labels = NULL,
              modx.labels = NULL,
              mod2.labels = NULL,
              main.title = NULL,
              legend.main = mod_legend_title_str) +
  # ylim(0,40) + # 3 points not shown
  # xlim(1,7) +
  scale_x_continuous(
    breaks = c(2, 6),
    labels = IV1_xticks_str) +
  theme(
        # plot.subtitle=element_text(size = 14+4),
        # legend.position = c(.95, .95),
        # legend.position="top",
        legend.position="right",
        # legend.justification = c("right", "top"),
        # legend.box.just = "right",
        # legend.margin = margin(6, 6, 6, 6),
        legend.margin = margin(0, 2, 0, -6),
        legend.title=element_text(size=legend_all),
        legend.text=element_text(size=legend_all-2, margin = margin(l = 0.5)),
        legend.key.width = unit(1, 'cm'), #change legend key width
        # legend.spacing.y = unit(0.5, 'cm'),
        axis.line = element_line(size = 0.5, colour = "black", linetype=1),
        axis.text.x = element_text(size = axis_text), axis.text.y = element_text(size = axis_text), 
        axis.title.x = element_text(size = axis_title, face = "bold"), axis.title.y = element_text(size = axis_title, face = "bold"),
        # panel.grid.minor = element_line(size = 0.25, linetype = 'dotted',
                                        # colour = "black"),
        panel.grid = element_blank(),
        panel.background = element_blank())

plot_33
save_name = paste("revision_OAFEM", mod_str, "INTER", IV1_str, sep = "_")
save_name = paste(Study_title, save_name, ".png", sep = "")
ggsave(paste(fig_folder,save_name, sep = "/"), width = w-3, height = h-2)

```

## figure with all panels
```{r}
ggarrange(plot_31, plot_32, plot_33, 
          ncol = 2, nrow = 2, labels="AUTO", common.legend = FALSE)

ggsave(paste(fig_folder, "revision_study3_OAFEM_inter.png", sep = "/"), width = w, height = h)
```

# Study 3, z-diff, FEVS
## parameters
```{r}
Study_ID = "3 all"
Study_title = "Study_3_FEVS_"
mydata = study3_data_z2_filtered
DV_str = 'fevs_sum'
DV_ylabel_str = 'FEVS' # DV_ylabel_str = 'Financial Exploitation \nVulnerability'
```

## 1. persuadability * everyday cognitive decline
```{r}
mod_str ='everyday_cog_avg'
mod_legend_title_str = 'Everyday Cognitive Decline'

###
IV1_str = 'gull_persuasive_avg'
IV1_xticks_str = c('less persuadable', 'more persuadable')
IV1_xlabel_str = 'Persuadability'
###

mydata = study3_data_z2_filtered[,c(DV_str, IV1_str, mod_str, "age_current", "gender", "race_binary", "education_control")] %>% 
  na.omit()

model_rlm_full = rlm(fevs_sum ~ gull_persuasive_avg * everyday_cog_avg + age_current + gender + race_binary + education_control, 
                     mydata, maxit = 100)

plot_41 =
  interact_plot(model_rlm_full, 
              pred = gull_persuasive_avg,
              modx = everyday_cog_avg,
              plot.points = TRUE,
              jitter = c(0.05,0.1),
              data = mydata,
              partial.residuals = FALSE,
              point.alpha = 0.3,
              point.size = 0.7,
              x.label = IV1_xlabel_str,
              y.label = DV_ylabel_str,
              pred.labels = NULL,
              modx.labels = NULL,
              mod2.labels = NULL,
              main.title = NULL,
              legend.main = mod_legend_title_str) +
  scale_x_continuous(
    breaks = c(2, 6),
    labels = IV1_xticks_str) +
  theme(
        # plot.subtitle=element_text(size = 14+4),
        # legend.position = c(.95, .95),
        # legend.position="top",
        legend.position="right",
        # legend.justification = c("right", "top"),
        # legend.box.just = "right",
        # legend.margin = margin(6, 6, 6, 6),
        legend.margin = margin(0, 2, 0, -6),
        legend.title=element_text(size=legend_all),
        legend.text=element_text(size=legend_all-2, margin = margin(l = 0.5)),
        # legend.spacing.y = unit(0.5, 'cm'),
        axis.line = element_line(size = 0.5, colour = "black", linetype=1),
        axis.text.x = element_text(size = axis_text), axis.text.y = element_text(size = axis_text), 
        axis.title.x = element_text(size = axis_title, face = "bold"), axis.title.y = element_text(size = axis_title, face = "bold"),
        # panel.grid.minor = element_line(size = 0.25, linetype = 'dotted',
                                        # colour = "black"),
        panel.grid = element_blank(),
        panel.background = element_blank())

plot_41
save_name = paste("revision_FEVS", mod_str, "INTER", IV1_str, sep = "_")
save_name = paste(Study_title, save_name, ".png", sep = "")
ggsave(paste(fig_folder,save_name, sep = "/"), width = w-3, height = h-2)
```

## 2. insensitivity to trustworthiness cues * everyday cognitive decline
```{r}
mod_str ='everyday_cog_avg'
mod_legend_title_str = 'Everyday Cognitive Decline'

###
IV1_str = 'gull_insensitive_avg'
IV1_xticks_str = c('less insensitive', 'more insensitive')
IV1_xlabel_str = 'Insensitivity to Trustworthiness Cues'

mydata = study3_data_z2_filtered[,c(DV_str, IV1_str, mod_str, "age_current", "gender", "race_binary", "education_control")] %>% 
  na.omit()

model_rlm_full = rlm(fevs_sum ~ gull_insensitive_avg * everyday_cog_avg + age_current + gender + race_binary + education_control,
                     mydata, maxit = 100)

plot_42 =
  interact_plot(model_rlm_full, 
              pred = gull_insensitive_avg,
              modx = everyday_cog_avg,
              plot.points = TRUE,
              jitter = c(0.05,0.1),
              data = mydata,
              partial.residuals = FALSE,
              point.alpha = 0.3,
              point.size = 0.7,
              # colors = c("red", "blue", "green"),
              x.label = IV1_xlabel_str,
              y.label = DV_ylabel_str,
              pred.labels = NULL,
              modx.labels = NULL,
              mod2.labels = NULL,
              main.title = NULL,
              legend.main = mod_legend_title_str) +
  scale_x_continuous(
    breaks = c(2, 5),
    labels = IV1_xticks_str) +
  theme(
        # plot.subtitle=element_text(size = 14+4),
        # legend.position = c(.95, .95),
        # legend.position="top",
        legend.position="right",
        # legend.justification = c("right", "top"),
        # legend.box.just = "right",
        # legend.margin = margin(6, 6, 6, 6),
        legend.margin = margin(0, 2, 0, -6),
        legend.title=element_text(size=legend_all),
        legend.text=element_text(size=legend_all-2, margin = margin(l = 0.5)),
        # legend.spacing.y = unit(0.5, 'cm'),
        axis.line = element_line(size = 0.5, colour = "black", linetype=1),
        axis.text.x = element_text(size = axis_text), axis.text.y = element_text(size = axis_text), 
        axis.title.x = element_text(size = axis_title, face = "bold"), axis.title.y = element_text(size = axis_title, face = "bold"),
        # panel.grid.minor = element_line(size = 0.25, linetype = 'dotted',
                                        # colour = "black"),
        panel.grid = element_blank(),
        panel.background = element_blank())

plot_42
save_name = paste("revision_FEVS", mod_str, "INTER", IV1_str, sep = "_")
save_name = paste(Study_title, save_name, ".png", sep = "")
ggsave(paste(fig_folder,save_name, sep = "/"), width = w-3, height = h-2)
```

## figure with all panels
```{r}
ggarrange(plot_41, plot_42, 
          ncol = 2, nrow = 1, labels="AUTO", common.legend = TRUE)

ggsave(paste(fig_folder, "revision_study3_FEVS_inter.png", sep = "/"), width = w, height = h-2)
```




