---
title: "fairness sensitivty based on lmer results"
author: "Jen Yang"
date: "2025-4-10, last modified 2025-4-10"
output: 
  html_document:
    code_folding: hide
    toc: true
    toc_float:
      collapsed: false
      smooth_scroll: false
    hightlight: zenburn
    toc_depth: 6
---

```{r clean, include=FALSE}
# clean environment
rm(list = ls())
```

# Load libraries
```{r libraries, message=FALSE, warning=TRUE, include=FALSE}
library(car)
library(plyr)
library(foreign)
library(pscl)
library(boot)
library(MASS)
library(robust)
library(sfsmisc)
library(ggplot2)
library(reshape2)
library(ppcor)
library(ggrepel)
library(Hmisc)
library(tidyverse)
library(sandwich)
library(ggpubr)
library(interactions)
library(knitr)
library(twowaytests)
library(ggfortify)
library(interactions)
library(broom)
library(patchwork)
library(robustbase)
library(lmtest)
library(modelr)
library(Rmisc)
# library(raincloudplots)
library(cowplot)
library(readr)
library(PupillometryR)
library(ggpp)
library(estimatr)
library(skedastic)
library(ggpubr)
library(lubridate)
library(readxl)
library(gridExtra)
library(scales)
library(rstudioapi)
library(jsonlite)
library(rjson)
library(readr)
library(hBayesDM)
library(brms)
library(lme4)
library(lmerTest)
```

# set directories
```{r}
# current code location
gitrepo_path = "/Users/momocco/Documents/GitHub/srndna-ug/behavioral_analyses"

# location to save fits
fit_dir = paste(gitrepo_path,"fits", sep = "/")

# create the fits folder it it doesn't exist
if (!dir.exists(fit_dir)) {
  dir.create(fit_dir)
}

UGR_behavior_raw_path =
  "/Users/momocco/Documents/GitHub/rf1-sra/stimuli/Scan-Lets_Make_A_Deal/logs"
```

# load behavior data
```{r}
# load subject run inclusion list
sub_L3_list = data.frame(subjID = c("11600", "11472"))

sub_run_list = data.frame(subjID = c("11600", "11472", "11451"), 
                          run1 = c(1,1,0),
                          run2 = c(1,0,0))

sub_N = nrow(sub_L3_list)

# sub loop
s = 1
sub_s = sub_L3_list$subjID[s]

# extract run inclusion information
run_check = c(sub_run_list$run1[s], sub_run_list$run2[s])

## run loop
r_N = 2
r = 1
run_id = r-1

r_check = run_check[r]

if (r_check == 1) {
behavior_s_r_name = sprintf("sub-%d_task-ultimatum_run-%d_raw.csv",
                            as.numeric(sub_s), run_id)
  
  
behavior_s_r_df = 
  read.csv(paste(UGR_behavior_raw_path, 
                 sub_s,
                 behavior_s_r_name, sep = "/"), header = TRUE)

# recode condition and response
## condition:  1 = Commented out, 2 = Nonsocial, 3 = Social
## response: 1 = left, 2 = right
}

```

# write the based script that prepare data based on final subject list
# create for loop to loop through the subject list
# do the extraction, recycle previous code


# load behavior data
```{r}
all_trials_df = read.csv(file = paste(data_dir, "all_trials_brains.csv", sep = "/"), header = TRUE)
all_trials_df = all_trials_df[all_trials_df$missed == 0, ]

indiv_df = read.csv(paste(data_dir, "participant_check.csv", sep = "/"), header = TRUE)  %>%
  mutate(age_bi = case_when(age <= 36 ~ "younger",
                            age > 36 ~ "older"))

all_trials_df = merge(all_trials_df, indiv_df, by.x = "subjID", by.y = "participant_id")

L3_47_df = read.csv(paste(data_dir, "participant_L3_47.csv", sep = "/"), header = TRUE)

sublist_final = L3_47_df %>% dplyr::select(subjID)

all_trials_df = all_trials_df[all_trials_df$subjID %in% sublist_final$subjID,] 

all_trials_df = all_trials_df %>% 
  mutate(ingroup = relevel(as.factor(ingroup), ref = "0"),
         human = relevel(as.factor(human), ref = "0"),
         age_bi = relevel(as.factor(age_bi), ref = "younger"),
         block_fair = relevel(as.factor(block_fair), ref = "0"),
         accept = relevel(as.factor(accept), ref = "0")) %>% 
  dplyr::select(subjID, offer, accept, human, ingroup, block_fair, age_bi, missed)

all_trials_human_df = all_trials_df[all_trials_df$human == 1,]

```

# sensitivity
## human only
### ingroup
```{r}
## ingroup offer sensitivity
ingroup_df = all_trials_human_df[all_trials_human_df$ingroup == 1,]
ingroup_mlm = glmer(accept ~ offer + (1+offer|subjID), 
                 data = ingroup_df, 
                 family = binomial)
summary(ingroup_mlm)

# ingroup_df = all_trials_human_df[all_trials_human_df$ingroup == 1,]
# ingroup_mlm_2 = glmer(accept ~ offer + (1+offer||subjID), 
#                  data = ingroup_df, 
#                  family = binomial)
# summary(ingroup_mlm_2)
# anova(ingroup_mlm_1, ingroup_mlm_2, refit = F)

ingroup_fixed_effects <- fixef(ingroup_mlm) %>% 
  as.data.frame() %>% 
  rownames_to_column(var = "fixed")

ingroup_random_effects <- ranef(ingroup_mlm, condVar = FALSE) %>% 
  as.data.frame()

ingroup_random_effects = ingroup_random_effects[ingroup_random_effects$term == "offer",] %>% 
  mutate(ingroup = condval,
         ingroup_fixed_rand = 
           condval + ingroup_fixed_effects$.[ingroup_fixed_effects$fixed == "offer"],
         subjID = grp) %>% 
  dplyr::select(subjID, ingroup, ingroup_fixed_rand)
```

### outgroup
```{r}
## outgroup offer sensitivity
outgroup_df = all_trials_human_df[all_trials_human_df$ingroup == 0,]
outgroup_mlm = glmer(accept ~ offer + (1+offer|subjID), 
                    data = outgroup_df, 
                    family = binomial)
summary(outgroup_mlm)

outgroup_fixed_effects <- fixef(outgroup_mlm) %>% 
  as.data.frame() %>% 
  rownames_to_column(var = "fixed")

outgroup_random_effects <- ranef(outgroup_mlm, condVar = FALSE) %>% 
  as.data.frame()

outgroup_random_effects = outgroup_random_effects[outgroup_random_effects$term == "offer",] %>% 
  mutate(outgroup = condval,
         outgroup_fixed_rand = 
           condval + outgroup_fixed_effects$.[outgroup_fixed_effects$fixed == "offer"],
         subjID = grp) %>% 
  dplyr::select(subjID, outgroup, outgroup_fixed_rand)
```

```{r}
## in-out
in_out_rand_df = merge(ingroup_random_effects, outgroup_random_effects, by = "subjID") %>% 
  mutate(in_out_rand_logit = ingroup - outgroup,
         in_out_full_logit = ingroup_fixed_rand - outgroup_fixed_rand,
         in_out_prob = (exp(ingroup) / (1 + exp(ingroup))) - exp(outgroup) / (1 + exp(outgroup))) %>%
  dplyr::select(subjID, ingroup_fixed_rand, outgroup_fixed_rand, in_out_rand_logit, in_out_full_logit, in_out_prob)
```

## computer
```{r}
## computer offer sensitivity
computer_df = all_trials_human_df[all_trials_df$human == 0,]
computer_mlm = glmer(accept ~ offer + (1+offer|subjID), 
                     data = computer_df, 
                     family = binomial)
# summary(computer_mlm)

computer_random_effects <- ranef(computer_mlm, condVar = FALSE) %>% 
  as.data.frame()
computer_random_effects = computer_random_effects[computer_random_effects$term == "offer",] %>% 
  mutate(computer = condval,
         subjID = grp) %>% 
  dplyr::select(subjID, computer)

## human offer sensitivity
human_df = all_trials_human_df[all_trials_df$human == 1,]
human_mlm = glmer(accept ~ offer + (1+offer|subjID), 
                     data = human_df, 
                     family = binomial)
# summary(human_mlm)

human_random_effects <- ranef(human_mlm, condVar = FALSE) %>% 
  as.data.frame()
human_random_effects = human_random_effects[human_random_effects$term == "offer",] %>% 
  mutate(human = condval,
         subjID = grp) %>% 
  dplyr::select(subjID, human)

## soc-nonsoc
soc_nonsoc_rand_df = merge(computer_random_effects, human_random_effects, by = "subjID") %>% 
  mutate(soc_nonsoc_logit = human - computer,
         soc_nonsoc_prob = (exp(human) / (1 + exp(human))) - exp(computer) / (1 + exp(computer))) %>% 
  dplyr::select(subjID, soc_nonsoc_logit, soc_nonsoc_prob)
```

# human, norm (pause for now)
```{r}
# norm_fit_1 = glmer(accept ~ ingroup +
#                    (1+ingroup|subjID) , 
#                  data = all_trials_human_df, 
#                  family = binomial)
# summary(norm_fit_1)
# 
# norm_fit_2 = glmer(accept ~ ingroup +
#                    (1+ingroup||subjID) , 
#                  data = all_trials_human_df, 
#                  family = binomial)
# summary(norm_fit_2)
# anova(norm_fit_1, norm_fit_2, refit = F)
```


# in_out_sens_df for L3 w/ cov
```{r}
## random sensitivity only
in_out_sens_df = in_out_rand_df %>% merge(., L3_47_df, by = "subjID") %>% 
  mutate(in_out_demean = in_out_rand_logit - mean(in_out_rand_logit),
         in_out_young = in_out_demean*younger,
         in_out_old = in_out_demean*older,
         ones = 1)
write.csv(in_out_sens_df, paste(data_dir, "in_out_sensitivity_logit.csv", sep = "/"),
          row.names = FALSE)

in_out_sens_df = in_out_sens_df %>% 
  select(subjID, ones, ismale, tsnr, fd_mean, RT, 
         younger, older,
         in_out_young, in_out_old)
write.csv(in_out_sens_df, paste(data_dir, "L3_cov_in_out_sensitivity_logit.csv", sep = "/"),
          row.names = FALSE)

## full slope, rand + fixed
in_out_sens_df = in_out_rand_df %>% merge(., L3_47_df, by = "subjID") %>% 
  mutate(in_out_demean = in_out_full_logit - mean(in_out_full_logit),
         in_out_young = in_out_demean*younger,
         in_out_old = in_out_demean*older,
         ones = 1)
write.csv(in_out_sens_df, paste(data_dir, "in_out_sensitivity_full_logit.csv", sep = "/"),
          row.names = FALSE)

in_out_sens_df = in_out_sens_df %>% 
  select(subjID, ones, ismale, tsnr, fd_mean, RT, 
         younger, older,
         in_out_young, in_out_old)
write.csv(in_out_sens_df, paste(data_dir, "L3_cov_in_out_sensitivity_full_logit.csv", sep = "/"),
          row.names = FALSE)
```

# soc_nonsoc_sens_df for L3 w/ cov
```{r}
soc_nonsoc_sens_df = soc_nonsoc_rand_df %>% merge(., L3_47_df, by = "subjID") %>% 
  mutate(soc_nonsoc_demean = soc_nonsoc_logit - mean(soc_nonsoc_logit),
         soc_nonsoc_young = soc_nonsoc_demean*younger,
         soc_nonsoc_old = soc_nonsoc_demean*older,
         ones = 1) %>% 
  select(subjID, ones, ismale, tsnr, fd_mean, RT, 
         younger, older,
         soc_nonsoc_young, soc_nonsoc_old)
write.csv(soc_nonsoc_sens_df, paste(data_dir, "L3_cov_soc_nonsoc_sensitivity_logit.csv", sep = "/"),
          row.names = FALSE)
```

# in_out_sens_df for L3 w/ cov
```{r}
in_out_sens_df = in_out_rand_df %>% merge(., L3_47_df, by = "subjID") %>% 
  mutate(in_out_demean = in_out_prob - mean(in_out_prob),
         in_out_young = in_out_demean*younger,
         in_out_old = in_out_demean*older,
         ones = 1) %>% 
  select(subjID, ones, ismale, tsnr, fd_mean, RT, 
         younger, older,
         in_out_young, in_out_old)
write.csv(in_out_sens_df, paste(data_dir, "L3_cov_in_out_sensitivity_prob.csv", sep = "/"),
          row.names = FALSE)
```

# soc_nonsoc_sens_df for L3 w/ cov
```{r}
soc_nonsoc_sens_df = soc_nonsoc_rand_df %>% merge(., L3_47_df, by = "subjID") %>% 
  mutate(soc_nonsoc_demean = soc_nonsoc_prob - mean(soc_nonsoc_prob),
         soc_nonsoc_young = soc_nonsoc_demean*younger,
         soc_nonsoc_old = soc_nonsoc_demean*older,
         ones = 1) %>% 
  select(subjID, ones, ismale, tsnr, fd_mean, RT, 
         younger, older,
         soc_nonsoc_young, soc_nonsoc_old)
write.csv(soc_nonsoc_sens_df, paste(data_dir, "L3_cov_soc_nonsoc_sensitivity_prob.csv", sep = "/"),
          row.names = FALSE)
```
