---
title: "singletrial_hypotheses_tests_srndnaUGR"
author: "Jen Yang"
date: "2025-04-09, last modified 2025-04-09"
output: 
  html_document:
    code_folding: hide
    toc: true
    toc_float:
      collapsed: false
      smooth_scroll: false
    hightlight: zenburn
    toc_depth: 6
---

```{r clean, include=FALSE}
# clean environment
rm(list = ls())
```

# Load libraries
```{r libraries, message_bi=FALSE, warning=TRUE, include=FALSE}
library(car)
library(plyr)
library(foreign)
library(pscl)
library(boot)
library(MASS)
library(robust)
library(sfsmisc)
library(ggplot2)
library(reshape2)
library(ppcor)
library(ggrepel)
library(Hmisc)
library(tidyverse)
library(sandwich)
library(ggpubr)
library(interactions)
library(knitr)
library(twowaytests)
library(ggfortify)
library(interactions)
library(broom)
library(patchwork)
library(robustbase)
library(lmtest)
library(modelr)
library(Rmisc)
# library(raincloudplots)
library(cowplot)
library(readr)
library(PupillometryR)
library(ggpp)
library(estimatr)
library(skedastic)
library(ggpubr)
library(lubridate)
library(readxl)
library(gridExtra)
library(scales)
library(rstudioapi)
library(jsonlite)
library(rjson)
library(readr)
library(hBayesDM)
library(brms)
library(emmeans)
library(mediation)
library(here)
library(lme4)
library(lmerTest)
library(broom.mixed)
library(easyRT)
library(parameters)
library(effectsize)
library(effects)
library(lmerTest)
library(ez)
library(afex)
library(marginaleffects)
library(magrittr)
```

```{r}
set.seed(123)
```

# directories
```{r}
gitrepo_path = "/Users/momocco/Documents/GitHub/srndna-ug/behavioral_analyses"

data_dir = paste(gitrepo_path,"data", sep = "/")
codes_dir = paste(gitrepo_path, "codes", sep = "/")
fit_dir = paste(gitrepo_path,"fits", sep = "/")
figure_dir = paste(gitrepo_path,"figures", sep = "/")
```

# load and prepare data
```{r}
# load subs
all_trials_df = read.csv(paste(data_dir, "all_trials_brains.csv", sep = "/"), header = TRUE) %>% 
  .[.$missed == 0,]

colnames(all_trials_df)[colnames(all_trials_df) == "subjID"] <- "participant_id"
indiv_df = read.csv(paste(data_dir, "participant_check.csv", sep = "/"), header = TRUE)  %>%
  mutate(age_bi = case_when(age <= 36 ~ "younger",
                            age > 36 ~ "older"))

all_trials_df = merge(all_trials_df, indiv_df, by.x = "participant_id", by.y = "participant_id")

sublist_final = read.csv(paste(data_dir, "participant_L3_47.csv", sep = "/"), header = TRUE)

all_trials_df = all_trials_df[all_trials_df$participant_id %in% sublist_final$subjID,]
```

## recode group and age
```{r}
## add a categorical variable that differentiate three groups
all_trials_df = all_trials_df %>% 
  mutate(group_tri = as.factor(case_when(human == 0 ~ 0, # computer
                               human == 1 & ingroup == 0 ~ 1, # outgroup
                               human == 1 & ingroup == 1 ~ 2))) # ingroup
# all_trials_df$group_tri = relevel(all_trials_df$group_tri, ref = "0") # computer

all_trials_df = all_trials_df %>% mutate(human = as.factor(human))

all_trials_df$group_tri = relevel(all_trials_df$group_tri, ref = "1") # outgroup

all_trials_df$age_bi = relevel(as.factor(all_trials_df$age_bi), ref = "younger")

all_trials_df = all_trials_df %>% 
  mutate(age_bi_dummy = case_when(age_bi == "younger" ~ 0,
                                  age_bi == "older" ~ 1)
         )
```

## factorize vars as needed
```{r}
factor_col_names = c("participant_id", "run", "missed", "accept",
                     "ingroup", "block_fair", "sex")
all_trials_df[factor_col_names] %<>% lapply(., factor) 
```

## add fdmean, tsnr vars to data
```{r}
fmri_control_data = 
  read.csv(paste(data_dir, "Task-ultimatum_Level-Run_Outlier-info.csv", 
                 sep = "/"), header = TRUE) %>% 
  filter(Sub %in% sublist_final$subjID == 1) %>% 
  # mutate(subjID = Sub) %>% 
  select(-task, -outlier_run_Custom1)

all_trials_df = merge(all_trials_df, fmri_control_data, 
                      by.x = c("participant_id", "run"),
                      by.y = c("Sub", "run"))
```

## remove incomplete rows
```{r}
all_trials_df %<>% na.omit 
```


# P2 NH1A, group_tri & age_bi respectively
"NH1A) The anterior insula (ins), dorsal anterior cingulate cortex (dACC), ventromedial prefrontal cortex (vmPFC), and ventral striatum (VS) will be associated with choice." [ins, dACC, vmPFC, VS]

brain ~ accept * age(or group) + (1|participant)

## prepare empty df to store results
```{r}
results_cols = c("brain", "mod", "Coef", "p", "p_check", "p_0125_check")
results_df = data.frame(matrix(nrow = 4*(3+1), ncol = length(results_cols)))
colnames(results_df) = results_cols
```

## anterior insula
### choice ~ anterior insula * age * group3 + controls, won't converge
```{r}
P2_NH1_AI_age_group_m1 =
  glmer(accept ~ anteriorinsula_corrected * age_bi * group_tri + offer +
         tsnr + fd_mean + response_time +
         # (1 + anteriorinsula_corrected + response_time || participant_id), # won't converge
          # (1 + response_time || participant_id), # won't converge
          (1| participant_id),
       data = all_trials_df,
       family = binomial)
summary(P2_NH1_AI_age_group_m1)
```

### choice ~ anterior insula * age + controls, NON
```{r}
P2_NH1_AI_age_m1 =
  glmer(accept ~ anteriorinsula_corrected * age_bi + offer +
         tsnr + fd_mean + response_time +
         (1 + anteriorinsula_corrected + response_time || participant_id),
       data = all_trials_df,
       family = binomial)
summary(P2_NH1_AI_age_m1)
```

### choice ~ anterior insula * group_tri + controls, won't converge
```{r}
P2_NH1_AI_group_m1 =
  glmer(accept ~ anteriorinsula_corrected * group_tri + offer +
         tsnr + fd_mean + response_time +
         # (1 + anteriorinsula_corrected + response_time || participant_id), # won't converge
          # (1 + response_time || participant_id), # won't converge
          (1| participant_id),
       data = all_trials_df,
       family = binomial)
summary(P2_NH1_AI_group_m1)
```

### choice ~ anterior insula * human + controls, SIG
```{r}
P2_NH1_AI_human_m1 =
  glmer(accept ~ anteriorinsula_corrected * human + offer +
         tsnr + fd_mean + response_time +
         (1 | participant_id),
         # (1 + anteriorinsula_corrected + response_time | participant_id), # won't converge
         # (1 + response_time || participant_id), # won't converge
       data = all_trials_df,
       family = binomial)
summary(P2_NH1_AI_human_m1)
```

#### plot
```{r}
# Compute partial residuals for X
# Step 1: Residualize y by Z and random effects
P2_NH1_AI_human_m1_pr_y = glmer(accept ~ human + offer +
                                tsnr + fd_mean + response_time +
                                (1 | participant_id),
                              data = all_trials_df,
                              family = binomial)


res.accept_pr <- residuals(P2_NH1_AI_human_m1_pr_y)

# # Step 2: Residualize X by Z and random effects
P2_NH1_AI_human_m1_pr_x = lmer(anteriorinsula_corrected ~ human + offer +
                                tsnr + fd_mean + response_time +
                                (1 | participant_id),
                              data = all_trials_df)
res.AI_pr <- residuals(P2_NH1_AI_human_m1_pr_x)

# Create partial residual plot
pr_plot_df = data.frame(res.x = res.AI_pr,
                        res.y = res.accept_pr,
                        AI = all_trials_df$anteriorinsula_corrected,
                        human = all_trials_df$human)

ggplot(pr_plot_df, aes(x = AI, y = res.y, color = human)) +
  # geom_point() +
  geom_smooth(method = "lm", se = F) +
  labs(x = "Partial residual for X (controlling for Z and participant)",
       y = "Partial residual for y (controlling for Z and participant)") +
  theme_minimal()

ggplot(pr_plot_df, aes(x = res.x, y = res.y, color = human)) +
  # geom_point() +
  geom_smooth(method = "lm", se = F) +
  labs(x = "Partial residual for X (controlling for Z and participant)",
       y = "Partial residual for y (controlling for Z and participant)") +
  theme_minimal()
```

### choice ~ anterior insula * similar + controls, NON
```{r}
all_trials_similar_df = filter(all_trials_df, human == "1")
P2_NH1_AI_similar_m1 =
  glmer(accept ~ anteriorinsula_corrected * ingroup + offer +
         tsnr + fd_mean + response_time +
          (1 + response_time || participant_id),
         # (1 + anteriorinsula_corrected + response_time || participant_id), # won't converge
       data = all_trials_similar_df,
       family = binomial)
summary(P2_NH1_AI_similar_m1)
```

### choice ~ anterior insula + controls, NON
```{r}
all_trials_similar_df = filter(all_trials_df, human == "1")
P2_NH1_AI_similar_m1 =
  glmer(accept ~ anteriorinsula_corrected + offer + 
         tsnr + fd_mean + response_time +
         # (1 + anteriorinsula_corrected + response_time || participant_id),
        (1 + response_time || participant_id),
       data = all_trials_similar_df,
       family = binomial)
summary(P2_NH1_AI_similar_m1)
```

## dACC
### choice ~ dACC * age * group3 + controls, fail converge
```{r}
## won't converge
P2_NH1_dacc_age_group_m1 =
  glmer(accept ~ dacc_corrected * age_bi * group_tri + offer +
         tsnr + fd_mean + response_time +
         # (1 + dacc_corrected + response_time || participant_id),
        (1| participant_id),
       data = all_trials_df,
       family = binomial)
summary(P2_NH1_dacc_age_group_m1)
```

### choice ~ dACC * age + controls, NON
```{r}
P2_NH1_dacc_age_m1 =
  glmer(accept ~ dacc_corrected * age_bi + offer +
         tsnr + fd_mean + response_time +
         # (1 + dacc_corrected + response_time || participant_id), # won't converge
          # (1 + response_time || participant_id), # won't converge
        (1 | participant_id),
       data = all_trials_df,
       family = binomial)
summary(P2_NH1_dacc_age_m1)
```

### choice ~ dACC * group3 + controls, NON
```{r}
P2_NH1_dacc_group_m1 =
  glmer(accept ~ dacc_corrected * group_tri + offer +
         tsnr + fd_mean + response_time +
         # (1 + dacc_corrected + response_time || participant_id), # won't converge
          # (1 + response_time || participant_id), # won't converge
          (1 | participant_id),
       data = all_trials_df,
       family = binomial)
summary(P2_NH1_dacc_group_m1)
```

### choice ~ dACC * human + controls, won't converge
```{r}
P2_NH1_dacc_human_m1 =
  glmer(accept ~ dacc_corrected * human + offer +
         tsnr + fd_mean + response_time +
         # (1 + dacc_corrected + response_time || participant_id), # won't converge
        # (1 + response_time || participant_id), # won't converge
          (1 | participant_id),
       data = all_trials_df,
       family = binomial)
summary(P2_NH1_dacc_human_m1)
```

### choice ~ dacc * similar + controls, NON
```{r}
all_trials_similar_df = filter(all_trials_df, human == "1")
P2_NH1_dacc_similar_m1 =
  glmer(accept ~ dacc_corrected * ingroup + offer +
          tsnr + fd_mean + response_time +
          # (1 + dacc_corrected + response_time || participant_id), # won't converge
          # (1 + response_time || participant_id), # won't converge
          (1 | participant_id),
        data = all_trials_similar_df,
        family = binomial)
summary(P2_NH1_dacc_similar_m1)
```

### choice ~ dacc + controls, NON
```{r}
P2_NH1_dacc_m1 =
  glmer(accept ~ dacc_corrected + offer +
          tsnr + fd_mean + response_time +
          (1 + response_time || participant_id),
        data = all_trials_df,
        family = binomial)
summary(P2_NH1_dacc_m1)
```

## VS
### choice ~ VS * age * group3 + controls, NON
```{r}
P2_NH1_VS_age_group_m1 =
  glmer(accept ~ VS_corrected * age_bi * group_tri + offer +
          tsnr + fd_mean + response_time +
          # (1 + VS_corrected + response_time || participant_id), # won't converge
          # (1 + response_time || participant_id), # won't converge
          (1 | participant_id),
        data = all_trials_df,
        family = binomial)
summary(P2_NH1_VS_age_group_m1)
```

### choice ~ VS * age + controls, NON
```{r}
P2_NH1_VS_age_m1 =
  glmer(accept ~ VS_corrected * age_bi + offer +
          tsnr + fd_mean + response_time +
          # (1 + VS_corrected + response_time || participant_id), # won't converge
          # (1 + response_time || participant_id), # won't converge
          (1 | participant_id),
        data = all_trials_df,
        family = binomial)
summary(P2_NH1_VS_age_m1)
```

### choice ~ VS * group3 + controls, won't converge
```{r}
P2_NH1_VS_group_m1 =
  glmer(accept ~ VS_corrected * group_tri + offer +
          tsnr + fd_mean + response_time +
          # (1 + VS_corrected + response_time || participant_id), # won't converge
          # (1 + response_time || participant_id), # won't converge
          # (1 | participant_id), # won't converge
        data = all_trials_df,
        family = binomial)
summary(P2_NH1_VS_group_m1)
```



### choice ~ VS * human + controls, NON
```{r}
P2_NH1_VS_human_m1 =
  glmer(accept ~ VS_corrected * human + offer +
          tsnr + fd_mean + response_time +
          # (1 + VS_corrected + response_time || participant_id), # won't converge
          (1 + response_time || participant_id),
        data = all_trials_df,
        family = binomial)
summary(P2_NH1_VS_human_m1)
```
### choice ~ VS * similar + controls, NON
```{r}
all_trials_similar_df = filter(all_trials_df, human == "1")
P2_NH1_VS_similar_m1 =
  glmer(accept ~ VS_corrected * ingroup + offer +
          tsnr + fd_mean + response_time +
          # (1 + VS_corrected + response_time || participant_id), # won't converge
          (1 + response_time || participant_id),
        data = all_trials_similar_df,
        family = binomial)
summary(P2_NH1_VS_similar_m1)
```
### choice ~ VS + controls, NON
```{r}
P2_NH1_VS_m1 =
  glmer(accept ~ VS_corrected + offer +
          tsnr + fd_mean + response_time +
          # (1 + response_time || participant_id), # won't converge
        (1 | participant_id),
        data = all_trials_df,
        family = binomial)
summary(P2_NH1_VS_m1)
```
## vmpfc
### choice ~ vmpfc * age * group3 + controls, won't converge
```{r}
P2_NH1_vmpfc_age_group_m1 =
  glmer(accept ~ vmpfc_corrected * age_bi * group_tri + offer +
          tsnr + fd_mean + response_time +
          # (1 + vmpfc_corrected + response_time || participant_id), # won't converge
          # (1 + response_time || participant_id), # won't converge
          # (1 | participant_id), # won't converge
        data = all_trials_df,
        family = binomial)
summary(P2_NH1_vmpfc_age_group_m1)
```

### choice ~ vmpfc * age + controls, NON
```{r}
P2_NH1_vmpfc_age_m1 =
  glmer(accept ~ vmpfc_corrected * age_bi + offer +
          tsnr + fd_mean + response_time +
          (1 + vmpfc_corrected + response_time || participant_id),
        data = all_trials_df,
        family = binomial)
summary(P2_NH1_vmpfc_age_m1)
```
### choice ~ vmpfc * group3 + controls, won't converge
```{r}
P2_NH1_vmpfc_group_m1 =
  glmer(accept ~ vmpfc_corrected * group_tri + offer +
          tsnr + fd_mean + response_time +
          # (1 + vmpfc_corrected + response_time || participant_id), # won't converge
          # (1 + response_time || participant_id), # won't converge
          # (1 | participant_id), # won't converge
          data = all_trials_df,
        family = binomial)
summary(P2_NH1_vmpfc_group_m1)
```

### choice ~ vmpfc * human + controls, NON
```{r}
P2_NH1_vmpfc_human_m1 =
  glmer(accept ~ vmpfc_corrected * human + offer +
          tsnr + fd_mean + response_time +
          # (1 + vmpfc_corrected + response_time || participant_id), # won't converge
          (1 + response_time || participant_id),
        data = all_trials_df,
        family = binomial)
summary(P2_NH1_vmpfc_human_m1)
```

### choice ~ vmpfc * similar + controls, NON
```{r}
all_trials_similar_df = filter(all_trials_df, human == "1")
P2_NH1_vmpfc_similar_m1 =
  glmer(accept ~ vmpfc_corrected * ingroup + offer +
          tsnr + fd_mean + response_time +
          # (1 + vmpfc_corrected + response_time || participant_id), # won't converge
          # (1 + response_time || participant_id), # won't converge
          (1 | participant_id),
        data = all_trials_similar_df,
        family = binomial)
summary(P2_NH1_vmpfc_similar_m1)
```

### choice ~ vmpfc + controls, NON
```{r}
P2_NH1_vmpfc_m1 =
  glmer(accept ~ vmpfc_corrected + offer +
          tsnr + fd_mean + response_time +
          (1 + vmpfc_corrected + response_time || participant_id),
        data = all_trials_df,
        family = binomial)
summary(P2_NH1_vmpfc_m1)
```

# to continue

### clean single trial results
```{r}
results_df = results_df %>% 
  mutate(p_check = case_when(p >=0.05 ~ NA,
                                p < 0.05 ~ "*" ),
         p_0125_check = case_when(p >=0.0125 ~ NA,
                                p < 0.0125 ~ "*"),
         p = round(p,4))
```



# single trial exploratory
## accept ~ brain * block
```{r}
## not sig
antIns_block_fit <- glmer(accept ~ anteriorinsula_corrected * block_fair +
                                        (1|participant_id),
                                      data = all_trials_df,
                                      family = binomial)
summary(antIns_block_fit)

#@ not sig
VS_block_fit <- glmer(accept ~ VS_corrected * block_fair +
                                        (1|participant_id),
                                      data = all_trials_df,
                                      family = binomial)
summary(VS_block_fit)

## not sig
dacc_block_fit <- glmer(accept ~ dacc_corrected * block_fair +
                                        (1|participant_id),
                                      data = all_trials_df,
                                      family = binomial)
summary(dacc_block_fit)

## not sig
vmpfc_block_fit <- glmer(accept ~ vmpfc_corrected * block_fair +
                                        (1|participant_id),
                                      data = all_trials_df,
                                      family = binomial)
summary(vmpfc_block_fit)
```

## brain ~ offer + group + block + accept
```{r}
# vmpfc_task_fit <- lmer(vmpfc_corrected ~ (1 |participant_id),
#                                       data = all_trials_df)
# summary(vmpfc_task_fit)
vmpfc_task_fit <- lm(vmpfc_corrected ~ offer + block_fair + accept + group_tri + age_bi,
                                      data = all_trials_df)
summary(vmpfc_task_fit)


# VS_task_fit <- lmer(VS_corrected ~ (1 |participant_id),
#                                       data = all_trials_df)
# summary(VS_task_fit)
VS_task_fit <- lm(VS_corrected ~ offer + block_fair + accept + group_tri + age_bi,
                                      data = all_trials_df)
summary(VS_task_fit)

# anteriorinsula_task_fit <- lmer(anteriorinsula_corrected ~ (1 |participant_id),
#                                       data = all_trials_df)
# summary(anteriorinsula_task_fit)
anteriorinsula_task_fit <- lm(anteriorinsula_corrected ~ offer + block_fair + accept + group_tri + age_bi,
                  data = all_trials_df)
summary(anteriorinsula_task_fit)

# dacc_task_fit <- lmer(dacc_corrected ~ (1 |participant_id),
#                                       data = all_trials_df)
# summary(dacc_task_fit)
dacc_task_fit <- lm(dacc_corrected ~ offer + block_fair + accept + group_tri + age_bi,
                  data = all_trials_df)
summary(dacc_task_fit)
```


```{r}
dacc_vmpfc_fit = lm(dacc_corrected ~ vmpfc_corrected * age_bi,
                  data = all_trials_df)
summary(dacc_vmpfc_fit)

VS_vmpfc_fit = lm(VS_corrected ~ vmpfc_corrected * age_bi,
                  data = all_trials_df)
summary(VS_vmpfc_fit)

anteriorinsula_vmpfc_fit = lm(anteriorinsula_corrected ~ vmpfc_corrected * age_bi,
                  data = all_trials_df)
summary(anteriorinsula_vmpfc_fit)

anteriorinsula_VS_fit = lm(anteriorinsula_corrected ~ VS_corrected * age_bi,
                  data = all_trials_df)
summary(anteriorinsula_VS_fit)

anteriorinsula_dacc_fit = lm(anteriorinsula_corrected ~ dacc_corrected * age_bi,
                  data = all_trials_df)
summary(anteriorinsula_dacc_fit)

VS_dacc_fit = lm(VS_corrected ~ dacc_corrected * age_bi,
                  data = all_trials_df)
summary(VS_dacc_fit)
```








## if brain contribute above behavior model
### base behavior model
```{r}
all_trials_df = na.omit(all_trials_df)

beh_full_fit = glmer(accept ~ offer * age_bi + block_fair + 
                                       (1|participant_id),
                                     data = all_trials_df,
                                     family = binomial)

summary(beh_full_fit)
```
### prepare empty df for results
```{r}
# brain_behavior_formula_cols = c("brain", "formula", "chisq_p", "sig_check")
# brain_behavior_formula_df = data.frame(matrix(nrow = 4, ncol = length(brain_behavior_formula_cols)))
# colnames(brain_behavior_formula_df) = brain_behavior_formula_cols

brain_behavior_cols = c("brain", "predictor", "pre_p", "pre_sig", "model_p", "model_sig")
brain_behavior_df = data.frame(matrix(nrow = 4, ncol = length(brain_behavior_cols)))
colnames(brain_behavior_df) = brain_behavior_cols
```

### VS,offer sig
```{r}
## full model, converged
# beh_VS_full_0_fit = glmer(accept ~ offer * age_bi + block_fair + 
#                             VS_corrected * offer * age_bi + 
#                             VS_corrected * block_fair +
#                             (1|participant_id),
#                           data = all_trials_df,
#                           family = binomial)
# 
# summary(beh_VS_full_0_fit)

## reduced model, no 3-way interaction
# beh_VS_full_1_fit = glmer(accept ~ offer * age_bi + block_fair + 
#                             VS_corrected * offer * age_bi -
#                             VS_corrected:offer:age_bi +
#                             VS_corrected * block_fair +
#                             (1|participant_id),
#                           data = all_trials_df,
#                           family = binomial)
# summary(beh_VS_full_1_fit)

## no diff in fit quality between full and reduced model. use reduced model for later comparison
# anova(beh_VS_full_0_fit, beh_VS_full_1_fit, refit = T)

## reduced model, brain * age
beh_VS_full_2_fit = glmer(accept ~ offer * age_bi + block_fair + 
                            VS_corrected * age_bi +
                            (1|participant_id),
                          data = all_trials_df,
                          family = binomial)
summary(beh_VS_full_2_fit)

anova_predictor_test = data.frame(Anova(beh_VS_full_2_fit))
anova_model_test = data.frame(anova(beh_full_fit, beh_VS_full_2_fit, refit = TRUE))

N_nonNA_results = sum(!is.na(brain_behavior_df$brain))
brain_name = "VS_corrected"

predictor_name = paste("age_bi", brain_name, sep = ":")
brain_behavior_df$brain[N_nonNA_results+1] = brain_name
brain_behavior_df$predictor[N_nonNA_results+1] = predictor_name

brain_behavior_df$pre_p[N_nonNA_results+1] = 
  anova_predictor_test$Pr..Chisq.[row.names(anova_predictor_test) == predictor_name]

brain_behavior_df$model_p[N_nonNA_results+1] = 
  anova_model_test$Pr..Chisq.[2]
```
### dacc, not sig but close
```{r}
# beh_dacc_full_0_fit = glmer(accept ~ offer * age_bi + block_fair + 
#                           dacc_corrected * offer * age_bi + dacc_corrected * block_fair +
#                           (1|participant_id),
#                         data = all_trials_df,
#                         family = binomial)
# 
# summary(beh_dacc_full_0_fit)

# beh_dacc_full_1_fit = glmer(accept ~ offer * age_bi + block_fair + 
#                           dacc_corrected * offer * age_bi - 
#                             dacc_corrected:offer:age_bi +
#                             dacc_corrected * block_fair +
#                           (1|participant_id),
#                         data = all_trials_df,
#                         family = binomial)

beh_dacc_full_2_fit = glmer(accept ~ offer * age_bi + block_fair +
                          dacc_corrected * age_bi +
                          (1|participant_id),
                        data = all_trials_df,
                        family = binomial)
summary(beh_dacc_full_2_fit)

anova_predictor_test = data.frame(Anova(beh_dacc_full_2_fit))
anova_model_test = data.frame(anova(beh_full_fit, beh_dacc_full_2_fit, refit = TRUE))

N_nonNA_results = sum(!is.na(brain_behavior_df$brain))
brain_name = "dacc_corrected"

predictor_name = paste("age_bi", brain_name, sep = ":")
brain_behavior_df$brain[N_nonNA_results+1] = brain_name
brain_behavior_df$predictor[N_nonNA_results+1] = predictor_name

brain_behavior_df$pre_p[N_nonNA_results+1] = 
  anova_predictor_test$Pr..Chisq.[row.names(anova_predictor_test) == predictor_name]

brain_behavior_df$model_p[N_nonNA_results+1] = 
  anova_model_test$Pr..Chisq.[2]
```

### vmpfc, not sig
```{r}
# beh_vmpfc_full_0_fit = glmer(accept ~ offer * age_bi + block_fair + 
#                             vmpfc_corrected * offer * age_bi + vmpfc_corrected * block_fair +
#                             (1|participant_id),
#                           data = all_trials_df,
#                           family = binomial)
# 
# summary(beh_vmpfc_full_0_fit)

# beh_vmpfc_full_1_fit = glmer(accept ~ offer * age_bi + block_fair + 
#                             vmpfc_corrected * offer * age_bi - 
#                               vmpfc_corrected:offer:age_bi +
#                               vmpfc_corrected * block_fair +
#                             (1|participant_id),
#                           data = all_trials_df,
#                           family = binomial)

beh_vmpfc_full_2_fit = glmer(accept ~ offer * age_bi + block_fair + 
                            vmpfc_corrected * age_bi - 
                            (1|participant_id),
                          data = all_trials_df,
                          family = binomial)

anova_predictor_test = data.frame(Anova(beh_vmpfc_full_2_fit))
anova_model_test = data.frame(anova(beh_full_fit, beh_vmpfc_full_2_fit, refit = TRUE))

N_nonNA_results = sum(!is.na(brain_behavior_df$brain))
brain_name = "vmpfc_corrected"

predictor_name = paste("age_bi", brain_name, sep = ":")
brain_behavior_df$brain[N_nonNA_results+1] = brain_name
brain_behavior_df$predictor[N_nonNA_results+1] = predictor_name

brain_behavior_df$pre_p[N_nonNA_results+1] = 
  anova_predictor_test$Pr..Chisq.[row.names(anova_predictor_test) == predictor_name]

brain_behavior_df$model_p[N_nonNA_results+1] = 
  anova_model_test$Pr..Chisq.[2]
```

### mark sig results
```{r}
brain_behavior_df = brain_behavior_df %>% 
  mutate(pre_sig = case_when(pre_p >=0.05 ~ NA,
                             pre_p < 0.05 ~ "*"),
         model_sig = case_when(model_p >=0.05 ~ NA,
                    model_p < 0.05 ~ "*"))
```


### anteriorinsula_corrected, very sig
```{r}
## full model won't converge
# beh_antIns_full_0_fit = glmer(accept ~ 
#                             anteriorinsula_corrected * offer * age_bi +
#                               anteriorinsula_corrected * block_fair +
#                             (1|participant_id),
#                           data = all_trials_df,
#                           family = binomial)
# allFit(beh_antIns_full_0_fit)

## reduced model based on purpose of test - see potentional interactions between brain and other non-brain factors
# beh_antIns_full_1_fit = glmer(accept ~ offer * age_bi + block_fair + 
#                             anteriorinsula_corrected * offer * age_bi -
#                               anteriorinsula_corrected:offer:age_bi +
#                               anteriorinsula_corrected * block_fair +
#                             (1|participant_id),
#                           data = all_trials_df,
#                           family = binomial)
# summary(beh_antIns_full_1_fit)

###### to delete ###### 
# temp_m = glmer(anteriorinsula_corrected ~ offer * age_bi * block_fair * group_tri +
#                             (1|participant_id),
#                           data = all_trials_df,
#                           family = binomial)
###### ###### ###### ###### 

beh_antIns_full_2_fit = glmer(accept ~ offer * age_bi + block_fair +
                            anteriorinsula_corrected * age_bi -
                            (1|participant_id),
                          data = all_trials_df,
                          family = binomial)
# summary(beh_antIns_full_2_fit)

anova_predictor_test = data.frame(Anova(beh_antIns_full_2_fit))
anova_model_test = data.frame(anova(beh_full_fit, beh_antIns_full_2_fit, refit = TRUE))

N_nonNA_results = sum(!is.na(brain_behavior_df$brain))
brain_name = "anteriorinsula_corrected"

predictor_name = paste("age_bi", brain_name, sep = ":")
brain_behavior_df$brain[N_nonNA_results+1] = brain_name
brain_behavior_df$predictor[N_nonNA_results+1] = predictor_name

brain_behavior_df$pre_p[N_nonNA_results+1] = 
  anova_predictor_test$Pr..Chisq.[row.names(anova_predictor_test) == predictor_name]

brain_behavior_df$model_p[N_nonNA_results+1] = 
  anova_model_test$Pr..Chisq.[2]
```
# hierarchical 1, brain x age, brain x offer
```{r}
## converged, anteriorinsula_corrected:age_biolder sig, anova sig
beh_antIns_full_0_fit = glmer(accept ~ 
                            anteriorinsula_corrected * offer * age_bi -
                              anteriorinsula_corrected:offer:age_bi +
                              # anteriorinsula_corrected * block_fair + # not sig, commented out
                              block_fair +
                            (1|participant_id),
                          data = all_trials_df,
                          family = binomial)
summary(beh_antIns_full_0_fit)
anova(beh_full_fit, beh_antIns_full_0_fit)

## converged, VS_corrected:offer sig, anova sig
beh_VS_full_0_fit = glmer(accept ~ 
                                VS_corrected * offer * age_bi -
                                VS_corrected:offer:age_bi +
                                # VS_corrected * block_fair + # not sig, commented out
                                block_fair +
                                (1|participant_id),
                              data = all_trials_df,
                              family = binomial)
summary(beh_VS_full_0_fit)
anova(beh_full_fit, beh_VS_full_0_fit)

## converged, no sig interaction, anova sig though
beh_dacc_full_0_fit = glmer(accept ~ 
                                dacc_corrected * offer * age_bi -
                                dacc_corrected:offer:age_bi +
                                # dacc_corrected * block_fair + # not sig, commented out
                              block_fair +
                                (1|participant_id),
                              data = all_trials_df,
                              family = binomial)
summary(beh_dacc_full_0_fit)
anova(beh_full_fit, beh_VS_full_0_fit)


## converged, not sig ingeraction, anove not sig
beh_vmpfc_full_0_fit = glmer(accept ~ 
                                vmpfc_corrected * offer * age_bi -
                                vmpfc_corrected:offer:age_bi +
                                # vmpfc_corrected * block_fair + # won't converge, conmment out
                               block_fair +
                                (1|participant_id),
                              data = all_trials_df,
                              family = binomial)
summary(beh_vmpfc_full_0_fit)
anova(beh_full_fit, beh_vmpfc_full_0_fit)
```

# hierarchical 2, brain * age only
```{r}
## converged, anteriorinsula_corrected:age_biolder sig, anova sig
beh_antIns_h2_fit = glmer(accept ~ 
                            offer * age_bi +
                              anteriorinsula_corrected * age_bi +
                              # anteriorinsula_corrected * block_fair + # not sig, commented out
                              block_fair +
                            (1|participant_id),
                          data = all_trials_df,
                          family = binomial)
summary(beh_antIns_h2_fit)
anova(beh_full_fit, beh_antIns_h2_fit)

## converged, interaction no sig, anova sig
beh_VS_full_h2_fit = glmer(accept ~ 
                                offer * age_bi +
                              VS_corrected * age_bi +
                                # VS_corrected * block_fair + # not sig, commented out
                                block_fair +
                                (1|participant_id),
                              data = all_trials_df,
                              family = binomial)
summary(beh_VS_full_h2_fit)
anova(beh_full_fit, beh_VS_full_h2_fit)

## converged, no sig interaction, anova sig though
beh_dacc_full_0_fit = glmer(accept ~ 
                                dacc_corrected * offer * age_bi -
                                dacc_corrected:offer:age_bi +
                                # dacc_corrected * block_fair + # not sig, commented out
                              block_fair +
                                (1|participant_id),
                              data = all_trials_df,
                              family = binomial)
summary(beh_dacc_full_0_fit)
anova(beh_full_fit, beh_VS_full_0_fit)


## converged, not sig ingeraction, anove not sig
beh_vmpfc_full_0_fit = glmer(accept ~ 
                                vmpfc_corrected * offer * age_bi -
                                vmpfc_corrected:offer:age_bi +
                                # vmpfc_corrected * block_fair + # won't converge, conmment out
                               block_fair +
                                (1|participant_id),
                              data = all_trials_df,
                              family = binomial)
summary(beh_vmpfc_full_0_fit)
anova(beh_full_fit, beh_vmpfc_full_0_fit)
```

### main brain only model
```{r}
beh_VS_full_fit = glmer(accept ~ offer * age_bi + block_fair + group_tri + 
                       VS_corrected + 
                                       (1|participant_id),
                                     data = all_trials_df,
                                     family = binomial)

# summary(beh_VS_full_fit)

beh_vmpfc_full_fit = glmer(accept ~ offer * age_bi + block_fair + group_tri + 
                       vmpfc_corrected + 
                                       (1|participant_id),
                                     data = all_trials_df,
                                     family = binomial)

beh_antIns_full_fit = glmer(accept ~ offer * age_bi + block_fair + group_tri + 
                       anteriorinsula_corrected + 
                         (1|participant_id),
                                     data = all_trials_df,
                                     family = binomial)

beh_dacc_full_fit = glmer(accept ~ offer * age_bi + block_fair + group_tri + 
                       dacc_corrected + 
                         (1|participant_id),
                                     data = all_trials_df,
                                     family = binomial)

anova(beh_full_fit, beh_VS_full_fit, refit = TRUE)
anova(beh_full_fit, beh_vmpfc_full_fit, refit = TRUE)
anova(beh_full_fit, beh_antIns_full_fit, refit = TRUE)
anova(beh_full_fit, beh_dacc_full_fit, refit = TRUE)
```






## P2 NH1B
"NH1B) The ins and dACC will be activated during the rejection of offers."
[insula, dACC][reject] (?)


## P2 NH1C
"NH1C) The vmPFC and VS will be activated during the acceptance of offers."
[vmPFC, VS][accept] (?) 


## P2 NH2A
"NH2A) All effects specified in NH1 will be blunted in older adults."
ROI mean ~ age



## P2 NH2B
"NH2B) The effect specified in NHB1 will be enhanced when rejecting unfair offers from human versus computer partners."
[insula, dACC][reject, human > computer]


# P2 NH single trial exploratory
### anterior insula, exploratory
```{r, eval = F}
# ## won't converge
# # model_P2_NH1_antIns_fit <- glmer(accept ~ anteriorinsula_corrected * age_bi * group_tri * block_fair +
# #                      (1|participant_id),
# #                             data = all_trials_df,
# #                             family = binomial)
# 
# ## converged, NO SIG three-way interaction
# model_P2_NH1_antIns_fit <- glmer(accept ~ anteriorinsula_corrected * age_bi * group_tri * block_fair -
#                             anteriorinsula_corrected:age_bi:group_tri:block_fair +
#                             (1|participant_id),
#                             data = all_trials_df,
#                             family = binomial)
# summary(model_P2_NH1_antIns_fit)
# 
# ## converged, SIG ant insula * group interaction
# model_P2_NH1_antIns_fit <- glmer(accept ~ anteriorinsula_corrected * age_bi * group_tri * block_fair -
#                             anteriorinsula_corrected:age_bi:group_tri:block_fair -
#                               anteriorinsula_corrected:age_bi:group_tri -
#                               anteriorinsula_corrected:age_bi:block_fair -
#                               anteriorinsula_corrected:group_tri:block_fair -
#                               age_bi:group_tri:block_fair +
#                               (1|participant_id),
#                             data = all_trials_df,
#                             family = binomial)
# summary(model_P2_NH1_antIns_fit)
# 
# ## won't converge
# # model_P2_NH1_fit <- glmer(accept ~ anteriorinsula_corrected * age_bi * group_tri +
# #                      (1|participant_id),
# #                             data = all_trials_df,
# #                             family = binomial)
# 
# ## converged, SIG insula*group interaction
# model_P2_NH1_antIns_fit <- glmer(accept ~ anteriorinsula_corrected * age_bi * group_tri -
#                             anteriorinsula_corrected:age_bi:group_tri + 
#                               anteriorinsula_corrected * age_bi * block_fair +
#                      (1|participant_id),
#                             data = all_trials_df,
#                             family = binomial)
# summary(model_P2_NH1_antIns_fit)
```


