---
title: "behavior_hypotheses_tests_srndnaUGR"
author: "Jen Yang"
date: "2024-11-11, last modified 2024-11-11"
output: 
  html_document:
    code_folding: hide
    toc: true
    toc_float:
      collapsed: false
      smooth_scroll: false
    hightlight: zenburn
    toc_depth: 6
---

```{r clean, include=FALSE}
# clean environment
rm(list = ls())
```

# Load libraries
```{r libraries, message_bi=FALSE, warning=TRUE, include=FALSE}
library(car)
library(plyr)
library(foreign)
library(pscl)
library(boot)
library(MASS)
library(robust)
library(sfsmisc)
library(ggplot2)
library(reshape2)
library(ppcor)
library(ggrepel)
library(Hmisc)
library(tidyverse)
library(sandwich)
library(ggpubr)
library(interactions)
library(knitr)
library(twowaytests)
library(ggfortify)
library(interactions)
library(broom)
library(patchwork)
library(robustbase)
library(lmtest)
library(modelr)
library(Rmisc)
# library(raincloudplots)
library(cowplot)
library(readr)
library(PupillometryR)
library(ggpp)
library(estimatr)
library(skedastic)
library(ggpubr)
library(lubridate)
library(readxl)
library(gridExtra)
library(scales)
library(rstudioapi)
library(jsonlite)
library(rjson)
library(readr)
library(hBayesDM)
library(brms)
library(emmeans)
library(mediation)
library(here)
library(lme4)
library(broom.mixed)
library(easyRT)
library(parameters)
library(effectsize)
library(effects)
library(lmerTest)
library(ez)
library(afex)
library(oro.nifti)
library(neurobase)

```

# load tsv and prolific raw data
```{r}
gitrepo_path = "/Users/momocco/Documents/GitHub/srndna-ug/behavioral_analyses"

data_dir = paste(gitrepo_path,"data", sep = "/")
codes_dir = paste(gitrepo_path, "codes", sep = "/")
fit_dir = paste(gitrepo_path,"fits", sep = "/")
figure_dir = paste(gitrepo_path,"figures", sep = "/")

image_dir = "/Users/momocco/Documents/SRNDNA_UG_SingleTrial/derivatives/single_trials"

singletrial_name = "task-ultimatum_run-01_singletrial-Act.nii.gz"
```

# load subject list
```{r}
sublist_name = "participant_L3_47.csv"
sublist_df = read.csv(paste(data_dir, sublist_name, sep = "/"), header = TRUE) %>% 
  select(subjID)
```

# load behavioral data
```{r}
trials_name = "all_trials.csv"
trials_all_df = read.csv(paste(data_dir, trials_name, sep = "/"), header = TRUE)
```


# load image
```{r}
# Load the NIFTI file
subID = sublist_df$subjID[1]
N_trials_subID = sum(trials_all_df$subjID == subID & trials_all_df$run == 1)
print(N_trials_subID)

image_name = paste(subID, singletrial_name, sep = "_")
image <- readNIfTI(paste(image_dir, subID, image_name, sep = "/"), reorient = FALSE)
image_dims <- dim(image)
print(image_dims)
```



# load and prepare data
```{r}
# load subs
all_trials_df = read.csv(paste(data_dir, "all_trials.csv", sep = "/"), header = TRUE)
colnames(all_trials_df)[colnames(all_trials_df) == "subjID"] <- "participant_id"
indiv_df = read.csv(paste(data_dir, "participant_check.csv", sep = "/"), header = TRUE)  %>%
  mutate(age_bi = case_when(age <= 36 ~ "younger",
                            age > 36 ~ "older"))

all_trials_df = merge(all_trials_df, indiv_df, by.x = "participant_id", by.y = "participant_id")

## add a categorical variable that differentiate three groups
all_trials_df = all_trials_df %>% 
  mutate(group_tri = as.factor(case_when(human == 0 ~ 0, # computer
                               human == 1 & ingroup == 0 ~ 1, # outgroup
                               human == 1 & ingroup == 1 ~ 2))) # ingroup
all_trials_df$group_tri = relevel(all_trials_df$group_tri, ref = "0")
all_trials_df$age_bi = relevel(as.factor(all_trials_df$age_bi), ref = "younger")

all_trials_df = all_trials_df %>% 
  mutate(age_bi_dummy = case_when(age_bi == "younger" ~ 0,
                                  age_bi == "older" ~ 1)
         )
```

# prereg 1 analyses
## P1 H1.1
H1.1: All participants will reject more unfair offers from human partners as compared to computer partners; this effect will be stronger in younger adults.

Result: only offer/fairness is related to acceptance
```{r}
## full model, won't converge
# model_fit <- glmer(accept ~ offer * human * age_bi + sex +
#                      (1 + offer * human | participant_id),
#                             data = all_trials_df,
#                             family = binomial)
# 

## won't converge
# model_fit <- glmer(accept ~ offer * human * age_bi + sex +
#                      (1 + offer * human || participant_id),
#                             data = all_trials_df,
#                             family = binomial)

## won't converge
# model_fit <- glmer(accept ~ offer * human + age_bi + sex +
#                      (1 + offer * human || participant_id),
#                             data = all_trials_df,
#                             family = binomial)

## won't converge
# model_fit <- glmer(accept ~ offer * human + age_bi + sex +
#                      (1 + offer + human || participant_id),
#                             data = all_trials_df,
#                             family = binomial)

## won't converge
# model_fit <- glmer(accept ~ offer * human * age_bi + sex +
#                      (1 + offer + human || participant_id),
#                             data = all_trials_df,
#                             family = binomial)

## won't converge
# model_fit <- glmer(accept ~ offer * human * age_bi + sex + 
#                      (1 + offer || participant_id),
#                             data = all_trials_df,
#                            family = binomial)

## won't converge
# model_fit <- glmer(accept ~ offer * human * age_bi + sex + 
#                      (1 + human || participant_id),
#                             data = all_trials_df,
#                             family = binomial)

## won't converge
# model1.1_fit <- glmer(accept ~ offer * human * age_bi + sex +
#                      (1 | participant_id),
#                             data = all_trials_df,
#                             family = binomial)
# summary(model1.1_fit)

## won't converge
# model1.1_2_fit <- glmer(accept ~ offer * human * age_bi_dummy + sex - offer : human : age_bi_dummy +
#                      (1 + age_bi_dummy | participant_id),
#                             data = all_trials_df,
#                             family = binomial)

## converged, SIG offer:age_bi effect, NO no offer * human effect or age * human
model1.1_2_fit <- glmer(accept ~ offer * human * age_bi + sex - offer : human : age_bi +
                     (1 | participant_id),
                            data = all_trials_df,
                            family = binomial)
summary(model1.1_2_fit)
```

## P1 H1.2
H1.2: Within social conditions, younger adults will show increased rates of acceptance when interacting with younger vs. older partners; older adults’ rates of acceptance will not differ between partners.

```{r}
## full model, won't converge
# model1.2_fit <- glmer(accept ~ offer * ingroup * age_bi +
#                      (1 + offer * ingroup | participant_id),
#                             data = all_trials_df,
#                             family = binomial)

## won't converge
# model_fit <- glmer(accept ~ offer * ingroup * age_bi + sex +
#                      (1 + offer * ingroup || participant_id),
#                             data = all_trials_df,
#                             family = binomial)

## won't converge
# model1.2_fit <- glmer(accept ~ offer * ingroup * age_bi +
#                      (1 + offer + ingroup || participant_id),
#                             data = all_trials_df,
#                             family = binomial)

## won't converge
# model_fit <- glmer(accept ~ offer * ingroup + age_bi + sex +
#                      (1 + offer + ingroup || participant_id),
#                             data = all_trials_df,
#                             family = binomial)

## won't converge
# model_fit <- glmer(accept ~ offer * ingroup * age_bi + sex +
#                      (1 + offer || participant_id),
#                             data = all_trials_df,
#                            family = binomial)

## won't converge
# model_fit <- glmer(accept ~ offer * ingroup * age_bi + sex +
#                      (1 + ingroup || participant_id),
#                             data = all_trials_df,
#                             family = binomial)

## converged, no sig offer * ingroup * age_bi
model1.2_fit <- glmer(accept ~ offer * ingroup * age_bi +
                     (1 | participant_id),
                            data = all_trials_df,
                            family = binomial)
summary(model1.2_fit)

## converged, SIG offer:age_biyounger
model1.2_1_fit <- glmer(accept ~ offer * ingroup * age_bi - offer : ingroup : age_bi +
                     (1 | participant_id),
                            data = all_trials_df,
                            family = binomial)
summary(model1.2_1_fit)

model1.2_2_fit <- glmer(accept ~ offer * age_bi + ingroup * age_bi +
                     (1 | participant_id),
                            data = all_trials_df,
                            family = binomial)
summary(model1.2_2_fit)
```
## P1 additional H1.3
suspected group effect of computer vs ingroup vs outgroup based on H1.1 and H1.2 results
H1.2 has sig offer*age interaction but H1.1 doesn't
```{r}
## won't converge 
# model1.3_fit <- glmer(accept ~ offer * group_tri * age_bi +
#                      (1 + offer + group_tri || participant_id),
#                             data = all_trials_df,
#                             family = binomial)

## converged, no sig offer * group_tri * age_bi
model1.3_fit <- glmer(accept ~ offer * group_tri * age_bi + sex +
                     (1 | participant_id),
                            data = all_trials_df,
                            family = binomial)
summary(model1.3_fit)

## converged, SIG offer:age_biolder
model1.3_1_fit <- glmer(accept ~ offer * group_tri + sex +
                          offer * age_bi +
                          age_bi * group_tri +
                     (1 | participant_id),
                            data = all_trials_df,
                            family = binomial)

summary(model1.3_1_fit)

## converged, SIG offer:age_biolder
model1.3_1_fit <- glmer(accept ~  offer * age_bi + sex +
                     (1 | participant_id),
                            data = all_trials_df,
                            family = binomial)

summary(model1.3_1_fit)

## won't converge
# model1.3_1_fit <- glmer(accept ~ offer * group_tri + 
#                           offer * age_bi + 
#                           age_bi * group_tri +
#                      (1 + offer + group_tri| participant_id),
#                             data = all_trials_df,
#                             family = binomial)

## won't converge
# model1.3_1_fit <- glmer(accept ~ offer * group_tri + 
#                           offer * age_bi + 
#                      (1 + offer + group_tri| participant_id),
#                             data = all_trials_df,
#                             family = binomial)

## converged, SIG offer * age
model1.3_1_fit <- glmer(accept ~ offer * group_tri +
                          offer * age_bi +
                     (1 | participant_id),
                            data = all_trials_df,
                            family = binomial)
summary(model1.3_1_fit)

## won't converge
model1.3_2_fit <- glmer(accept ~ offer + group_tri + age_bi +
                     (1 + age_bi|participant_id),
                            data = all_trials_df,
                            family = binomial)
summary(model1.3_2_fit)
```

# prereg 2 analyses
## P2 BH3



# alpha ~ age_bi * human/computer, not sig
```{r}
all_trials_df = indiv_df %>% 
  select(participant_id, age_bi, computer_alpha, human_alpha) %>% 
  melt(., id.vars = c("participant_id","age_bi"), variable.name = "alpha_group") %>% 
  mutate(alpha = as.factor(alpha_group))

model_fit <- lmer(value ~ alpha * age_bi + (1 | participant_id),
                      data = all_trials_df)
summary(model_fit)
```

# alpha ~ age_bi * ingroup/outgroup, not sig
```{r}
all_trials_df = indiv_df %>% 
  select(participant_id, age_bi, ingroup_alpha, outgroup_alpha) %>% 
  melt(., id.vars = c("participant_id","age_bi"), variable.name = "alpha_group") %>% 
  mutate(alpha = as.factor(alpha_group))

model_fit <- lmer(value ~ alpha_group * age_bi + (1 | participant_id),
                      data = all_trials_df)
summary(model_fit)
```

# epsilon ~ age_bi * human/computer, not sig
```{r}
all_trials_df = indiv_df %>% 
  select(participant_id, age_bi, age_bi, computer_epsilon, human_epsilon) %>% 
  melt(., id.vars = c("participant_id","age_bi"), variable.name = "epsilon_group") %>% 
  mutate(epsilon = as.factor(epsilon_group)) %>% 
  within(epsilon_group <- relevel(epsilon_group, ref = "computer_epsilon"))

model_fit <- lmer(value ~ epsilon * age_bi + (1 | participant_id),
                  data = all_trials_df)
summary(model_fit)

model_fit <- lmer(value ~ epsilon * age_bi + (1 | participant_id),
                  data = all_trials_df)
summary(model_fit)

model_1_fit <- lmer(value ~ epsilon + age_bi + (1 | participant_id),
                  data = all_trials_df)
summary(model_1_fit)
```

# epsilon ~ age_bi * ingroup/outgroup, group main sig
```{r}
all_trials_df = indiv_df %>% 
  select(participant_id, age_bi, age_bi, ingroup_epsilon, outgroup_epsilon) %>% 
  melt(., id.vars = c("participant_id", "age_bi"), variable.name = "epsilon_group") %>% 
  mutate(epsilon = as.factor(epsilon_group)) %>% 
  within(epsilon_group <- relevel(epsilon_group, ref = "outgroup_epsilon"))

model_fit <- lmer(value ~ epsilon_group * age_bi + (1 | participant_id),
                  data = all_trials_df)
summary(model_fit)

model_1_fit <- lmer(value ~ epsilon_group + age_bi + (1 | participant_id),
                  data = all_trials_df)
summary(model_1_fit)
```