---
title: "SRNDNA figures"
author: "Jen Yang"
date: "2025-06-09, last modified 2025-06-09"
output: 
  html_document:
    code_folding: hide
    toc: true
    toc_float:
      collapsed: false
      smooth_scroll: false
    hightlight: zenburn
    toc_depth: 6
---

```{r clean, include=FALSE}
# clean environment
rm(list = ls())
```

# Load libraries
```{r libraries, message=FALSE, warning=TRUE, include=FALSE}
library(car)
library(plyr)
library(foreign)
library(pscl)
library(boot)
library(MASS)
library(robust)
library(sfsmisc)
library(ggplot2)
library(reshape2)
library(ppcor)
library(ggrepel)
library(Hmisc)
library(tidyverse)
library(sandwich)
library(ggpubr)
library(interactions)
library(knitr)
library(twowaytests)
library(ggfortify)
library(interactions)
library(broom)
library(patchwork)
library(robustbase)
library(lmtest)
library(modelr)
library(Rmisc)
# library(raincloudplots)
library(cowplot)
library(readr)
library(PupillometryR)
library(ggpp)
library(estimatr)
library(skedastic)
library(ggpubr)
library(lubridate)
library(readxl)
library(gridExtra)
library(scales)
library(rstudioapi)
library(jsonlite)
library(rjson)
library(readr)
library(hBayesDM)
library(brms)
library(emmeans)
library(mediation)
library(here)
library(lme4)
library(broom.mixed)
library(easyRT)
library(parameters)
library(effectsize)
library(effects)
library(lmerTest)
library(ez)
library(LMMstar)
```

# set directories
```{r}
gitrepo_path = "/Users/momocco/Documents/GitHub/srndna-ug/behavioral_analyses"

data_dir = paste(gitrepo_path,"data", sep = "/")
codes_dir = paste(gitrepo_path, "codes", sep = "/")
fit_dir = paste(gitrepo_path,"fits", sep = "/")
figure_dir = paste(gitrepo_path,"figures", sep = "/")

ROImean_dir = "/Users/momocco/Documents/GitHub/srndna-ug/imaging_plots_SANS"
```

# plot param setup
```{r}
axis_title = 16
axis_ticks = 10
axis_text = 12
axis_label = 14

legend_all = 12

annotate_text = 4
axis_line_width = 1
fit_line_width = 2

data_point_alpha = 0.5
data_point_size = 3*0.8

mean_point_size = 3

line_width = 1
point_size = 3

summary_point_alpha = 1
summary_point_size = 3

annotate_text = 4

w = 5
h = 4
```

# fmri whole brain
## load and code data
```{r}
list_fmri_df = read.csv(paste(data_dir, "participant_L3_47.csv", sep = "/"),
                          header = T) %>% dplyr::select(subjID)

participant_check_df = read.csv(paste(data_dir, "participant_check.csv", sep = "/"), header = T)

participant_demo_df = 
  merge(list_fmri_df, participant_check_df, by.x = "subjID", by.y = "participant_id", all.x = T) %>% 
  mutate(age_bi = case_when(age <= 36 ~ "younger", age > 36 ~ "older"),
         age_bi = relevel(as.factor(age_bi), ref = "younger"))

## load tsnr, fd_mean, and RT
sub_control_df = read.csv(paste(data_dir, "participant_L3_47.csv", sep = "/"),
                          header = T) %>% 
  select(subjID, tsnr, fd_mean, RT)

control_vars = colnames(sub_control_df)[-1]
```

## dmn, cope7, in-out c3 y-o, paracingulate gyrus?, -13.3, 34, 27.8 (aCC?, COG -3.6 33.4 32.9)
### prep df for ggplot
```{r}
## data prep
in_name = "dmn_p_in-out_y-o_type-nppi-dmn_cope-04.txt"
out_name = "dmn_p_in-out_y-o_type-nppi-dmn_cope-06.txt"

in_ROI = read.table(paste(ROImean_dir, in_name, sep = '/'),sep=" ",header=F)
out_ROI = read.table(paste(ROImean_dir, out_name, sep = '/'),sep=" ",header=F)

in_df = cbind(list_fmri_df, age_bi = participant_demo_df$age_bi, 
              in_ROI = in_ROI$V1, # for packed interaction, y axis = contrasted brain activity
              ROI = in_ROI$V1, # for unpacked interaction, y axis = no-contrast brain activity
              group = as.factor("ingroup")) # for unpacked interaction, y axis = no-contrast brain activity

in_df = merge(in_df, sub_control_df, by = "subjID")

out_df = cbind(list_fmri_df, age_bi = participant_demo_df$age_bi, 
               out_ROI = out_ROI$V1, # for packed interaction, y axis = contrasted brain activity
               ROI = out_ROI$V1, # for unpacked interaction, y axis = no-contrast brain activity
               group = as.factor("outgroup")) # for unpacked interaction, y axis = no-contrast brain activity
out_df = merge(out_df, sub_control_df, by = "subjID")

plot_df = in_df %>% 
  mutate(out_ROI = out_df$out_ROI,
         DV = in_ROI - out_ROI) %>% 
  select("subjID", "DV", "age_bi", control_vars)
```

### get partial DV
```{r}
m_DV_res = lm(DV ~ tsnr + fd_mean + RT, plot_df)
plot_df %<>% mutate(DV_res = residuals(m_DV_res)) 
```

### prepare partial residual summary for reg line and error bar
```{r}
summary_plot_df <- plot_df %>%
  group_by(age_bi) %>%
  summarise(mean_DV_res = mean(DV_res, na.rm = TRUE),
    se_DV_res = sd(DV_res, na.rm = TRUE) / sqrt(n()))
```

### ggplot and save
```{r}
set.seed(1234)

x_label = ""
y_label = "DMN-dACC, similar > disimilar (β)\noffer size modulated"
title_label = ""

color_label = "Age Group"
color_age = c("older" = "#006900", "younger"= "#00d000") # "#37ff37"

figure_name = "DMN_dACC_in-out_age_NoBehCov"

p_scatter =
  ggplot() +
  geom_jitter(data = plot_df, aes(x = age_bi, y = DV_res, color = age_bi),
              alpha = data_point_alpha, 
              width = 0.1, size = data_point_size) + # Adjust jitter width for categorical X
  geom_point(data = summary_plot_df, aes(x = age_bi, y = mean_DV_res), 
             size = mean_point_size, alpha = data_point_alpha, shape = 18) +
  geom_errorbar(data = summary_plot_df, 
                aes(x = age_bi, 
                    ymin = mean_DV_res - se_DV_res, ymax = mean_DV_res + se_DV_res),
                width = 0.1) +
  scale_color_manual(values = color_age) +
  labs(x = x_label, y = y_label, color = color_label, title = title_label) +
  # labs(x = x_label, y = y_label, color = color_label, title = NULL) +
  geom_line(data = summary_plot_df, # Connect means with a line
            aes(x = as.numeric(age_bi), y = mean_DV_res), 
            color = "black", linewidth = fit_line_width) +
  # theme_classic() +
  theme(axis.line = element_line(linewidth = 1, colour = "black", linetype=1),
        legend.title = element_text(face = "bold"),
        axis.text.x = element_text(size = axis_text), 
        axis.text.y = element_text(size = axis_text), 
        axis.title.x = element_text(size = axis_title, face="bold"), 
        axis.title.y = element_text(size = axis_title, face="bold")) 

p_scatter

ggsave(paste(figure_dir, paste(figure_name, "scatter_manu.png", sep = "_"),
             sep = "/"), p_scatter, width = w*1.1, height = h)
```

## ecn, in-out, sensitivity_logit * age, frontal pole/mpfc?
### prepare df for ggplot
```{r}
## data prep
in_name = "ecn_p_in-out_o-y_sens-logit_type-nppi-ecn_cope-04.txt"
out_name = "ecn_p_in-out_o-y_sens-logit_type-nppi-ecn_cope-06.txt"

in_ROI = read.table(paste(ROImean_dir, in_name, sep = '/'), sep=" ",header=F)
out_ROI = read.table(paste(ROImean_dir, out_name, sep = '/'), sep=" ",header=F)

sensitivity_name = "in_out_sensitivity_logit.csv"
sensitivity_name = "in_out_sensitivity_full_logit.csv"
sensitivity_df = read.csv(paste(data_dir, sensitivity_name, sep = '/'), header = T)

in_df = cbind(list_fmri_df, age_bi = participant_demo_df$age_bi, 
              in_ROI = in_ROI$V1, # for packed interaction, y axis = contrasted brain activity
              ROI = in_ROI$V1, # for unpacked interaction, y axis = no-contrast brain activity
              group = as.factor("ingroup")) # for unpacked interaction, y axis = no-contrast brain activity

in_df = merge(in_df, sub_control_df, by = "subjID")

out_df = cbind(list_fmri_df, age_bi = participant_demo_df$age_bi, 
               out_ROI = out_ROI$V1, # for packed interaction, y axis = contrasted brain activity
               ROI = out_ROI$V1, # for unpacked interaction, y axis = no-contrast brain activity
               group = as.factor("outgroup")) # for unpacked interaction, y axis = no-contrast brain activity

out_df = merge(out_df, sub_control_df, by = "subjID")

plot_df = in_df %>% 
  mutate(out_ROI = out_df$out_ROI,
         DV = in_ROI - out_ROI,
         sensitivity_in_out = sensitivity_df$in_out_full_logit) %>% 
  select("subjID", "DV", "age_bi", "sensitivity_in_out", control_vars)
```

### get partial DV
```{r}
m_DV_res = lm(DV ~ tsnr + fd_mean + RT, plot_df)
plot_df %<>% mutate(DV_res = residuals(m_DV_res)) 
```

### plot and save
```{r}
set.seed(1234)

x_label = "Norm Violation Senstivity\nsimilar > disimilar"
y_label = "ECN-mPFC, similar > disimilar (β)\noffer size modulated"
title_label = ""

color_label = "Age Group"
color_age = c("older" = "#003c66", "younger"= "#0098ff")

# figure_name = "ECN_mPFC_in-out_age_BehFairSensitivity"
figure_name = "ECN_mPFC_in-out_age_BehFairSensitivityFull"

p_scatter =
  ggplot(plot_df, aes(x = sensitivity_in_out, y = DV_res, color = age_bi)) +
  geom_point(alpha = data_point_alpha, size = data_point_size, show.legend = FALSE) +
  geom_smooth(formula = "y~x", method = "lm", 
              se = TRUE,
              linetype = "solid",
              linewidth = 2, 
              alpha = 0.2) +
  scale_color_manual(values = color_age) +
  guides(color = guide_legend(override.aes = list(fill = NA))) +
  # theme_classic() +
  labs(x = x_label, y = y_label, color = color_label, title = title_label) +
  # labs(x = x_label, y = y_label, color = color_label, title = NULL) +
  guides(color = guide_legend(override.aes = list(fill = NA))) +
  theme(axis.line = element_line(linewidth = 1, colour = "black", linetype=1),
        legend.title = element_text(face = "bold"),
        axis.text.x = element_text(size = axis_text), 
        axis.text.y = element_text(size = axis_text), 
        axis.title.x = element_text(size = axis_title, face="bold"), 
        axis.title.y = element_text(size = axis_title, face="bold"))
        # legend.position="bottom left", legend.box = "horizontal")
        # legend.position="none")

p_scatter

ggsave(paste(figure_dir, paste(figure_name, "scatter_manu.png", sep = "_"),
             sep = "/"), p_scatter, width = w*1.1, height = h)
```

# single trial

## load data
```{r}
# load subs
all_trials_df = read.csv(paste(data_dir, "all_trials_brains.csv", sep = "/"), header = TRUE) %>% 
  .[.$missed == 0,]

colnames(all_trials_df)[colnames(all_trials_df) == "subjID"] <- "participant_id"
indiv_df = read.csv(paste(data_dir, "participant_check.csv", sep = "/"), header = TRUE)  %>%
  mutate(age_bi = case_when(age <= 36 ~ "younger",
                            age > 36 ~ "older"))

all_trials_df = merge(all_trials_df, indiv_df, by.x = "participant_id", by.y = "participant_id")

sublist_final = read.csv(paste(data_dir, "participant_L3_47.csv", sep = "/"), header = TRUE)

all_trials_df = all_trials_df[all_trials_df$participant_id %in% sublist_final$subjID,]
```

## recode group and age
```{r}
## add a categorical variable that differentiate three groups
all_trials_df = all_trials_df %>% 
  mutate(group_tri = as.factor(case_when(human == 0 ~ 0, # computer
                               human == 1 & ingroup == 0 ~ 1, # outgroup
                               human == 1 & ingroup == 1 ~ 2))) # ingroup
# all_trials_df$group_tri = relevel(all_trials_df$group_tri, ref = "0") # computer

all_trials_df = all_trials_df %>% mutate(human = as.factor(human))

all_trials_df$group_tri = relevel(all_trials_df$group_tri, ref = "1") # outgroup

all_trials_df$age_bi = relevel(as.factor(all_trials_df$age_bi), ref = "younger")

all_trials_df = all_trials_df %>% 
  mutate(age_bi_dummy = case_when(age_bi == "younger" ~ 0,
                                  age_bi == "older" ~ 1)
         )
```

## factorize vars as needed
```{r}
factor_col_names = c("participant_id", "run", "missed", "accept",
                     "ingroup", "block_fair", "sex")
all_trials_df[factor_col_names] %<>% lapply(., factor) 
```

## add fdmean, tsnr vars to data
```{r}
fmri_control_data = 
  read.csv(paste(data_dir, "Task-ultimatum_Level-Run_Outlier-info.csv", 
                 sep = "/"), header = TRUE) %>% 
  filter(Sub %in% sublist_final$subjID == 1) %>% 
  # mutate(subjID = Sub) %>% 
  select(-task, -outlier_run_Custom1)

all_trials_df = merge(all_trials_df, fmri_control_data, 
                      by.x = c("participant_id", "run"),
                      by.y = c("Sub", "run"))
```

## remove incomplete rows
```{r}
all_trials_df %<>% na.omit 
```

## anterior singula
### prepare df for ggplot
```{r}
# P2_NH1_AI_human_m1 =
#   glmer(accept ~ anteriorinsula_corrected * human + offer +
#          tsnr + fd_mean + response_time +
#          (1 | participant_id),
#        data = all_trials_df,
#        family = binomial)
# summary(P2_NH1_AI_human_m1)

plot_df = all_trials_df %>%
  select(participant_id, accept, anteriorinsula_corrected, human, 
         age_bi, offer, tsnr, fd_mean, response_time)
```

### choice ~ anterior insula * age + controls, SIG, small
#### get partial DV
```{r}
m_DV_res = glmer(accept ~ offer * age_bi +
         tsnr + fd_mean + response_time +
         (1 | participant_id),
       data = plot_df,
       family = binomial)
plot_df %<>% mutate(DV_res = residuals(m_DV_res))
```

#### plot and save
```{r}
x_label = "single-trial anterior insula activation"
y_label = "Accept (logit)"
title_label = ""


color_label = "Age Group"
color_age = c("older" = "#006900", "younger"= "#00d000") # "#37ff37"

# figure_name = "ECN_mPFC_in-out_age_BehFairSensitivity"
figure_name = "ant_insula_age_SingleTrial"

p_scatter =
  ggplot(plot_df, 
         aes(x = anteriorinsula_corrected,
             y = DV_res,
             color = age_bi)) +
  # geom_point(alpha = data_point_alpha, size = data_point_size, show.legend = FALSE) +
  geom_smooth(formula = "y~x", method = "lm", 
              se = TRUE,
              linetype = "solid",
              linewidth = 2, 
              alpha = 0.2) +
  scale_color_manual(values = color_age) +
  # guides(color = guide_legend(override.aes = list(fill = NA))) +
  # theme_classic() +
  labs(x = x_label, y = y_label, color = color_label, title = title_label) +
  # guides(color = guide_legend(override.aes = list(fill = NA))) +
  theme(axis.line = element_line(linewidth = 1, colour = "black", linetype=1),
        legend.title = element_text(face = "bold"),
        axis.text.x = element_text(size = axis_text), 
        axis.text.y = element_text(size = axis_text), 
        axis.title.x = element_text(size = axis_title, face="bold"), 
        axis.title.y = element_text(size = axis_title, face="bold"))
        # legend.position="bottom left", legend.box = "horizontal")
        # legend.position="none")

p_scatter

ggsave(paste(figure_dir,
             paste(figure_name, "scatter_manu.png", sep = "_"),
             sep = "/"),
       p_scatter, width = w*1.1, height = h)
```

### choice ~ anterior insula * human + controls, SIG
#### get partial DV
```{r}
m_DV_res = glmer(accept ~ offer * age_bi +
         tsnr + fd_mean + response_time +
         (1 | participant_id),
       data = plot_df,
       family = binomial)
plot_df %<>% mutate(DV_res = residuals(m_DV_res))
```

#### plot and save
```{r}
x_label = "single-trial anterior insula activation"
y_label = "Accept (logit)"
title_label = ""


color_label = "Partner Identity"
color_human = c("#7f0000", "#ff7f7f")

# figure_name = "ECN_mPFC_in-out_age_BehFairSensitivity"
figure_name = "ant_insula_hum-com_SingleTrial"

p_scatter =
  ggplot(plot_df, 
         aes(x = anteriorinsula_corrected,
             y = DV_res,
             color = human)) +
  # geom_point(alpha = data_point_alpha, size = data_point_size, show.legend = FALSE) +
  geom_smooth(formula = "y~x", method = "lm", 
              se = TRUE,
              linetype = "solid",
              linewidth = 2, 
              alpha = 0.2) +
  scale_color_manual(values = color_human, 
                     labels = c("computer", "human")) +
  # guides(color = guide_legend(override.aes = list(fill = NA))) +
  # theme_classic() +
  labs(x = x_label, y = y_label, color = color_label, title = title_label) +
  # guides(color = guide_legend(override.aes = list(fill = NA))) +
  theme(axis.line = element_line(linewidth = 1, colour = "black", linetype=1),
        legend.title = element_text(face = "bold"),
        axis.text.x = element_text(size = axis_text), 
        axis.text.y = element_text(size = axis_text), 
        axis.title.x = element_text(size = axis_title, face="bold"), 
        axis.title.y = element_text(size = axis_title, face="bold"))
        # legend.position="bottom left", legend.box = "horizontal")
        # legend.position="none")

p_scatter

ggsave(paste(figure_dir,
             paste(figure_name, "scatter_manu.png", sep = "_"),
             sep = "/"),
       p_scatter, width = w*1.1, height = h)
```

# behavior
```{r}
model_all_fit = glmer(accept ~ 
                            offer * age_bi + (1|participant_id), 
                          data = all_trials_df, 
                          family = binomial)
summary(model_all_fit)

all_trials_similar_df = all_trials_df[all_trials_df$human == 1,]
model_similar_fit = glmer(accept ~ 
                            offer * age_bi + (1|participant_id), 
                          data = all_trials_similar_df, 
                          family = binomial)
summary(model_similar_fit)
```

### prepare df for ggplot
```{r}
plot_df = all_trials_df %>%
  select(participant_id, accept, 
         age_bi, offer)
```

### plot and save
```{r}
set.seed(1234)

pred_offer_age_prob <-Effect(c("age_bi", "offer"), model_all_fit, 
                             xlevels = list(offer = 1:10) )
pred_offer_age_prob_df<-data.frame(pred_offer_age_prob)

m_params = model_parameters(model_all_fit, effects = "fixed")

p_val = m_params[m_params$Parameter == "offer:age_biolder", "p"]

plot_offer_age = 
ggplot(pred_offer_age_prob_df, aes(x=offer,y=fit,color=age_bi)) +
  geom_line(linewidth = line_width) +
  geom_point(size = point_size-1) +
  geom_errorbar(aes(ymin = fit-0.5*se, ymax = fit+0.5*se),
                width=.1) +
  scale_color_manual(values = color_age) +
  # scale_color_manual(values = c("#E69F00", "#56B4E9", "#009E73")) +
  labs(x = "Offer Size in $", y = "Predicted P(Accept)", color = "Age", 
       title = "Offer Acceptance Probability, all",) + 
  coord_cartesian(xlim=c(1, 10), ylim = c(0,1)) +
  annotate("text", 
           x = -Inf, y = Inf, 
           label = sprintf("p = %.3f", p_val), 
           hjust = -0.2,
           vjust = 2, 
           size = annotate_text, color = "black") +
  theme(axis.line = element_line(linewidth = 1, colour = "black", linetype=1),
        axis.text.x = element_text(size = axis_text), 
        axis.text.y = element_text(size = axis_text), 
        axis.title.x = element_text(size = axis_title, face="bold"), 
        axis.title.y = element_text(size = axis_title, face="bold"))

plot_offer_age

ggsave(paste(figure_dir, "behavior_offer_age_All.png", sep = "/"),
       plot_offer_age, width = w*1.1, height = h)
```



# end of code