---
title: "matlab ugRL fit check"
author: "Jen Yang"
date: "2024-12-12, last modified 2024-12-12"
output: 
  html_document:
    code_folding: hide
    toc: true
    toc_float:
      collapsed: false
      smooth_scroll: false
    hightlight: zenburn
    toc_depth: 6
---

```{r clean, include=FALSE}
# clean environment
rm(list = ls())
```

# Load libraries
```{r libraries, message=FALSE, warning=TRUE, include=FALSE}
library(car)
library(plyr)
library(foreign)
library(pscl)
library(boot)
library(MASS)
library(robust)
library(sfsmisc)
library(ggplot2)
library(reshape2)
library(ppcor)
library(ggrepel)
library(Hmisc)
library(tidyverse)
library(sandwich)
library(ggpubr)
library(interactions)
library(knitr)
library(twowaytests)
library(ggfortify)
library(interactions)
library(broom)
library(patchwork)
library(robustbase)
library(lmtest)
library(modelr)
library(Rmisc)
# library(raincloudplots)
library(cowplot)
library(readr)
library(PupillometryR)
library(ggpp)
library(estimatr)
library(skedastic)
library(ggpubr)
library(lubridate)
library(readxl)
library(gridExtra)
library(scales)
library(rstudioapi)
library(jsonlite)
library(rjson)
library(readr)
library(hBayesDM)
library(brms)
```

# load tsv and prolific raw data
```{r}
gitrepo_path = "/Users/momocco/Documents/GitHub/srndna-ug/behavioral_analyses"

data_dir = paste(gitrepo_path,"data", sep = "/")
codes_dir = paste(gitrepo_path, "codes", sep = "/")
fits_dir = paste(gitrepo_path,"fits", sep = "/")
figures_dir = paste(gitrepo_path,"figures", sep = "/")

bids_dir = "/Users/momocco/Documents/GitHub/srndna-datapaper/bids"
```

# load functions
```{r}
source(paste(codes_dir, "posterior_histo_plot_fun.R", sep = "/"))
source(paste(codes_dir, "corrMatrix_upper_fun.R", sep = "/"))
source(paste(codes_dir, "corrMatrix_plot_fun.R", sep = "/"))
```

# data prep
```{r}
# load sub list
participant_name = "sub_include.csv"
participants_df = read.table(file = paste(data_dir, participant_name, sep = "/"), header = TRUE)

posterior_names = c('alpha_i', 'tau_i', 'epsilon_i')
prior_names = c('alpha0', 'tau0', 'epsilon0', 'norm0')
```

# plot corr matrix and distribution
## figure parameters
```{r}
w_corr = 7
h_corr = 7

h_histo = 7
w_histo = 7
bin_N = 50
bin_N_scaled = 30
```

## alpha 0-20, tau 0-10, norm0 customized based on choice
```{r}
cvs_suff = "_ugrRL.csv"
fig_folder = "ugRL_alpha20tau10"
plot_title = "alpha 0-20, tau 0-10"
param_range = c(20, 10, 1)

for (i in 1:nrow(participants_df)) {
  sub_i_name = participants_df$subjID[i]
  print(paste(i, sub_i_name, sep = "/"))
  
  sub_i_csv = paste(sub_i_name, cvs_suff, sep = "")
  print(sub_i_csv)
  
  sub_i_fit = read.csv(paste(fits_dir, sub_i_csv, sep = "/"), header = T) %>% 
    # filter(exitflag == 1) %>% 
    filter(negLL <= quantile(negLL, probs = 0.05)) %>% 
    select(negLL, prior_names, posterior_names)
  
  posterior_histo_plot_fun(sub_i_name, sub_i_fit, param_range, cvs_suff, fig_folder, w_histo, h_histo, bin_N, bin_N_scaled, figures_dir)
  # corrMatrix_plot_fun(sub_i_name, sub_i_fit, plot_title, w_corr, h_corr, figures_dir, fig_folder)
}
```

## alpha 0-30, tau 0-10, norm0 customized based on choice
```{r}
cvs_suff = "_alpha0_30_ugrRL.csv"
fig_folder = "ugRL_alpha30tau10"
plot_title = "alpha 0-30, tau 0-10"
param_range = c(30, 10, 1)

for (i in 1:nrow(participants_df)) {
  sub_i_name = participants_df$subjID[i]
  print(paste(i, sub_i_name, sep = "/"))
  
  sub_i_csv = paste(sub_i_name, cvs_suff, sep = "")
  print(sub_i_csv)
  
  sub_i_fit = read.csv(paste(fits_dir, sub_i_csv, sep = "/"), header = T) %>% 
    # filter(exitflag == 1) %>% 
    filter(negLL <= quantile(negLL, probs = 0.05)) %>%
    select(negLL, prior_names, posterior_names)
  
  posterior_histo_plot_fun(sub_i_name, sub_i_fit, param_range, cvs_suff, fig_folder, w_histo, h_histo, bin_N, bin_N_scaled, figures_dir)
  corrMatrix_plot_fun(sub_i_name, sub_i_fit, plot_title, w_corr, h_corr, figures_dir, fig_folder)
}
```

## GU paper, norm0 variable 0-20
```{r}
cvs_suff = "_GUpaper_ugrRL.csv"
fig_folder = "ugRL_GUpaper"
plot_title = "alpha 0-1, tau 0-1, norm0 0-20"
param_range = c(1, 1, 1)

for (i in 1:nrow(participants_df)) {
  sub_i_name = participants_df$subjID[i]
  print(paste(i, sub_i_name, sep = "/"))
  
  sub_i_csv = paste(sub_i_name, cvs_suff, sep = "")
  print(sub_i_csv)
  
  sub_i_fit = read.csv(paste(fits_dir, sub_i_csv, sep = "/"), header = T) %>% 
    # filter(exitflag == 1) %>% 
    filter(negLL <= quantile(negLL, probs = 0.05)) %>%
    select(negLL, prior_names, posterior_names)
  
  posterior_histo_plot_fun(sub_i_name, sub_i_fit, param_range, cvs_suff, fig_folder, w_histo, h_histo, bin_N, bin_N_scaled, figures_dir)
  corrMatrix_plot_fun(sub_i_name, sub_i_fit, plot_title, w_corr, h_corr, figures_dir, fig_folder)
}
```

## alpha 0-1, tau 0-1, norm0 customized based on choice
```{r}
cvs_suff = "_alpha0_1_ugrRL.csv"
fig_folder = "ugRL_alpha1tau1"
plot_title = "alpha 0-1, tau 0-1, norm0 choice informed"
param_range = c(1, 1, 1)

# for (i in c(2:10, 12:25, 27:33, 35:nrow(participants_df))) {
for (i in 1:nrow(participants_df)) {
  sub_i_name = participants_df$subjID[i]
  print(paste(i, sub_i_name, sep = "/"))
  
  sub_i_csv = paste(sub_i_name, cvs_suff, sep = "")
  print(sub_i_csv)
  
  sub_i_fit = read.csv(paste(fits_dir, sub_i_csv, sep = "/"), header = T) %>% 
    # filter(exitflag == 1) %>% 
    filter(negLL <= quantile(negLL, probs = 0.05)) %>%
    select(negLL, prior_names, posterior_names)
  
  posterior_histo_plot_fun(sub_i_name, sub_i_fit, param_range, cvs_suff, fig_folder, w_histo, h_histo, bin_N, bin_N_scaled, figures_dir)
  corrMatrix_plot_fun(sub_i_name, sub_i_fit, plot_title, w_corr, h_corr, figures_dir, fig_folder)
}
```

## alpha 0-100, tau 0-20, norm0 customized based on choice
```{r}
cvs_suff = "_alpha100tau20_ugrRL.csv"
fig_folder = "ugRL_alpha100tau20"
dir.create(file.path(figures_dir, fig_folder))
plot_title = "alpha 0-100, tau 0-20, norm0 choice informed"
param_range = c(100, 20, 1)

for (i in 1:nrow(participants_df)) {
  sub_i_name = participants_df$subjID[i]
  print(paste(i, sub_i_name, sep = "/"))
  
  sub_i_csv = paste(sub_i_name, cvs_suff, sep = "")
  print(sub_i_csv)
  
  sub_i_fit = read.csv(paste(fits_dir, sub_i_csv, sep = "/"), header = T) %>% 
    # filter(exitflag == 1) %>% 
    filter(negLL <= quantile(negLL, probs = 0.05)) %>%
    select(negLL, prior_names, posterior_names)
  
  posterior_histo_plot_fun(sub_i_name, sub_i_fit, param_range, cvs_suff, fig_folder, w_histo, h_histo, bin_N, bin_N_scaled, figures_dir)
  corrMatrix_plot_fun(sub_i_name, sub_i_fit, plot_title, w_corr, h_corr, figures_dir, fig_folder)
}
```

## alpha 0-500, tau 0-100, norm0 customized based on choice
```{r}
cvs_suff = "_alpha500tau100norm0rnd_ugrRL.csv"
fig_folder = "ugRL_alpha500tau100norm0rnd"
dir.create(file.path(figures_dir, fig_folder))
plot_title = "alpha 0-500, tau 0-100, norm0 choice informed"
param_range = c(500, 100, 1)

for (i in 1:nrow(participants_df)) {
  sub_i_name = participants_df$subjID[i]
  print(paste(i, sub_i_name, sep = "/"))
  
  sub_i_csv = paste(sub_i_name, cvs_suff, sep = "")
  print(sub_i_csv)
  
  sub_i_fit = read.csv(paste(fits_dir, sub_i_csv, sep = "/"), header = T) %>% 
    # filter(exitflag == 1) %>%
    filter(negLL <= quantile(negLL, probs = 0.05)) %>%
    select(negLL, prior_names, posterior_names)

  posterior_histo_plot_fun(sub_i_name, sub_i_fit, param_range, cvs_suff, fig_folder, w_histo, h_histo, bin_N, bin_N_scaled, figures_dir)
  corrMatrix_plot_fun(sub_i_name, sub_i_fit, plot_title, w_corr, h_corr, figures_dir, fig_folder)
}
```

## alpha 0-500, tau 0-200, norm0 rnd
```{r}
cvs_suff = "_alpha500tau200norm0rnd_ugrRL.csv"
fig_folder = "ugRL_alpha500tau200norm0rnd"
dir.create(file.path(figures_dir, fig_folder))
plot_title = "alpha 0-500, tau 0-200, norm0 choice informed"
param_range = c(500, 200, 1)

# for (i in 1:nrow(participants_df)) {
for (i in 35) {
  sub_i_name = participants_df$subjID[i]
  print(paste(i, sub_i_name, sep = "/"))
  
  sub_i_csv = paste(sub_i_name, cvs_suff, sep = "")
  print(sub_i_csv)
  
  sub_i_fit = read.csv(paste(fits_dir, sub_i_csv, sep = "/"), header = T) %>% 
    # filter(exitflag == 1) %>%
    filter(negLL <= quantile(negLL, probs = 0.05)) %>%
    select(negLL, prior_names, posterior_names)

  posterior_histo_plot_fun(sub_i_name, sub_i_fit, param_range, cvs_suff, fig_folder, w_histo, h_histo, bin_N, bin_N_scaled, figures_dir)
  corrMatrix_plot_fun(sub_i_name, sub_i_fit, plot_title, w_corr, h_corr, figures_dir, fig_folder)
}
```

## alpha 0-500, tau 0-500, norm0 rnd
```{r}
cvs_suff = "_alpha500tau500norm0rnd_ugrRL.csv"
fig_folder = "ugRL_alpha500tau500norm0rnd"
dir.create(file.path(figures_dir, fig_folder))
plot_title = "alpha 0-500, tau 0-500, norm0 choice informed"
param_range = c(500, 500, 1)

# for (i in 1:nrow(participants_df)) {
for (i in 35) {
  sub_i_name = participants_df$subjID[i]
  print(paste(i, sub_i_name, sep = "/"))
  
  sub_i_csv = paste(sub_i_name, cvs_suff, sep = "")
  print(sub_i_csv)
  
  sub_i_fit = read.csv(paste(fits_dir, sub_i_csv, sep = "/"), header = T) %>% 
    # filter(exitflag == 1) %>%
    filter(negLL <= quantile(negLL, probs = 0.05)) %>%
    select(negLL, prior_names, posterior_names)

  posterior_histo_plot_fun(sub_i_name, sub_i_fit, param_range, cvs_suff, fig_folder, w_histo, h_histo, bin_N, bin_N_scaled, figures_dir)
  corrMatrix_plot_fun(sub_i_name, sub_i_fit, plot_title, w_corr, h_corr, figures_dir, fig_folder)
}
```


## alpha 0-700, tau 0-500, norm0 rnd
```{r}
cvs_suff = "_alpha700tau500norm0rnd_ugrRL.csv"
fig_folder = "ugRL_alpha700tau500norm0rnd"
dir.create(file.path(figures_dir, fig_folder))
plot_title = "alpha 0-700, tau 0-500, norm0 choice informed"
param_range = c(700, 500, 1)

# for (i in 1:nrow(participants_df)) {
for (i in 36) {
  sub_i_name = participants_df$subjID[i]
  print(paste(i, sub_i_name, sep = "/"))
  
  sub_i_csv = paste(sub_i_name, cvs_suff, sep = "")
  print(sub_i_csv)
  
  sub_i_fit = read.csv(paste(fits_dir, sub_i_csv, sep = "/"), header = T) %>% 
    # filter(exitflag == 1) %>%
    filter(negLL <= quantile(negLL, probs = 0.05)) %>%
    select(negLL, prior_names, posterior_names)
  
  posterior_histo_plot_fun(sub_i_name, sub_i_fit, param_range, cvs_suff, fig_folder, w_histo, h_histo, bin_N, bin_N_scaled, figures_dir)
  corrMatrix_plot_fun(sub_i_name, sub_i_fit, plot_title, w_corr, h_corr, figures_dir, fig_folder)
}
```

## alpha 0-1000, tau 0-500, norm0 rnd
```{r}
cvs_suff = "_alpha1000tau500norm0rnd_ugrRL.csv"
fig_folder = "ugRL_alpha1000tau500norm0rnd"
dir.create(file.path(figures_dir, fig_folder))
plot_title = "alpha 0-1000, tau 0-500, norm0 choice informed"
param_range = c(1000, 500, 1)

# for (i in 1:nrow(participants_df)) {
for (i in 36) {
  sub_i_name = participants_df$subjID[i]
  print(paste(i, sub_i_name, sep = "/"))
  
  sub_i_csv = paste(sub_i_name, cvs_suff, sep = "")
  print(sub_i_csv)
  
  sub_i_fit = read.csv(paste(fits_dir, sub_i_csv, sep = "/"), header = T) %>% 
    # filter(exitflag == 1) %>%
    filter(negLL <= quantile(negLL, probs = 0.05)) %>%
    select(negLL, prior_names, posterior_names)
  
  posterior_histo_plot_fun(sub_i_name, sub_i_fit, param_range, cvs_suff, fig_folder, w_histo, h_histo, bin_N, bin_N_scaled, figures_dir)
  corrMatrix_plot_fun(sub_i_name, sub_i_fit, plot_title, w_corr, h_corr, figures_dir, fig_folder)
}
```

## alpha 0-2000, tau 0-500, norm0 rnd
```{r}
cvs_suff = "_alpha2000tau500norm0rnd_ugrRL.csv"
fig_folder = "ugRL_alpha2000tau500norm0rnd"
dir.create(file.path(figures_dir, fig_folder))
plot_title = "alpha 0-2000, tau 0-500, norm0 choice informed"
param_range = c(2000, 500, 1)

# for (i in 1:nrow(participants_df)) {
for (i in 36) {
  sub_i_name = participants_df$subjID[i]
  print(paste(i, sub_i_name, sep = "/"))
  
  sub_i_csv = paste(sub_i_name, cvs_suff, sep = "")
  print(sub_i_csv)
  
  sub_i_fit = read.csv(paste(fits_dir, sub_i_csv, sep = "/"), header = T) %>% 
    # filter(exitflag == 1) %>%
    filter(negLL <= quantile(negLL, probs = 0.005)) %>%
    select(negLL, prior_names, posterior_names)
  
  posterior_histo_plot_fun(sub_i_name, sub_i_fit, param_range, cvs_suff, fig_folder, w_histo, h_histo, bin_N, bin_N_scaled, figures_dir)
  corrMatrix_plot_fun(sub_i_name, sub_i_fit, plot_title, w_corr, h_corr, figures_dir, fig_folder)
}
```

## alpha 0-5000, tau 0-500, norm0 rnd
```{r}
N_iter = 10000
cvs_suff = "_alpha5000tau500norm0rnd_ugrRL.csv"
fig_folder = "ugRL_alpha5000tau500norm0rnd"
dir.create(file.path(figures_dir, fig_folder))
plot_title = "alpha 0-5000, tau 0-500, norm0 choice informed"
param_range = c(5000, 500, 1)

# for (i in 1:nrow(participants_df)) {
for (i in 36) {
  sub_i_name = participants_df$subjID[i]
  print(paste(i, sub_i_name, sep = "/"))
  
  sub_i_csv = paste(sub_i_name, cvs_suff, sep = "")
  print(sub_i_csv)
  
  sub_i_fit = read.csv(paste(fits_dir, sub_i_csv, sep = "/"), header = T) %>% 
    filter(exitflag == 1) %>%
    # filter(negLL <= min(negLL) + 1) %>%
    filter(negLL <= max(quantile(negLL, probs = 1000/N_iter), 
                        min(negLL) + 1)) %>%
    select(negLL, prior_names, posterior_names)
  
  posterior_histo_plot_fun(sub_i_name, sub_i_fit, param_range, cvs_suff, fig_folder, w_histo, h_histo, bin_N, bin_N_scaled, figures_dir)
  corrMatrix_plot_fun(sub_i_name, sub_i_fit, plot_title, w_corr, h_corr, figures_dir, fig_folder)
}
```

## alpha 0-20, tau 0-10, norm0 rnd
```{r}
N_iter = 10000
cvs_suff = "_alpha20tau10norm0rnd_ugrRL.csv"
fig_folder = "ugRL_alpha20tau10norm0rnd"
dir.create(file.path(figures_dir, fig_folder))
plot_title = "alpha 0-20, tau 0-10, norm0 choice informed"
param_range = c(20, 10, 1)

for (i in 1:nrow(participants_df)) {
# for (i in 36) {
  sub_i_name = participants_df$subjID[i]
  print(paste(i, sub_i_name, sep = "/"))
  
  sub_i_csv = paste(sub_i_name, cvs_suff, sep = "")
  print(sub_i_csv)
  
   sub_i_fit = read.csv(paste(fits_dir, sub_i_csv, sep = "/"), header = T) %>% 
    filter(exitflag == 1) %>%
    # filter(negLL <= min(negLL) + 1) %>%
    # filter(negLL <= quantile(negLL, probs = 1000/N_iter)) %>%
    filter(negLL <= min(quantile(negLL, probs = 2000/N_iter),
                        min(negLL) + 1)) %>%
    select(negLL, prior_names, posterior_names)
  
  posterior_histo_plot_fun(sub_i_name, sub_i_fit, param_range, cvs_suff, fig_folder, w_histo, h_histo, bin_N, bin_N_scaled, figures_dir)
  corrMatrix_plot_fun(sub_i_name, sub_i_fit, plot_title, w_corr, h_corr, figures_dir, fig_folder)
}
```



