---
title: "full behavioral tests"
author: "Jen Yang"
date: "2025-6-16, last modified 2025-6-16"
output: 
  html_document:
    code_folding: hide
    toc: true
    toc_float:
      collapsed: false
      smooth_scroll: false
    hightlight: zenburn
    toc_depth: 6
---

```{r clean, include=FALSE}
# clean environment
rm(list = ls())
```

# Load libraries
```{r libraries, message=FALSE, warning=TRUE, include=FALSE}
library(car)
library(plyr)
library(foreign)
library(pscl)
library(boot)
library(MASS)
library(robust)
library(sfsmisc)
library(ggplot2)
library(reshape2)
library(ppcor)
library(ggrepel)
library(Hmisc)
library(tidyverse)
library(sandwich)
library(ggpubr)
library(interactions)
library(knitr)
library(twowaytests)
library(ggfortify)
library(broom)
library(patchwork)
library(robustbase)
library(lmtest)
library(modelr)
library(Rmisc)
library(cowplot)
library(readr)
library(PupillometryR)
library(ggpp)
library(estimatr)
library(skedastic)
library(ggpubr)
library(lubridate)
library(readxl)
library(gridExtra)
library(scales)
library(rstudioapi)
library(jsonlite)
library(rjson)
library(readr)
library(hBayesDM)
library(brms)
library(emmeans)
library(mediation)
library(here)
library(lme4)
library(broom.mixed)
library(easyRT)
library(parameters)
library(effectsize)
library(effects)
library(lmerTest)
library(ez)
library(afex)
library(marginaleffects)

library(stringr)
library(performance)
library(lattice)
library(sjPlot)
library(DHARMa)

library(sjPlot)
library(stargazer)
```

# dir and sub info
```{r}
gitrepo_path = "/Users/momocco/Documents/GitHub/srndna-ug/behavioral_analyses"

data_dir = paste(gitrepo_path,"data", sep = "/")
codes_dir = paste(gitrepo_path, "codes", sep = "/")
fit_dir = paste(gitrepo_path,"fits", sep = "/")
figure_dir = paste(gitrepo_path,"figures", sep = "/")
```

# load behavior data
```{r}
all_trials_df = read.csv(file = paste(data_dir, "all_trials_brains.csv", sep = "/"), header = TRUE)
all_trials_df = all_trials_df[all_trials_df$missed == 0, ]

indiv_df = read.csv(paste(data_dir, "participant_check.csv", sep = "/"), header = TRUE)  %>%
  mutate(age_bi = case_when(age <= 36 ~ "younger",
                            age > 36 ~ "older"))

all_trials_df = merge(all_trials_df, indiv_df, by.x = "subjID", by.y = "participant_id")

L3_47_df = read.csv(paste(data_dir, "participant_L3_47.csv", sep = "/"), header = TRUE)

sublist_final = L3_47_df %>% dplyr::select(subjID)

all_trials_df = all_trials_df[all_trials_df$subjID %in% sublist_final$subjID,] 

all_trials_df = all_trials_df %>% 
  mutate(ingroup = relevel(as.factor(ingroup), ref = "0"),
         human = relevel(as.factor(human), ref = "0"),
         age_bi = relevel(as.factor(age_bi), ref = "younger"),
         block_fair = relevel(as.factor(block_fair), ref = "0"),
         accept = relevel(as.factor(accept), ref = "0")) %>% 
  dplyr::select(subjID, offer, accept, human, ingroup, block_fair, age_bi, missed)

all_trials_human_df = all_trials_df[all_trials_df$human == 1,]

```

# BH1 accept ~ offer * similar * age, won't converge
```{r}
offer_age_ingroup_mlm = glmer(accept ~ offer * age_bi * ingroup + 
                          (1+offer|subjID), 
                        data = all_trials_human_df, 
                        family = binomial)
summary(offer_age_ingroup_mlm)
```

# BH1_1 accept ~ offer * similar, NON
```{r}
offer_ingroup_mlm = glmer(accept ~ offer * ingroup + 
                       (1+offer|subjID), 
                 data = all_trials_human_df, 
                 family = binomial)
summary(offer_ingroup_mlm)
```

BH1_2 accept ~ offer * age, NON
```{r}
offer_age_mlm = glmer(accept ~ offer * age_bi + 
                       (1+offer|subjID), 
                 data = all_trials_human_df, 
                 family = binomial)
summary(offer_age_mlm)
```

# BH1_2 accept ~ offer * age, SIG
```{r}
offer_age_mlm = glmer(accept ~ offer * age_bi +
                          (1+offer|subjID), 
                        data = all_trials_human_df, 
                        family = binomial)
summary(offer_age_mlm)
```

# BH1_3 accept ~ offer + age, age not sig
```{r}
offer_age_mlm_3 = glmer(accept ~ offer + age_bi +
                          (1+offer|subjID), 
                        data = all_trials_human_df, 
                        family = binomial)
summary(offer_age_mlm_3)
```

# BH1_4 accept ~ offer + similar, similar not sig
```{r}
offer_similar_mlm_4 = glmer(accept ~ offer + ingroup +
                          (1+offer|subjID), 
                        data = all_trials_human_df, 
                        family = binomial)
summary(offer_similar_mlm_4)
```

# BH1_5 accept ~ offer, SIG
```{r}
offer_mlm = glmer(accept ~ offer + 
                          (1+offer|subjID), 
                        data = all_trials_human_df, 
                        family = binomial)
summary(offer_mlm)
```

# table of estimates
```{r}
stargazer_output1 <- capture.output(stargazer(offer_age_mlm, offer_ingroup_mlm, offer_age_mlm_3, offer_similar_mlm_4, type="text",star.cutoffs=.05,star.char="*", notes="*p<0.05",notes.append=F,
          out = paste(figure_dir, "behavior_tbl1.txt", sep = "/")))
stargazer_output1
write.csv(stargazer_output1, 
          file = paste(figure_dir, "behavior_tbl1.csv", sep = "/"), row.names = FALSE)

stargazer_output2 = capture.output(stargazer(
  # offer_ingroup_mlm, offer_age_mlm, 
          # offer_age_mlm_3, offer_similar_mlm_4,
          offer_mlm,
          type="text",star.cutoffs=.05,star.char="*",
          notes="*p<0.05",notes.append=F,
          out = paste(figure_dir, "behavior_tbl2.txt", sep = "/")))
stargazer_output2
write.csv(stargazer_output2, 
          file = paste(figure_dir, "behavior_tbl2.csv", sep = "/"), row.names = FALSE)



```

# two-step exploratory
## human only
### ingroup
```{r}
## ingroup offer sensitivity
ingroup_df = all_trials_human_df[all_trials_human_df$ingroup == 1,]
ingroup_mlm = glmer(accept ~ offer + (1+offer||subjID), 
                 data = ingroup_df, 
                 family = binomial)
summary(ingroup_mlm)

# ingroup_df = all_trials_human_df[all_trials_human_df$ingroup == 1,]
# ingroup_mlm_2 = glmer(accept ~ offer + (1+offer||subjID), 
#                  data = ingroup_df, 
#                  family = binomial)
# summary(ingroup_mlm_2)
# anova(ingroup_mlm_1, ingroup_mlm_2, refit = F)

ingroup_fixed_effects <- fixef(ingroup_mlm) %>% 
  as.data.frame() %>% 
  rownames_to_column(var = "fixed")

ingroup_random_effects <- ranef(ingroup_mlm, condVar = FALSE) %>% 
  as.data.frame()

ingroup_all_effects = 
  ingroup_random_effects[ingroup_random_effects$term == "offer",] %>% 
  mutate(ingroup_rand = condval,
         ingroup_fixed_rand = 
           condval + ingroup_fixed_effects$.[ingroup_fixed_effects$fixed == "offer"],
         subjID = grp) %>% 
  dplyr::select(subjID, ingroup_rand, ingroup_fixed_rand)
```

### outgroup
```{r}
## outgroup offer sensitivity
outgroup_df = all_trials_human_df[all_trials_human_df$ingroup == 0,]
outgroup_mlm = glmer(accept ~ offer + (1+offer|subjID), 
                    data = outgroup_df, 
                    family = binomial)
summary(outgroup_mlm)

outgroup_fixed_effects <- fixef(outgroup_mlm) %>% 
  as.data.frame() %>% 
  rownames_to_column(var = "fixed")

outgroup_random_effects <- ranef(outgroup_mlm, condVar = FALSE) %>% 
  as.data.frame()

outgroup_all_effects = 
  outgroup_random_effects[outgroup_random_effects$term == "offer",] %>% 
  mutate(outgroup_rand = condval,
         outgroup_fixed_rand = 
           condval + outgroup_fixed_effects$.[outgroup_fixed_effects$fixed == "offer"],
         subjID = grp) %>% 
  dplyr::select(subjID, outgroup_rand, outgroup_fixed_rand)
```

### in-out DV
```{r}
## in-out
in_out_rand_df = merge(ingroup_all_effects, outgroup_all_effects, by = "subjID") %>% 
  mutate(in_out_rand_logit = ingroup_rand - outgroup_rand,
         in_out_full_logit = ingroup_fixed_rand - outgroup_fixed_rand,
         in_out_prob = (exp(ingroup_rand) / (1 + exp(ingroup_rand))) - exp(outgroup_rand) / (1 + exp(outgroup_rand))) %>%
  dplyr::select(subjID, ingroup_fixed_rand, outgroup_fixed_rand, in_out_rand_logit, in_out_full_logit, in_out_prob)
```

## tests
### in_out ~ age, NON
```{r}
in_out_rand_age_df = merge(in_out_rand_df, indiv_df, 
                           by.x = "subjID", by.y = "participant_id")

summary(lm(in_out_rand_logit~age_bi, in_out_rand_age_df))
```

# figure, accept ~ offer
## plot param setup
```{r}
axis_title = 12
axis_ticks = 10
axis_text = 12
axis_label = 12

legend_all = 12

annotate_text = 4
axis_line_width = 1
fit_line_width = 2

data_point_alpha = 0.5
data_point_size = 3*0.8

mean_point_size = 3

line_width = 1
point_size = 3

summary_point_alpha = 1
summary_point_size = 3

annotate_text = 4

w = 3.4
h = 3.4*1.25
```
## prepare df for ggplot
```{r}
plot_df = all_trials_human_df %>% 
  mutate(participant_id = subjID) %>% 
  select(participant_id, accept, 
         age_bi, offer)
```

## plot and save
```{r}
set.seed(1234)

pred_offer_age_prob <-Effect(c("offer"), offer_mlm, 
                             xlevels = list(offer = 1:10) )
pred_offer_age_prob_df<-data.frame(pred_offer_age_prob)

m_params = model_parameters(offer_mlm, effects = "fixed")

p_val = m_params[m_params$Parameter == "offer", "p"]
if (p_val < 0.001) {
  p_val = 0.001
}

plot_offer =
ggplot(pred_offer_age_prob_df, aes(x=offer,y=fit)) +
  geom_line(linewidth = line_width) +
  geom_point(size = point_size-1) +
  geom_errorbar(aes(ymin = fit-0.5*se, ymax = fit+0.5*se),
                width=.1) +
  # scale_color_manual(values = color_age) +
  # scale_color_manual(values = c("#E69F00", "#56B4E9", "#009E73")) +
  labs(x = "Offer Size in $", y = "Predicted P(Accept)", color = "Age", 
       title = "",) + 
  coord_cartesian(xlim=c(1, 10), ylim = c(0,1)) +
  annotate("text", 
           x = -Inf, y = Inf, 
           label = sprintf("p < %.3f", p_val), 
           hjust = -0.2,
           vjust = 2, 
           size = annotate_text, color = "black") +
  theme(axis.line = element_line(linewidth = 1, colour = "black", linetype=1),
        axis.text.x = element_text(size = axis_text), 
        axis.text.y = element_text(size = axis_text), 
        axis.title.x = element_text(size = axis_title, face="bold"), 
        axis.title.y = element_text(size = axis_title, face="bold"))

plot_offer

ggsave(paste(figure_dir, "behavior_offer_manu.png", sep = "/"),
       plot_offer, width = w, height = h/1.75, unit = "in", dpi=300)
```




# end of code