---
title: "full behavioral tests"
author: "Jen Yang"
date: "2025-6-16, last modified 2025-6-16"
output: 
  html_document:
    code_folding: hide
    toc: true
    toc_float:
      collapsed: false
      smooth_scroll: false
    hightlight: zenburn
    toc_depth: 6
---

```{r clean, include=FALSE}
# clean environment
rm(list = ls())
```

# Load libraries
```{r libraries, message=FALSE, warning=TRUE, include=FALSE}
library(car)
library(plyr)
library(foreign)
library(pscl)
library(boot)
library(MASS)
library(robust)
library(sfsmisc)
library(ggplot2)
library(reshape2)
library(ppcor)
library(ggrepel)
library(Hmisc)
library(tidyverse)
library(sandwich)
library(ggpubr)
library(interactions)
library(knitr)
library(twowaytests)
library(ggfortify)
library(broom)
library(patchwork)
library(robustbase)
library(lmtest)
library(modelr)
library(Rmisc)
library(cowplot)
library(readr)
library(PupillometryR)
library(ggpp)
library(estimatr)
library(skedastic)
library(ggpubr)
library(lubridate)
library(readxl)
library(gridExtra)
library(scales)
library(rstudioapi)
library(jsonlite)
library(rjson)
library(readr)
library(hBayesDM)
library(brms)
library(emmeans)
library(mediation)
library(here)
library(lme4)
library(broom.mixed)
library(easyRT)
library(parameters)
library(effectsize)
library(effects)
library(lmerTest)
library(ez)
library(afex)
library(marginaleffects)

library(stringr)
library(performance)
library(lattice)
library(sjPlot)
library(DHARMa)
library(equatiomatic)
```

# dir and sub info
```{r}
gitrepo_path = "/Users/momocco/Documents/GitHub/srndna-ug/behavioral_analyses"

data_dir = paste(gitrepo_path,"data", sep = "/")
codes_dir = paste(gitrepo_path, "codes", sep = "/")
fit_dir = paste(gitrepo_path,"fits", sep = "/")
figure_dir = paste(gitrepo_path,"figures", sep = "/")
```

# load behavior data
```{r}
all_trials_df = read.csv(file = paste(data_dir, "all_trials_brains.csv", sep = "/"), header = TRUE)
all_trials_df = all_trials_df[all_trials_df$missed == 0, ]

indiv_df = read.csv(paste(data_dir, "participant_check.csv", sep = "/"), header = TRUE)  %>%
  mutate(age_bi = case_when(age <= 36 ~ "younger",
                            age > 36 ~ "older"))

all_trials_df = merge(all_trials_df, indiv_df, by.x = "subjID", by.y = "participant_id")

L3_47_df = read.csv(paste(data_dir, "participant_L3_47.csv", sep = "/"), header = TRUE)

sublist_final = L3_47_df %>% dplyr::select(subjID)

all_trials_df = all_trials_df[all_trials_df$subjID %in% sublist_final$subjID,] 

all_trials_df = all_trials_df %>% 
  mutate(ingroup = relevel(as.factor(ingroup), ref = "0"),
         human = relevel(as.factor(human), ref = "0"),
         age_bi = relevel(as.factor(age_bi), ref = "younger"),
         block_fair = relevel(as.factor(block_fair), ref = "0"),
         accept = relevel(as.factor(accept), ref = "0")) %>% 
  dplyr::select(subjID, offer, accept, human, ingroup, block_fair, age_bi, missed)

all_trials_human_df = all_trials_df[all_trials_df$human == 1,]

```

# H1.1 accept ~ offer * hum/computer * age, won't converge
```{r}
age_HumCom_mlm1 = glmer(accept ~ offer * age_bi * human + 
                       (1+offer|subjID), 
                 data = all_trials_df, 
                 family = binomial)
summary(age_HumCom_mlm1)
```

# H1.1 accept ~ offer * hum/computer, NON
```{r}
HumCom_mlm1 = glmer(accept ~ offer * human + 
                       (1+offer|subjID), 
                 data = all_trials_df, 
                 family = binomial)
summary(HumCom_mlm1)
```

# H1.1' accept ~ offer * similar, NON
```{r}
ingroup_mlm1 = glmer(accept ~ offer * ingroup + 
                       (1+offer|subjID), 
                 data = all_trials_human_df, 
                 family = binomial)
summary(ingroup_mlm1)
```

H1.1' accept ~ offer * age, NON
```{r}
age_mlm1 = glmer(accept ~ offer * age_bi + 
                       (1+offer|subjID), 
                 data = all_trials_df, 
                 family = binomial)
summary(age_mlm1)
```


# H1.2 accept ~ offer * similar/dissimilar * age, won't converge
```{r}
age_ingroup_mlm1 = glmer(accept ~ offer * age_bi * ingroup + 
                          (1+offer|subjID), 
                        data = all_trials_human_df, 
                        family = binomial)
summary(age_ingroup_mlm1)
```

# H1.2 accept ~ offer * similar/dissimilar, NON
```{r}
age_ingroup_mlm2 = glmer(accept ~ offer * ingroup + 
                          (1+offer|subjID), 
                        data = all_trials_human_df, 
                        family = binomial)
summary(age_ingroup_mlm2)
```

# H1.2' accept ~ offer * age, NON
```{r}
age_ingroup_mlm3 = glmer(accept ~ offer * age_bi + 
                          (1+offer|subjID), 
                        data = all_trials_human_df, 
                        family = binomial)
summary(age_ingroup_mlm3)
```

# accept ~ offer, SIG
```{r}
all_trials_human_df = all_trials_human_df %>% mutate(offer_sd = as.numeric(scale(offer))) 
offer_mlm = glmer(accept ~ offer + 
                          (1+offer|subjID), 
                        data = all_trials_human_df, 
                        family = binomial)
summary(offer_mlm)
```


# two-step exploratory
## human only
### ingroup
```{r}
## ingroup offer sensitivity
ingroup_df = all_trials_human_df[all_trials_human_df$ingroup == 1,]
ingroup_mlm = glmer(accept ~ offer + (1+offer||subjID), 
                 data = ingroup_df, 
                 family = binomial)
summary(ingroup_mlm)

# ingroup_df = all_trials_human_df[all_trials_human_df$ingroup == 1,]
# ingroup_mlm_2 = glmer(accept ~ offer + (1+offer||subjID), 
#                  data = ingroup_df, 
#                  family = binomial)
# summary(ingroup_mlm_2)
# anova(ingroup_mlm_1, ingroup_mlm_2, refit = F)

ingroup_fixed_effects <- fixef(ingroup_mlm) %>% 
  as.data.frame() %>% 
  rownames_to_column(var = "fixed")

ingroup_random_effects <- ranef(ingroup_mlm, condVar = FALSE) %>% 
  as.data.frame()

ingroup_all_effects = 
  ingroup_random_effects[ingroup_random_effects$term == "offer",] %>% 
  mutate(ingroup_rand = condval,
         ingroup_fixed_rand = 
           condval + ingroup_fixed_effects$.[ingroup_fixed_effects$fixed == "offer"],
         subjID = grp) %>% 
  dplyr::select(subjID, ingroup_rand, ingroup_fixed_rand)
```

### outgroup
```{r}
## outgroup offer sensitivity
outgroup_df = all_trials_human_df[all_trials_human_df$ingroup == 0,]
outgroup_mlm = glmer(accept ~ offer + (1+offer|subjID), 
                    data = outgroup_df, 
                    family = binomial)
summary(outgroup_mlm)

outgroup_fixed_effects <- fixef(outgroup_mlm) %>% 
  as.data.frame() %>% 
  rownames_to_column(var = "fixed")

outgroup_random_effects <- ranef(outgroup_mlm, condVar = FALSE) %>% 
  as.data.frame()

outgroup_all_effects = 
  outgroup_random_effects[outgroup_random_effects$term == "offer",] %>% 
  mutate(outgroup_rand = condval,
         outgroup_fixed_rand = 
           condval + outgroup_fixed_effects$.[outgroup_fixed_effects$fixed == "offer"],
         subjID = grp) %>% 
  dplyr::select(subjID, outgroup_rand, outgroup_fixed_rand)
```

### in-out DV
```{r}
## in-out
in_out_rand_df = merge(ingroup_all_effects, outgroup_all_effects, by = "subjID") %>% 
  mutate(in_out_rand_logit = ingroup_rand - outgroup_rand,
         in_out_full_logit = ingroup_fixed_rand - outgroup_fixed_rand,
         in_out_prob = (exp(ingroup_rand) / (1 + exp(ingroup_rand))) - exp(outgroup_rand) / (1 + exp(outgroup_rand))) %>%
  dplyr::select(subjID, ingroup_fixed_rand, outgroup_fixed_rand, in_out_rand_logit, in_out_full_logit, in_out_prob)
```

## computer vs human
### computer
```{r}
## computer offer sensitivity
computer_df = all_trials_df[all_trials_df$human == 0,]
computer_mlm = glmer(accept ~ offer + (1+offer|subjID), 
                     data = computer_df, 
                     family = binomial)
summary(computer_mlm)

computer_fixed_effects <- fixef(computer_mlm) %>% 
  as.data.frame() %>% 
  rownames_to_column(var = "fixed")

computer_random_effects <- ranef(computer_mlm, condVar = FALSE) %>% 
  as.data.frame()

computer_all_effects = 
  computer_random_effects[computer_random_effects$term == "offer",] %>% 
  mutate(computer_rand = condval,
         computer_fixed_rand = 
           condval + computer_fixed_effects$.[computer_fixed_effects$fixed == "offer"],
         subjID = grp) %>% 
  dplyr::select(subjID, computer_rand, computer_fixed_rand)
```

### human
```{r}
## human offer sensitivity
human_df = all_trials_df[all_trials_df$human == 1,]
human_mlm = glmer(accept ~ offer + (1+offer|subjID), 
                     data = human_df, 
                     family = binomial)
summary(human_mlm)

human_fixed_effects <- fixef(human_mlm) %>% 
  as.data.frame() %>% 
  rownames_to_column(var = "fixed")

human_random_effects <- ranef(human_mlm, condVar = FALSE) %>% 
  as.data.frame()

human_all_effects = 
  human_random_effects[human_random_effects$term == "offer",] %>% 
  mutate(human_rand = condval,
         human_fixed_rand = 
           condval + human_fixed_effects$.[human_fixed_effects$fixed == "offer"],
         subjID = grp) %>% 
  dplyr::select(subjID, human_rand, human_fixed_rand)
```

### human-computer DV
```{r}
## in-out
hum_com_rand_df = merge(human_all_effects, computer_all_effects, by = "subjID") %>% 
  mutate(hum_com_rand_logit = human_rand - computer_rand,
         hum_com_full_logit = human_fixed_rand - computer_fixed_rand,
         hum_com_prob = (exp(human_rand) / (1 + exp(human_rand))) - exp(computer_rand) / (1 + exp(computer_rand))) %>%
  dplyr::select(subjID, human_fixed_rand, computer_fixed_rand, hum_com_rand_logit, hum_com_full_logit, hum_com_prob)
```

## tests
### human_computer ~ age
```{r}
hum_com_rand_age_df = merge(hum_com_rand_df, indiv_df, 
                           by.x = "subjID", by.y = "participant_id")

summary(lm(hum_com_rand_logit~age_bi, hum_com_rand_age_df))
```


### in_out ~ age, NON
```{r}
in_out_rand_age_df = merge(in_out_rand_df, indiv_df, 
                           by.x = "subjID", by.y = "participant_id")

summary(lm(in_out_rand_logit~age_bi, in_out_rand_age_df))
```

# end of code