---
title: "block_hypotheses_tests_srndnaUGR"
author: "Jen Yang"
date: "2025-06-02, last modified 2025-07-02"
output: 
  html_document:
    code_folding: hide
    toc: true
    toc_float:
      collapsed: false
      smooth_scroll: false
    hightlight: zenburn
    toc_depth: 6
---

```{r clean, include=FALSE}
# clean environment
rm(list = ls())
```

# Load libraries
```{r libraries, message_bi=FALSE, warning=TRUE, include=FALSE}
library(car)
library(plyr)
library(foreign)
library(pscl)
library(boot)
library(MASS)
library(robust)
library(sfsmisc)
library(ggplot2)
library(reshape2)
library(ppcor)
library(ggrepel)
library(Hmisc)
library(tidyverse)
library(sandwich)
library(ggpubr)
library(interactions)
library(knitr)
library(twowaytests)
library(ggfortify)
library(broom)
library(patchwork)
library(robustbase)
library(lmtest)
library(modelr)
library(Rmisc)
library(cowplot)
library(readr)
library(PupillometryR)
library(ggpp)
library(estimatr)
library(skedastic)
library(ggpubr)
library(lubridate)
library(readxl)
library(gridExtra)
library(scales)
library(rstudioapi)
library(jsonlite)
library(rjson)
library(readr)
library(hBayesDM)
library(brms)
library(emmeans)
library(mediation)
library(here)
library(lme4)
library(broom.mixed)
library(easyRT)
library(parameters)
library(effectsize)
library(effects)
library(lmerTest)
library(ez)
library(afex)
library(marginaleffects)

library(stringr)
library(performance)
library(lattice)
library(sjPlot)
library(DHARMa)
library(equatiomatic)
```

```{r}
set.seed(123)
```

# set directories
```{r}
gitrepo_path = "/Users/momocco/Documents/GitHub/srndna-ug/behavioral_analyses"

data_dir = paste(gitrepo_path,"data", sep = "/")
codes_dir = paste(gitrepo_path, "codes", sep = "/")
fit_dir = paste(gitrepo_path,"fits", sep = "/")
figure_dir = paste(gitrepo_path,"figures", sep = "/")
```

# load and prepare data
```{r}
# load subs
all_trials_df = read.csv(paste(data_dir, "all_trials_brains.csv", sep = "/"), header = TRUE) %>% 
  .[.$missed == 0,]

colnames(all_trials_df)[colnames(all_trials_df) == "subjID"] <- "participant_id"
indiv_df = read.csv(paste(data_dir, "participant_check.csv", sep = "/"), header = TRUE)  %>%
  mutate(age_bi = case_when(age <= 36 ~ "younger",
                            age > 36 ~ "older"))

all_trials_df = merge(all_trials_df, indiv_df, by.x = "participant_id", by.y = "participant_id")

sublist_final = read.csv(paste(data_dir, "participant_L3_47.csv", sep = "/"), header = TRUE)

all_trials_df = all_trials_df[all_trials_df$participant_id %in% sublist_final$subjID,]
```

# recode partner identity, group_tri, and age group, age_bi
```{r}
## add a categorical variable that differentiate three groups
all_trials_df = all_trials_df %>% 
  mutate(group_tri = as.factor(case_when(human == 0 ~ 0, # computer
                               human == 1 & ingroup == 0 ~ 1, # outgroup
                               human == 1 & ingroup == 1 ~ 2))) # ingroup
# all_trials_df$group_tri = relevel(all_trials_df$group_tri, ref = "0") # computer

all_trials_df = all_trials_df %>% mutate(human = as.factor(human))

all_trials_df$group_tri = relevel(all_trials_df$group_tri, ref = "1") # outgroup

all_trials_df$age_bi = relevel(as.factor(all_trials_df$age_bi), ref = "younger")

all_trials_df = all_trials_df %>% 
  mutate(age_bi_dummy = case_when(age_bi == "younger" ~ 0,
                                  age_bi == "older" ~ 1)
         )
```

# factorize vars as needed
```{r}
factor_col_names = c("participant_id", "run", "missed", "accept",
                     "ingroup", "block_fair", "sex")
all_trials_df[factor_col_names] %<>% lapply(., factor) 
```

# case count of each possible combination of offer size and block type
```{r}
offer_block_tbl = table(all_trials_df$offer, all_trials_df$block_fair)
print(offer_block_tbl)
```


# filter trials, keep only 25% and 30% offers
these two offers exist in both block types, therefore in theory would reduce collinearity
```{r}
all_trials_df_filtered = all_trials_df %>%  filter(offer %in% c(20*0.25, 20*0.3)) # 25% and 30% of 20
```

# test correlation between offer and block type for collinearity
offer and block type are highly correlated. will have collinearity problem if both are included in a model.
```{r}
offer_block_m = lmer(offer~block_fair + (1 + offer ||participant_id), 
                     data = all_trials_df)
summary(offer_block_m)
icc(offer_block_m)
```

# test correlation between FILTERED offer and block type for collinearity
FILTERED offer and block type are NO LONGER correlated!
```{r}
offerFILTERED_block_m = glmer(block_fair ~ offer + (1 + offer ||participant_id), 
                             data = all_trials_df_filtered,
                             family = "binomial")
summary(offerFILTERED_block_m)
icc(offerFILTERED_block_m)

offer_block_m = lmer(offer~block_fair + (1 + offer ||participant_id), 
                     data = all_trials_df_filtered)
summary(offerFILTERED_block_m)
icc(offerFILTERED_block_m)
```

# accept ~ block * age_bi * group_tri + offer
```{r}
## won't converge
# block_age_group_m1 =
#   glmer(accept ~ block_fair * age_bi * group_tri + offer +
#           (1 + offer ||participant_id),
#         data = all_trials_df_filtered,
#         family = binomial)
# summary(block_age_group_m1)

## won't converge
# block_age_group_m2 =
#   glmer(accept ~ block_fair * group_tri + block_fair * age_bi + offer +
#           (1 + offer ||participant_id),
#         data = all_trials_df_filtered,
#         family = binomial)
# summary(block_age_group_m2)

## converged. nothing.
block_age_group_m3 = 
  glmer(accept ~ block_fair * group_tri + age_bi + offer +
          (1 + offer||participant_id),
        data = all_trials_df_filtered,
        family = binomial)
summary(block_age_group_m3)
icc(block_age_group_m3)

## tested if random slope is necessary. anova result indicates it's unnecessary.
block_age_group_m3_1 = 
  glmer(accept ~ block_fair * age_bi + group_tri + offer +
          (1|participant_id),
        data = all_trials_df_filtered,
        family = binomial)
summary(block_age_group_m3_1)

anova(block_age_group_m3_1, block_age_group_m3, refit = FALSE) # p = 0.9

## converged. nothing.
block_age_group_m4 = 
  glmer(accept ~ block_fair * age_bi + group_tri + offer +
          (1 |participant_id),
        data = all_trials_df_filtered,
        family = binomial)
summary(block_age_group_m4)

## converged. nothing.
block_age_group_m5 = 
  glmer(accept ~ block_fair + age_bi + group_tri + offer +
          (1|participant_id),
        data = all_trials_df_filtered,
        family = binomial)
summary(block_age_group_m5)
```

