---
title: "prereg 1 activation ROI test"
author: "Jen Yang"
date: "2025-07-08, last modified 2025-07-08"
output: 
  html_document:
    code_folding: hide
    toc: true
    toc_float:
      collapsed: false
      smooth_scroll: false
    hightlight: zenburn
    toc_depth: 6
---

```{r clean, include=FALSE}
# clean environment
rm(list = ls())
```

# Load libraries
```{r libraries, message_bi=FALSE, warning=TRUE, include=FALSE}
library(car)
library(plyr)
library(foreign)
library(pscl)
library(boot)
library(MASS)
library(robust)
library(sfsmisc)
library(ggplot2)
library(reshape2)
library(ppcor)
library(ggrepel)
library(Hmisc)
library(tidyverse)
library(sandwich)
library(ggpubr)
library(interactions)
library(knitr)
library(twowaytests)
library(ggfortify)
library(broom)
library(patchwork)
library(robustbase)
library(lmtest)
library(modelr)
library(Rmisc)
library(cowplot)
library(readr)
library(PupillometryR)
library(ggpp)
library(estimatr)
library(skedastic)
library(ggpubr)
library(lubridate)
library(readxl)
library(gridExtra)
library(scales)
library(rstudioapi)
library(jsonlite)
library(rjson)
library(readr)
library(hBayesDM)
library(brms)
library(emmeans)
library(mediation)
library(here)
library(lme4)
library(broom.mixed)
library(easyRT)
library(parameters)
library(effectsize)
library(effects)
library(lmerTest)
library(ez)
library(afex)
library(marginaleffects)

library(stringr)
library(performance)
library(lattice)
library(sjPlot)
library(DHARMa)
library(equatiomatic)

library(magrittr)
```

```{r}
set.seed(123)
```

# directories
```{r}
srndna_path = "/Users/momocco/Documents/GitHub/srndna-ug"
ROImean_path = "imaging_plots_reg1"
gitrepo_path = "/Users/momocco/Documents/GitHub/srndna-ug/behavioral_analyses"

data_dir = paste(gitrepo_path,"data", sep = "/")
codes_dir = paste(gitrepo_path, "codes", sep = "/")
fit_dir = paste(gitrepo_path,"fits", sep = "/")
figure_dir = paste(gitrepo_path,"figures", sep = "/")
```

# load and prepare data
## load participant list and demographics
```{r}
list_fmri_df = read.csv(paste(data_dir, "participant_L3_47.csv", sep = "/"),
                          header = T) %>% dplyr::select(subjID)

participant_check_df = read.csv(paste(data_dir, "participant_check.csv", sep = "/"), header = T)

participant_demo_df = 
  merge(list_fmri_df, participant_check_df, by.x = "subjID", by.y = "participant_id", all.x = T) %>% 
  mutate(age_bi = case_when(age <= 36 ~ "younger", age > 36 ~ "older"),
         age_bi = relevel(as.factor(age_bi), ref = "younger"))
```

## load ROI means and combine into a wide df
```{r}
# dlpfc
dlpfc_comp_df = read.table(
  paste(srndna_path, ROImean_path,
         "bi_nanRemoved_resliced_dlpfc_sphere5_brain_type-act_cope-02.txt", sep = "/"),
  sep = "\t", header = FALSE)

dlpfc_similar_df = read.table(
  paste(srndna_path, ROImean_path,
        "bi_nanRemoved_resliced_dlpfc_sphere5_brain_type-act_cope-04.txt", sep = "/"),
  sep = "\t", header = FALSE)

dlpfc_dissimilar_df = read.table(
  paste(srndna_path, ROImean_path,
        "bi_nanRemoved_resliced_dlpfc_sphere5_brain_type-act_cope-06.txt", sep = "/"),
  sep = "\t", header = FALSE)

# anterior insula
antInsula_comp_df = read.table(
  paste(srndna_path, ROImean_path,
        "bi_nanRemoved_resliced_anteriorinsula_sphere5_mask_type-act_cope-02.txt", sep = "/"),
  sep = "\t", header = FALSE)

antInsula_similar_df = read.table(
  paste(srndna_path, ROImean_path,
        "bi_nanRemoved_resliced_anteriorinsula_sphere5_mask_type-act_cope-04.txt", sep = "/"),
  sep = "\t", header = FALSE)

antInsula_dissimilar_df = read.table(
  paste(srndna_path, ROImean_path,
        "bi_nanRemoved_resliced_anteriorinsula_sphere5_mask_type-act_cope-06.txt", sep = "/"),
  sep = "\t", header = FALSE)

# pTPJ
pTPJ_comp_df = read.table(
  paste(srndna_path, ROImean_path,
        "bi_nanRemoved_resliced_seed-pTPJ_type-act_cope-02.txt", sep = "/"),
  sep = "\t", header = FALSE)

pTPJ_similar_df = read.table(
  paste(srndna_path, ROImean_path,
        "bi_nanRemoved_resliced_seed-pTPJ_type-act_cope-04.txt", sep = "/"),
  sep = "\t", header = FALSE)

pTPJ_dissimilar_df = read.table(
  paste(srndna_path, ROImean_path,
        "bi_nanRemoved_resliced_seed-pTPJ_type-act_cope-06.txt", sep = "/"),
  sep = "\t", header = FALSE)

# combine all df
all_df = participant_demo_df %>% 
  mutate(dlpfc_comp = dlpfc_comp_df$V1,
         dlpfc_similar = dlpfc_similar_df$V1,
         dlpfc_dissimilar = dlpfc_dissimilar_df$V1,
         antInsula_comp = antInsula_comp_df$V1,
         antInsula_similar = antInsula_similar_df$V1,
         antInsula_dissimilar = antInsula_dissimilar_df$V1,
         pTPJ_comp = pTPJ_comp_df$V1,
         pTPJ_similar = pTPJ_similar_df$V1,
         pTPJ_dissimilar = pTPJ_dissimilar_df$V1)

all_df$age_bi = relevel(all_df$age_bi, ref = "younger")
```

# H2.1
H2.1: Recruitment of neural circuits associated with processing social norm violations (DLPFC, insula) will be diminished in older adults during receipt of unfair offers from human vs. computer partners.

## dlpfc
### make long format df
```{r}
# make long format df
dlpfc_df = all_df %>% 
  select(subjID, age_bi, dlpfc_comp, dlpfc_similar, dlpfc_dissimilar) %>% 
  pivot_longer(
    cols = starts_with("dlpfc_"), # A helpful way to select columns
    names_to = "partner",
    names_prefix = "dlpfc_",     # Remove this prefix from the new column names
    values_to = "roi_mean"
  ) %>% 
  mutate(partner = as.factor(partner),
         subjID = as.factor(subjID),
         age_bi = as.factor(age_bi))
```

### similar vs dissimilar, age sig
```{r}
dlpfc_df_similar = filter(dlpfc_df, partner %in% c("similar", "dissimilar"))

# partner * age_bi, nothing
dlpfc_similar_age = lmer(roi_mean ~ partner * age_bi + (1|subjID),
                        data = dlpfc_df_similar)
summary(dlpfc_similar_age)

# partner, nothing
dlpfc_similar = lmer(roi_mean ~ partner + (1|subjID),
                        data = dlpfc_df_similar)
summary(dlpfc_similar)

# age, p = 0.0355
dlpfc_age = lmer(roi_mean ~ age_bi + (1|subjID),
                        data = dlpfc_df_similar)
summary(dlpfc_age)
```

### human vs computer, partner * age sig
```{r}
dlpfc_df_comp = all_df %>% 
  select(subjID, age_bi, dlpfc_comp, dlpfc_similar, dlpfc_dissimilar) %>% 
  mutate(dlpfc_hum = 0.5 *(dlpfc_similar+dlpfc_dissimilar)) %>% 
  select(subjID, age_bi, dlpfc_comp, dlpfc_hum) %>% 
  pivot_longer(
    cols = starts_with("dlpfc_"), # A helpful way to select columns
    names_to = "partner",
    names_prefix = "dlpfc_",     # Remove this prefix from the new column names
    values_to = "roi_mean"
  ) %>% 
  mutate(partner = as.factor(partner),
         subjID = as.factor(subjID))

# partner * age_bi, p = 0.0412
dlpfc_comp_age = lmer(roi_mean ~ partner * age_bi + (1|subjID),
                         data = dlpfc_df_comp)
summary(dlpfc_comp_age)

# # partner
# dlpfc_comp = lmer(roi_mean ~ partner + (1|subjID),
#                      data = dlpfc_df_comp)
# summary(dlpfc_comp)
# 
# # age
# dlpfc_age = lmer(roi_mean ~ age_bi + (1|subjID),
#                  data = dlpfc_df_comp)
# summary(dlpfc_age)
```

## anterior insula
### make long format df
```{r}
# make long format df
antInsula_df = all_df %>% 
  select(subjID, age_bi, antInsula_comp, antInsula_similar, antInsula_dissimilar) %>% 
  pivot_longer(
    cols = starts_with("antInsula_"), # A helpful way to select columns
    names_to = "partner",
    names_prefix = "antInsula_",     # Remove this prefix from the new column names
    values_to = "roi_mean"
  ) %>% 
  mutate(partner = as.factor(partner),
         subjID = as.factor(subjID),
         age_bi = as.factor(age_bi))
```

### similar vs dissimilar, nothing
```{r}
antInsula_df_similar = filter(antInsula_df, partner %in% c("similar", "dissimilar"))

# partner * age_bi, nothing
antInsula_similar_age = lmer(roi_mean ~ partner * age_bi + (1|subjID),
                         data = antInsula_df_similar)
summary(antInsula_similar_age)

# partner, nothing
antInsula_similar = lmer(roi_mean ~ partner + (1|subjID),
                     data = antInsula_df_similar)
summary(antInsula_similar)

# age, nothing
antInsula_age = lmer(roi_mean ~ age_bi + (1|subjID),
                 data = antInsula_df_similar)
summary(antInsula_age)
```

### human vs computer
```{r}
antInsula_df_comp = all_df %>% 
  select(subjID, age_bi, antInsula_comp, antInsula_similar, antInsula_dissimilar) %>% 
  mutate(antInsula_hum = 0.5 *(antInsula_similar+antInsula_dissimilar)) %>% 
  select(subjID, age_bi, antInsula_comp, antInsula_hum) %>% 
  pivot_longer(
    cols = starts_with("antInsula_"), # A helpful way to select columns
    names_to = "partner",
    names_prefix = "antInsula_",     # Remove this prefix from the new column names
    values_to = "roi_mean"
  ) %>% 
  mutate(partner = as.factor(partner),
         subjID = as.factor(subjID))

# partner * age_bi, nothing
antInsula_comp_age = lmer(roi_mean ~ partner * age_bi + (1|subjID),
                         data = antInsula_df_comp)
summary(antInsula_comp_age)

# partner, nothing
antInsula_comp = lmer(roi_mean ~ partner + (1|subjID),
                     data = antInsula_df_comp)
summary(antInsula_comp)

# age, nothing
antInsula_age = lmer(roi_mean ~ age_bi + (1|subjID),
                 data = antInsula_df_comp)
summary(antInsula_age)
```

# pTPJ
### make long format df
```{r}
# make long format df
pTPJ_df = all_df %>% 
  select(subjID, age_bi, pTPJ_comp, pTPJ_similar, pTPJ_dissimilar) %>% 
  pivot_longer(
    cols = starts_with("pTPJ_"), # A helpful way to select columns
    names_to = "partner",
    names_prefix = "pTPJ_",     # Remove this prefix from the new column names
    values_to = "roi_mean"
  ) %>% 
  mutate(partner = as.factor(partner),
         subjID = as.factor(subjID),
         age_bi = as.factor(age_bi))
```

### similar vs dissimilar, nothing
```{r}
pTPJ_df_similar = filter(pTPJ_df, partner %in% c("similar", "dissimilar"))

# partner * age_bi, nothing
pTPJ_similar_age = lmer(roi_mean ~ partner * age_bi + (1|subjID),
                             data = pTPJ_df_similar)
summary(pTPJ_similar_age)

# partner, nothing
pTPJ_similar = lmer(roi_mean ~ partner + (1|subjID),
                         data = pTPJ_df_similar)
summary(pTPJ_similar)

# age, nothing
pTPJ_age = lmer(roi_mean ~ age_bi + (1|subjID),
                     data = pTPJ_df_similar)
summary(pTPJ_age)
```

### human vs computer
```{r}
pTPJ_df_comp = all_df %>% 
  select(subjID, age_bi, pTPJ_comp, pTPJ_similar, pTPJ_dissimilar) %>% 
  mutate(pTPJ_hum = 0.5 *(pTPJ_similar+pTPJ_dissimilar)) %>% 
  select(subjID, age_bi, pTPJ_comp, pTPJ_hum) %>% 
  pivot_longer(
    cols = starts_with("pTPJ_"), # A helpful way to select columns
    names_to = "partner",
    names_prefix = "pTPJ_",     # Remove this prefix from the new column names
    values_to = "roi_mean"
  ) %>% 
  mutate(partner = as.factor(partner),
         subjID = as.factor(subjID))

# partner * age_bi, nothing
pTPJ_comp_age = lmer(roi_mean ~ partner * age_bi + (1|subjID),
                          data = pTPJ_df_comp)
summary(pTPJ_comp_age)

# partner, nothing
pTPJ_comp = lmer(roi_mean ~ partner + (1|subjID),
                      data = pTPJ_df_comp)
summary(pTPJ_comp)

# age, nothing
pTPJ_age = lmer(roi_mean ~ age_bi + (1|subjID),
                     data = pTPJ_df_comp)
summary(pTPJ_age)
```
# to continue



# end of code

