---
title: "singletrial_hypotheses_tests_srndnaUGR"
author: "Jen Yang"
date: "2025-04-09, last modified 2025-07-03"
output: 
  html_document:
    code_folding: hide
    toc: true
    toc_float:
      collapsed: false
      smooth_scroll: false
    hightlight: zenburn
    toc_depth: 6
---

```{r clean, include=FALSE}
# clean environment
rm(list = ls())
```

# Load libraries
```{r libraries, message_bi=FALSE, warning=TRUE, include=FALSE}
library(car)
library(plyr)
library(foreign)
library(pscl)
library(boot)
library(MASS)
library(robust)
library(sfsmisc)
library(ggplot2)
library(reshape2)
library(ppcor)
library(ggrepel)
library(Hmisc)
library(tidyverse)
library(sandwich)
library(ggpubr)
library(interactions)
library(knitr)
library(twowaytests)
library(ggfortify)
library(broom)
library(patchwork)
library(robustbase)
library(lmtest)
library(modelr)
library(Rmisc)
library(cowplot)
library(readr)
library(PupillometryR)
library(ggpp)
library(estimatr)
library(skedastic)
library(ggpubr)
library(lubridate)
library(readxl)
library(gridExtra)
library(scales)
library(rstudioapi)
library(jsonlite)
library(rjson)
library(readr)
library(hBayesDM)
library(brms)
library(emmeans)
library(mediation)
library(here)
library(lme4)
library(broom.mixed)
library(easyRT)
library(parameters)
library(effectsize)
library(effects)
library(lmerTest)
library(ez)
library(afex)
library(marginaleffects)

library(stringr)
library(performance)
library(lattice)
library(sjPlot)
library(DHARMa)
library(equatiomatic)

library(magrittr)
```

```{r}
set.seed(123)
```

# directories
```{r}
gitrepo_path = "/Users/momocco/Documents/GitHub/srndna-ug/behavioral_analyses"

data_dir = paste(gitrepo_path,"data", sep = "/")
codes_dir = paste(gitrepo_path, "codes", sep = "/")
fit_dir = paste(gitrepo_path,"fits", sep = "/")
figure_dir = paste(gitrepo_path,"figures", sep = "/")
```

# load and prepare data
```{r}
# load subs
all_trials_df = read.csv(paste(data_dir, "all_trials_brains.csv", sep = "/"), header = TRUE) %>% 
  .[.$missed == 0,]

colnames(all_trials_df)[colnames(all_trials_df) == "subjID"] <- "participant_id"
indiv_df = read.csv(paste(data_dir, "participant_check.csv", sep = "/"), header = TRUE)  %>%
  mutate(age_bi = case_when(age <= 36 ~ "younger",
                            age > 36 ~ "older"))

all_trials_df = merge(all_trials_df, indiv_df, by.x = "participant_id", by.y = "participant_id")

sublist_final = read.csv(paste(data_dir, "participant_L3_47.csv", sep = "/"), header = TRUE)

all_trials_df = all_trials_df[all_trials_df$participant_id %in% sublist_final$subjID,]
```

## recode group and age
```{r}
## add a categorical variable that differentiate three groups
all_trials_df = all_trials_df %>% 
  mutate(group_tri = as.factor(case_when(human == 0 ~ 0, # computer
                               human == 1 & ingroup == 0 ~ 1, # outgroup
                               human == 1 & ingroup == 1 ~ 2))) # ingroup
# all_trials_df$group_tri = relevel(all_trials_df$group_tri, ref = "0") # computer

all_trials_df = all_trials_df %>% mutate(human = as.factor(human))

all_trials_df$group_tri = relevel(all_trials_df$group_tri, ref = "1") # outgroup

all_trials_df$age_bi = relevel(as.factor(all_trials_df$age_bi), ref = "younger")

all_trials_df = all_trials_df %>% 
  mutate(age_bi_dummy = case_when(age_bi == "younger" ~ 0,
                                  age_bi == "older" ~ 1)
         )
```

## factorize vars as needed
```{r}
factor_col_names = c("participant_id", "run", "missed", "accept",
                     "ingroup", "block_fair", "sex")
all_trials_df[factor_col_names] %<>% lapply(., factor) 
```

## add fdmean, tsnr vars to data
```{r}
fmri_control_data = 
  read.csv(paste(data_dir, "Task-ultimatum_Level-Run_Outlier-info.csv", 
                 sep = "/"), header = TRUE) %>% 
  filter(Sub %in% sublist_final$subjID == 1) %>% 
  # mutate(subjID = Sub) %>% 
  select(-task, -outlier_run_Custom1)

all_trials_df = merge(all_trials_df, fmri_control_data, 
                      by.x = c("participant_id", "run"),
                      by.y = c("Sub", "run"))
```

## remove incomplete rows
```{r}
all_trials_df %<>% na.omit
```

## standardize data to facilitate convergence
```{r}
col_stnd = c("offer", "response_time", 
             "anteriorinsula_corrected", "dacc_corrected", "VS_corrected", "vmpfc_corrected",
             "tsnr", "fd_mean")

all_trials_df %<>%
  mutate(across(all_of(col_stnd), ~as.numeric(scale(.))))
```

## create human-only dataset
```{r}
all_trials_similar_df = filter(all_trials_df, human == "1")
```


## test if it's worth adding random slope for response time (perhaps)
```{r}
summary(
  glmer(accept ~ response_time + 
          (1 + response_time||participant_id ), 
        data = all_trials_df,
       family = binomial))
```


# P2 NH1A, group_tri & age_bi respectively
"NH1A) The anterior insula (ins), dorsal anterior cingulate cortex (dACC), ventromedial prefrontal cortex (vmPFC), and ventral striatum (VS) will be associated with choice." [ins, dACC, vmPFC, VS]

brain ~ accept * age(or group) + (1|participant)

## prepare empty df to store results
```{r}
results_cols = c("brain", "mod", "Coef", "p", "p_check", "p_0125_check")
results_df = data.frame(matrix(nrow = 4*(3+1), ncol = length(results_cols)))
colnames(results_df) = results_cols
```

## anterior insula
### test if it's worth adding a random slope for brain (NO)
```{r}
summary(
  glmer(accept ~ anteriorinsula_corrected + 
          (1 + anteriorinsula_corrected||participant_id ), 
        data = all_trials_df,
       family = binomial))
```

### choice ~ anterior insula * age * group3 + controls, won't converge
```{r}
P2_NH1_AI_age_group_m1 =
  glmer(accept ~ anteriorinsula_corrected * age_bi * group_tri + 
          offer +
         tsnr + fd_mean + response_time +
        # (1 + offer + response_time || participant_id), # won't converge
        (1 + offer || participant_id), # won't converge
       data = all_trials_df,
       family = binomial)
summary(P2_NH1_AI_age_group_m1)
```

### choice ~ anterior insula * age + controls, won't converge
```{r}
P2_NH1_AI_age_m1 =
  glmer(accept ~ anteriorinsula_corrected * age_bi + 
          offer +
         tsnr + fd_mean + response_time +
        # (1 + offer + response_time || participant_id), # won't converge
        (1 + offer || participant_id), # won't converge
       data = all_trials_df,
       family = binomial)

summary(P2_NH1_AI_age_m1)
```

### choice ~ anterior insula * group_tri + controls, won't converge
```{r}
P2_NH1_AI_group_m1 =
  glmer(accept ~ anteriorinsula_corrected * group_tri + offer +
         tsnr + fd_mean + response_time +
         # (1 + offer + response_time || participant_id), # won't converge
        (1 + offer || participant_id), # won't converge
       data = all_trials_df,
       family = binomial)
summary(P2_NH1_AI_group_m1)
```

### choice ~ anterior insula * human + controls, won't converge
```{r}
P2_NH1_AI_human_m1 =
  glmer(accept ~ anteriorinsula_corrected * human + offer + age_bi + 
         tsnr + fd_mean + response_time +
         # (1 + offer + response_time || participant_id), # won't converge
        (1 + offer || participant_id), # won't converge
       data = all_trials_df,
       family = binomial)
summary(P2_NH1_AI_human_m1)
```

### choice ~ anterior insula * similar + controls, won't converge
```{r}
P2_NH1_AI_human_m1 =
  glmer(accept ~ anteriorinsula_corrected * ingroup + offer + age_bi + 
         tsnr + fd_mean + response_time +
         # (1 + offer + response_time || participant_id), # won't converge
        (1 + offer || participant_id), # won't converge
       data = all_trials_df[all_trials_df$human == 1,],
       family = binomial)
summary(P2_NH1_AI_human_m1)
```

#### plot (to abandon)
```{r}
# Compute partial residuals for X
# Step 1: Residualize y by Z and random effects
P2_NH1_AI_human_m1_pr_y = glmer(accept ~ human + offer +
                                tsnr + fd_mean + response_time +
                                (1 | participant_id),
                              data = all_trials_df,
                              family = binomial)


res.accept_pr <- residuals(P2_NH1_AI_human_m1_pr_y)

# # Step 2: Residualize X by Z and random effects
P2_NH1_AI_human_m1_pr_x = lmer(anteriorinsula_corrected ~ human + offer +
                                tsnr + fd_mean + response_time +
                                (1 | participant_id),
                              data = all_trials_df)
res.AI_pr <- residuals(P2_NH1_AI_human_m1_pr_x)

# Create partial residual plot
pr_plot_df = data.frame(res.x = res.AI_pr,
                        res.y = res.accept_pr,
                        AI = all_trials_df$anteriorinsula_corrected,
                        human = all_trials_df$human)

ggplot(pr_plot_df, aes(x = AI, y = res.y, color = human)) +
  # geom_point() +
  geom_smooth(method = "lm", se = F) +
  labs(x = "Partial residual for X (controlling for Z and participant)",
       y = "Partial residual for y (controlling for Z and participant)") +
  theme_minimal()

ggplot(pr_plot_df, aes(x = res.x, y = res.y, color = human)) +
  # geom_point() +
  geom_smooth(method = "lm", se = F) +
  labs(x = "Partial residual for X (controlling for Z and participant)",
       y = "Partial residual for y (controlling for Z and participant)") +
  theme_minimal()
```

### choice ~ anterior insula + controls, # won't converge
```{r}

P2_NH1_AI_similar_m1 =
  glmer(accept ~ anteriorinsula_corrected + offer + age_bi + 
         tsnr + fd_mean + response_time +
        # (1 + offer + response_time || participant_id), # won't converge
        (1 + offer || participant_id), # won't converge
       data = all_trials_df,
       family = binomial)
summary(P2_NH1_AI_similar_m1)
```

## dACC
### test if it's worth adding a random slope for brain (NO)
```{r}
summary(
  glmer(accept ~ dacc_corrected + 
          (1 + dacc_corrected||participant_id ), 
        data = all_trials_df,
       family = binomial))
```

### choice ~ dACC * age * group3 + controls, won't converge
```{r}
## won't converge
P2_NH1_dacc_age_group_m1 =
  glmer(accept ~ dacc_corrected * age_bi * group_tri + offer +
         tsnr + fd_mean + response_time +
         # (1 + offer + response_time || participant_id), # won't converge
        (1 + offer || participant_id), # won't converge
       data = all_trials_df,
       family = binomial)
summary(P2_NH1_dacc_age_group_m1)
```

### choice ~ dACC * age + controls, won't converge
```{r}
P2_NH1_dacc_age_m1 =
  glmer(accept ~ dacc_corrected * age_bi + offer +
         tsnr + fd_mean + response_time +
          # (1 + offer + response_time || participant_id), # won't converge
        (1 + offer || participant_id), # won't converge
       data = all_trials_df,
       family = binomial)
summary(P2_NH1_dacc_age_m1)
```

### choice ~ dACC * group3 + controls, won't converge
```{r}
P2_NH1_dacc_group_m1 =
  glmer(accept ~ dacc_corrected * group_tri + offer + age_bi +
         tsnr + fd_mean + response_time +
         # (1 + offer + response_time || participant_id), # won't converge
          (1 + offer || participant_id), # won't converge
       data = all_trials_df,
       family = binomial)
summary(P2_NH1_dacc_group_m1)
```

### choice ~ dACC * human + controls, won't converge
```{r}
P2_NH1_dacc_human_m1 =
  glmer(accept ~ dacc_corrected * human + offer + age_bi +
         tsnr + fd_mean + response_time +
         # (1 + offer + response_time || participant_id), # won't converge
        (1 + offer || participant_id), # won't converge
       data = all_trials_df,
       family = binomial)
summary(P2_NH1_dacc_human_m1)
```

### choice ~ dacc * similar + controls, won't converge
```{r}

P2_NH1_dacc_similar_m1 =
  glmer(accept ~ dacc_corrected * ingroup + offer + age_bi +
          tsnr + fd_mean + response_time +
          # (1 + offer + response_time || participant_id), # won't converge
        (1 + offer || participant_id), # won't converge
        data = all_trials_similar_df,
        family = binomial)
summary(P2_NH1_dacc_similar_m1)
```

### choice ~ dacc + controls, NON
```{r}
P2_NH1_dacc_m1 =
  glmer(accept ~ dacc_corrected + offer + age_bi + 
          tsnr + fd_mean + response_time +
          # (1 + offer + response_time || participant_id), # won't converge
        (1 + offer || participant_id),
        data = all_trials_df,
        family = binomial)
summary(P2_NH1_dacc_m1)
```

## VS
### test if it's worth adding a random slope for brain (NO)
```{r}
summary(
  glmer(accept ~ VS_corrected + 
          (1 + VS_corrected||participant_id ), 
        data = all_trials_df,
       family = binomial))
```


### choice ~ VS * age * group3 + controls, won't converge
```{r}
P2_NH1_VS_age_group_m1 =
  glmer(accept ~ VS_corrected * age_bi * group_tri + offer +
          tsnr + fd_mean + response_time +
          # (1 + offer + response_time || participant_id), # won't converge
          (1 + offer || participant_id), # won't converge
        data = all_trials_df,
        family = binomial)
summary(P2_NH1_VS_age_group_m1)
```

### choice ~ VS * age + controls, won't converge
```{r}
P2_NH1_VS_age_m1 =
  glmer(accept ~ VS_corrected * age_bi + offer +
          tsnr + fd_mean + response_time +
          # (1 + offer + response_time || participant_id), # won't converge
          (1 + offer || participant_id), # won't converge
        data = all_trials_df,
        family = binomial)
summary(P2_NH1_VS_age_m1)
```

### choice ~ VS * group3 + controls, won't converge
```{r}
P2_NH1_VS_group_m1 =
  glmer(accept ~ VS_corrected * group_tri + offer + age_bi +
          tsnr + fd_mean + response_time +
          # (1 + VS_corrected + offer + response_time || participant_id), # won't converge
          (1 + offer + response_time || participant_id), # won't converge
        data = all_trials_df,
        family = binomial)
summary(P2_NH1_VS_group_m1)
```



### choice ~ VS * human + controls, won't converge
```{r}
P2_NH1_VS_human_m1 =
  glmer(accept ~ VS_corrected * human + offer + age_bi +
          tsnr + fd_mean + response_time +
          # (1 + offer + response_time || participant_id), # won't converge
          (1 + offer || participant_id), #won't converge
        data = all_trials_df,
        family = binomial)
summary(P2_NH1_VS_human_m1)
```

### choice ~ VS * similar + controls, won't converge
```{r}

P2_NH1_VS_similar_m1 =
  glmer(accept ~ VS_corrected * ingroup + offer + age_bi +
          tsnr + fd_mean + response_time +
          # (1 + offer + response_time || participant_id), # won't converge
          (1 + offer || participant_id), # won't converge
        data = all_trials_similar_df,
        family = binomial)
summary(P2_NH1_VS_similar_m1)
```

### choice ~ VS + controls, won't converge
```{r}
P2_NH1_VS_m1 =
  glmer(accept ~ VS_corrected + offer +  age_bi +
          tsnr + fd_mean + response_time +
          # (1 + offer + response_time || participant_id), # won't converge
        (1 + offer || participant_id), # won't converge
        data = all_trials_df,
        family = binomial)
summary(P2_NH1_VS_m1)
```

## vmpfc
### test if it's worth adding a random slope for brain (NO)
```{r}
summary(
  glmer(accept ~ vmpfc_corrected + 
          (1 + vmpfc_corrected||participant_id ), 
        data = all_trials_df,
       family = binomial))
```

### choice ~ vmpfc * age * group3 + controls, won't converge
```{r}
P2_NH1_vmpfc_age_group_m1 =
  glmer(accept ~ vmpfc_corrected * age_bi * group_tri + offer +
          tsnr + fd_mean + response_time +
          # (1 + offer + response_time || participant_id), # won't converge
          (1 + offer || participant_id), # won't converge
        data = all_trials_df,
        family = binomial)
summary(P2_NH1_vmpfc_age_group_m1)
```

### choice ~ vmpfc * age + controls, won't converge
```{r}
P2_NH1_vmpfc_age_m1 =
  glmer(accept ~ vmpfc_corrected * age_bi + offer +
          tsnr + fd_mean + response_time +
          # (1 + offer + response_time || participant_id), # won't converge
        (1 + offer || participant_id), # won't converge
        data = all_trials_df,
        family = binomial)
summary(P2_NH1_vmpfc_age_m1)
```

### choice ~ vmpfc * group3 + controls, won't converge
```{r}
P2_NH1_vmpfc_group_m1 =
  glmer(accept ~ vmpfc_corrected * group_tri + offer + age_bi +
          tsnr + fd_mean + response_time +
          # (1 + offer + response_time || participant_id), # won't converge
          (1 + offer || participant_id), # won't converge
          data = all_trials_df,
        family = binomial)
summary(P2_NH1_vmpfc_group_m1)
```

### choice ~ vmpfc * human + controls, won't converge
```{r}
P2_NH1_vmpfc_human_m1 =
  glmer(accept ~ vmpfc_corrected * human + offer + age_bi +
          tsnr + fd_mean + response_time +
          # (1 + offer + response_time || participant_id), # won't converge
          (1 + offer || participant_id), # won't converge
        data = all_trials_df,
        family = binomial)
summary(P2_NH1_vmpfc_human_m1)
```

### choice ~ vmpfc * similar + controls, won't converge
```{r}

P2_NH1_vmpfc_similar_m1 =
  glmer(accept ~ vmpfc_corrected * ingroup + offer + age_bi +
          tsnr + fd_mean + response_time +
          # (1 + offer + response_time || participant_id), # won't converge
          (1 + offer || participant_id), # won't converge
        data = all_trials_similar_df,
        family = binomial)
summary(P2_NH1_vmpfc_similar_m1)
```

### choice ~ vmpfc + controls, won't converge
```{r}
P2_NH1_vmpfc_m1 =
  glmer(accept ~ vmpfc_corrected + offer + age_bi +
          tsnr + fd_mean + response_time +
          # (1 + vmpfc_corrected + offer + response_time || participant_id), # won't converge
        (1 + offer || participant_id), # won't converge
        data = all_trials_df,
        family = binomial)
summary(P2_NH1_vmpfc_m1)
```

# strictly NH1A with controls and random slope of offer
## human vs computer with fmri controls, won't converge
```{r}
# won't converge
full_model = glmer(accept ~ offer + age_bi + human +
                     tsnr + fd_mean + response_time + 
                     vmpfc_corrected + VS_corrected + 
                     dacc_corrected + anteriorinsula_corrected +
                     (1 + offer || participant_id), 
                   data = all_trials_df, family = 'binomial')
summary(full_model)

# with only random intercept, not the right model, but let's see
# converged, not sig
full_model_1 = glmer(accept ~ offer + age_bi + human +
                     tsnr + fd_mean + response_time +
                     vmpfc_corrected + VS_corrected + 
                     dacc_corrected + anteriorinsula_corrected +
                     (1 | participant_id), 
                   data = all_trials_df, family = 'binomial')
summary(full_model_1)
```

## human vs computer WITHOUT fmri controls, converged but not sig
```{r}
full_model_NOcontrol = glmer(accept ~ offer + age_bi + human +
                     # tsnr + fd_mean + response_time + 
                     vmpfc_corrected + VS_corrected + 
                     dacc_corrected + anteriorinsula_corrected +
                     (1 + offer || participant_id), 
                   data = all_trials_df, family = 'binomial')
summary(full_model_NOcontrol)

# with only random intercept, not the right model, but let's see
full_model_NOcontrol_1 = glmer(accept ~ offer + age_bi + human +
                     # tsnr + fd_mean + response_time +
                     vmpfc_corrected + VS_corrected + 
                     dacc_corrected + anteriorinsula_corrected +
                     (1 | participant_id), 
                   data = all_trials_df, family = 'binomial')
summary(full_model_NOcontrol_1)

anova(full_model_NOcontrol, full_model_NOcontrol_1, refit = FALSE)
```


## similar vs disimilar, won't converge
```{r}
# won't converge
full_model_similar = glmer(accept ~ offer + age_bi + ingroup +
                     tsnr + fd_mean + response_time + 
                     vmpfc_corrected + VS_corrected + 
                     dacc_corrected + anteriorinsula_corrected +
                     (1 + offer || participant_id), 
                   data = all_trials_similar_df, family = 'binomial')
summary(full_model_similar)

# with only random intercept, not the right model, but let's see
# won't converge
full_model_similar_1 = glmer(accept ~ offer + age_bi + ingroup +
                     # tsnr + fd_mean + response_time + 
                     vmpfc_corrected + VS_corrected + 
                     dacc_corrected + anteriorinsula_corrected +
                     (1| participant_id), 
                   data = all_trials_similar_df, family = 'binomial')
summary(full_model_similar_1)
```


# compare model fit between models with and without random slope of offer
model with randon slope of offer is better
```{r}
random_offer_slope_model = glmer(accept ~ offer +
                     (1 + offer|| participant_id), 
                   data = all_trials_df, family = 'binomial')
# summary(random_offer_slope_model)
icc(random_offer_slope_model)

random_interceptONLY_model = glmer(accept ~ offer +
                     (1 | participant_id), 
                   data = all_trials_df, family = 'binomial')
# summary(random_interceptONLY_model)
icc(random_interceptONLY_model)

anova(random_offer_slope_model, random_interceptONLY_model)
```

# compare model fit between model with random slope of offer with fixed age and without random slope
result: with random slope of offer is better
```{r}
age_random_offer_slope_model = glmer(accept ~ offer + age_bi +
                     (1 + offer|| participant_id), 
                   data = all_trials_df, family = 'binomial')
summary(age_random_offer_slope_model)
icc(age_random_offer_slope_model)

age_random_interceptONLY_model = glmer(accept ~ offer + age_bi +
                     (1| participant_id), 
                   data = all_trials_df, family = 'binomial')
summary(age_random_interceptONLY_model)
icc(age_random_interceptONLY_model)

anova(age_random_offer_slope_model, age_random_interceptONLY_model, refit = FALSE)
```


# end of code

