---
title: "srndna-ultimatum-analyses"
author: "Rita M Ludwig"
date: "2022-09-13"
output: html_document
---
```{r load_packages, include=FALSE}
library(tidyverse)
library(dplyr)
library(stringr)
library(tools)
library(lme4)
library(performance)
library(lattice)
library(sjPlot)
library(DHARMa)
library(interactions)
library(equatiomatic)
```
```{r, setup, include=FALSE}
# Set the correct path to the behavioral data folder
knitr::opts_knit$set(root.dir = '/Users/rludwig/Documents/srndnaUG/data/')
```
```{r import_dataframes, include=FALSE}
blockdf = read_csv("srndna-ultimatum-behavioral-data.csv", show_col_types = FALSE) %>%
  mutate(partner = as.character(partner) %>% fct_recode("computer" = "0", "dissimilar" = "1", "similar" = "2")) %>%
  mutate(partner_binary = case_when(partner != "computer" ~ "human",
                                    TRUE ~ "computer")) %>%
  mutate(agecat = as_factor(agecat)) %>%
  mutate(IsFairBlock = as.character(IsFairBlock) %>% fct_recode("unfair" = "0", "fair" = "1")) %>%
  mutate(trial_type = paste(partner,IsFairBlock, " "))

trialdf = read_csv("srndna-ultimatum-behavioral-data_pertrial.csv", show_col_types = FALSE, ) %>%
  mutate(agecat = as_factor(agecat)) %>%
  mutate(IsFairBlock = as.character(IsFairBlock) %>% fct_recode("unfair" = "0", "fair" = "1")) %>%
  mutate(partner = as.character(partner) %>% fct_recode("computer" = "1", "dissimilar" = "2", "similar" = "3")) %>%
  mutate(response = as.character(response) %>% fct_recode("reject" = "0", "accept" = "1")) %>%
  mutate(trial_type = as_factor(trial_type))

# A REMINDER: I removed sub-143 for now, not sure what's going on with their EV file
```
First, test the hypotheses that were part of the aspredicted pre-registration that are predicting average proportion of acceptance rates per block (vs individual binary offer decisions).
```{r asp_model_testing}
#Test the null model
null_model_sne = lmer(proportion_accept ~ 1 + (1|participant_id), data = blockdf)
summary(null_model_sne)
#ICC - the proportion of variance in acceptance that is attributable to participants
icc(null_model_sne)

#Fixed effects for partner
# Partner type: 0 = computer, 1 = outgroup, 2 = ingroup
partner_model_sne = lmer(proportion_accept ~ partner + (1|participant_id), data = blockdf)
summary(partner_model_sne)
#ICC - the proportion of variance in acceptance that is attributable to participants, after accounting for partner type
icc(partner_model_sne)

#Fixed effects for fairness
# IsFairBlock: 1 = fair, 0  unfair
fair_model_sne = lmer(proportion_accept ~ IsFairBlock + (1|participant_id), data = blockdf)
summary(fair_model_sne)
#ICC - the proportion of variance in acceptance that is attributable to participants, after accounting for partner type
icc(fair_model_sne)

#Fixed effects for age
age_model_sne = lmer(proportion_accept ~ agecat + (1|participant_id), data = blockdf)
summary(age_model_sne)
#ICC - the proportion of variance in acceptance that is attributable to participants, after accounting for their age
icc(age_model_sne)

#Testing the hypothesis: Younger adults will accept more offers from human partners who are similar to them, but older adults will not discriminate. 
#NOTE: have to add a random slope to the level 1 model to give the model something to actually attribute the variance of at level 2.
#Age: 0 = younger, 1 = older; Partner: 0 = computer, 1 = dissimilar, 2 = similar
h1_model_sne = lmer(proportion_accept ~ 1 + partner + agecat + partner:agecat + (1 + partner|participant_id), data=blockdf, REML = TRUE)
summary(h1_model_sne)
icc(h1_model_sne)
# now check for multicollinearity
check_collinearity(h1_model_sne)

#young, similar: 0.658964
#young, dissimilar: 0.662427
#old, similar: 0.688135
#old, dissimilar: 0.6977


#Testing the hypothesis: Everyone will reject more unfair offers from human (vs. computer) partners, and this effect will be stronger for younger adults.
#Age: 0 = younger, 1 = older; Partner: 0 = computer, 1 = dissimilar, 2 = similar, # IsFairBlock: 1 = fair, 0  unfair
h2_model_sne = lmer(proportion_accept ~ 1 + IsFairBlock*partner*agecat + (1 + IsFairBlock|participant_id), data=blockdf, REML = TRUE)
summary(h2_model_sne)
icc(h2_model_sne)
# now check for multicollinearity
check_collinearity(h2_model_sne)

#young,unfair,computer: 0.489907
#young, unfair, human: 0.514462
#old, unfair, computer: 0.610964
#old, unfair, human: 0.520964
```
As established in the pre-registration, the following code will test a series of mixed effects logistic regression models, beginning with a "null" model to test for evidence of L2 variance. Relative fit of these models is assessed via significance tests on chi square differences.

The mixed effects models of interest are: a) a model with offer value, b) a model with offer value and offer block type, c) a model with trial offer value, offer block type, and BOLD signal in each ROI, d) a 'full' model with all covariates.

Model C as described above in R notation is:
accept ~ offer value * offer block + vmpfc + dacc + insula + (1 | participantID)
```{r osf_model_testing}
#Create grand mean-centered offer variable to aid in interpretability
trialdf$Offer_centered = scale(trialdf$Offer, center=TRUE, scale=FALSE)

#Test the null model
null_model = glmer(response ~ 1 + (1|participant_id), data = trialdf, family = 'binomial')
summary(null_model)
#ICC - the proportion of variance in acceptance that is attributable to participants
icc(null_model)

#Test the offer value model (model a, above)
offer_model = glmer(response ~ Offer + (1|participant_id), data = trialdf, family = 'binomial')
summary(offer_model)
icc(offer_model)

#Test the age and partner model (aspredicted hypothesis; should be HUMAN v computer
partnerage_model = glmer(response ~ partner*agedummy + (1|participant_id), data = trialdf, family = 'binomial')
summary(partnerage_model)
icc(partnerage_model)

#Test the offer value, age, and partner model (aspredicted hypothesis; should be HUMAN v computer
offerpartnerage_model = glmer(response ~ IsFairBlock*partner*agedummy + (1|participant_id), data = trialdf, family = 'binomial')
summary(offerpartnerage_model)
icc(offerpartnerage_model)

#Test the offer value and block type model (model b, above)
offerblock_model = glmer(response ~ Offer_centered * IsFairBlock + (1|participant_id), data = trialdf, family = 'binomial')
summary(offerblock_model)
icc(offerblock_model)

#Test the offer value, block type, and ROIs model (model c, above)
ROIs_model = glmer(response ~ Offer * IsFairBlock + aINS + dACC + VMPFC + VS + (1 | participant_id), data = trialdf, family = 'binomial')
summary(ROIs_model)
icc(ROIs_model)

#Test the full model
full_model = glmer(response ~ Offer * IsFairBlock + partner + agedummy + aINS + dACC + VMPFC + VS + (1 | participant_id), data = trialdf, family = 'binomial')
summary(full_model)

```
Model assumption testing, data inspection. Model assumption testing conducted using the package DHARMa, which "uses a simulation-based approach to create readily interpretable scaled (quantile) residuals for fitted (generalized) linear mixed models."
```{r assumption_testing}
##Inspect data - are there differences in intercepts and slopes across choices within participants? (Looks like yes)
data_sub = trialdf %>% 
  filter(str_detect(participant_id, "sub-10[1-9]"))
data_sub %>% 
  ggplot(mapping = aes(x = Offer, y = response, colour = factor(participant_id))) +
  geom_point() +
  geom_smooth(mapping = aes(group = participant_id), method = "lm", se = FALSE, fullrange = TRUE) +
  labs(colour = "participant_id")
blockdata_sub = blockdf %>%
  filter(str_detect(participant_id, "sub-11[1-9]"))
blockdata_sub %>% 
  ggplot(mapping = aes(x = trial_type, y = proportion_accept, color = participant_id, group = participant_id)) + geom_line() + geom_point()

##Simulate residuals using the DHARMa package
simulatedresiduals_null = simulateResiduals(fittedModel = null_model, plot = F)
simulatedresiduals_offer = simulateResiduals(fittedModel = offer_model, plot = F)
simulatedresiduals_offerblock = simulateResiduals(fittedModel = offerblock_model, plot = F)
simulatedresiduals_ROIs = simulateResiduals(fittedModel = ROIs_model, plot = F)
simulatedresiduals_full = simulateResiduals(fittedModel = full_model, plot = F)

## QQplots and residuals vs predicted values
plot(simulatedresiduals_null)
plot(simulatedresiduals_offer)
plot(simulatedresiduals_offerblock)
plot(simulatedresiduals_ROIs)
plot(simulatedresiduals_full)

##Autocorrelation check
resTime_null = recalculateResiduals(simulatedresiduals_null, sel = trialdf$participant_id == "sub-106")
testTemporalAutocorrelation(resTime_null, time = unique(trialdf$runningtrialno))

```
```{r tables_figures}
# Tables
tab_model(offer_model)
tab_model(offerblock_model)
tab_model(ROIs_model)
tab_model(full_model)

# Plots
plot_model(offer_model, vline.color = "black")
plot_model(offerblock_model, vline.color = "black")
plot_model(partnerage_model, vline.color = "black")
plot_model(ROIs_model, vline.color = "black")
plot_model(full_model, vline.color = "black")

interact_plot(partnerage_model, pred = agedummy, modx = partner)
interact_plot(offerblock_model, pred = Offer_centered, modx = IsFairBlock)





```
